---
title: "CB-mouthColor"
author: "Justin Mann"
date: "4/16/2021"
output: html_document
---

```{r libraries, message=FALSE, warning=FALSE}
library(RColorBrewer); #brewer.pal(n=8, name = "Dark2") #;display.brewer.pal(n = 8, name = "Dark2")
library(tidyverse); theme_set(theme_classic()) #ggplot2, dplyr, tibble, etc.
library(plotly) #use ggplotly() for interactive plots with scoll-over IDs
library(knitr) #use kable() to make formatted tables
library(kableExtra)
library(Rtsne)
library(glmmTMB)
library(lme4)
library(sjPlot)
library(ggpubr) #ggarrange() figure wraps
library(plyr)
library(ggeffects) #ggpredict
library(rstanarm) #stan models
library(shinystan) #stan model evaluation >launch_shinystan_demo()
library(loo) #loo() to compare fits between bayesian models
library(MuMIn) #dredge, model averaging
library(AICcmodavg) #aictab() for AICc model comparisons
library(coin) #permutation test for ratios with independence_test()
library(janitor) #get_dupes() finds and prints duplicates
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<br>

### <b>Read in mouth color data (mc)</b>
<br>
```{r mouth color dataframe}
allAges.mc=tibble(read.csv("CB-mouthColor.csv", h=T)) #N=215

#subset with ages 23-27
mc <- allAges.mc %>% filter(between(age,23,27)) #N=133
```
<br>


<b>Create subsets of mc for females (N=78) and males (N=55) only</b>
```{r subset mc by sex}
#females only
female.mc <- mc %>% 
  filter(sex == "F") #N=78
#males only
male.mc <- mc %>% 
  filter(sex == "M") #N=55
```
<br>

### <b>Read in nestling morphometrics data (nm)</b>
<br>
<b>Nestling morphometrics are being used here to boost sample size for calculating mass/tarsus residuals</b>
<br>
<b>Replace zeros with NAs, sort and filter by age (23-27)</b> 
```{r nestling morphometrics dataframe}
nm=tibble(read.csv("nestlingMorph.csv", h=T))
#replace zeros with NAs in morphometrics 
nm[nm==0] <- NA
#remove nestlingMeasurementNumber
nm <- nm[,-1]
#sort by year > nestName > id
nm <- nm %>% arrange(year, nestName ,id)
#filter to include only ages 23-27
nm <- nm %>% filter(between(age, 23, 27)) 
```
<br>

<b>Create subset of nm including only sexed birds (N=503; females=268; males=235)</b>
```{r subset nm for sexed birds}
#subset nm to include only sexed birds and remove NAs from mass & tarsus
sexed.nm <- nm %>% drop_na(sex, tarsus, mass) #N=503
#make sex a factor rather than character
sexed.nm$sex <- as.factor(sexed.nm$sex)
```
<br>

### Plot--mass distribution by sex
<br>

<b>Only includes sexed individuals (N=503)</b>
```{r mass distribution by sex}
sexed.nm %>% 
  ggplot(aes(mass, fill=sex))+
  geom_histogram(binwidth = 10)+
  scale_fill_manual(values = c("#1B9E77", "#D73027"),
                    name = "",
                    labels = c("Female","Male"))+
  annotate(geom = "text", x=375, y=29, label="N=268")+
  annotate(geom = "text", x=390, y=5, label="N=235")
```
<br>

### Plot--tarsus distribution by sex
<br>

<b>Only includes sexed individuals (N=503)</b>
```{r tarsus distribution by sex}
sexed.nm %>% 
  ggplot(aes(tarsus, fill=sex))+
  geom_histogram(binwidth = 0.5)+
  scale_fill_manual(values = c("#1B9E77", "#D73027"),
                    name = "",
                    labels = c("Female","Male"))+
  annotate(geom = "text", x=59, y=28, label="N=268")+
  annotate(geom = "text", x=60, y=5, label="N=235")
```
<br>

### Plot--mass by tarsus with sex filter (N=503)
```{r Plot--mass ~ tarsus with sex filter}
massTarsus.plot <- sexed.nm %>% 
  ggplot(aes(x=tarsus,y=mass,color=sex,label=id))+
  geom_point(alpha=0.5)+
  geom_smooth()+
  scale_color_manual(values = c("#1B9E77", "#D73027"),
                    name = "",
                    labels = c("Female","Male"))
ggplotly(massTarsus.plot)
```
<br>

Remove outliers (SWB-W BURP03, EN WKAY05, GL JSUP05, YASB WCEM01), now N=499
```{r remove mass/tarsus outliers from sexed.nm}
sexed.nm <- sexed.nm[-c(211, 141, 332, 353),] #N=499
```
<br>

```{r Plot--mass ~ tarsus with sex filter outliers removed}
massTarsus.plot <- sexed.nm %>% 
  ggplot(aes(x=tarsus,y=mass,color=sex,label=id))+
  geom_point(alpha=0.5)+
  geom_smooth()+
  scale_color_manual(values = c("#1B9E77", "#D73027"),
                    name = "",
                    labels = c("Female","Male"))
ggplotly(massTarsus.plot)
```
<br>

```{r nm-sexes separate}
#females only 
female.nm <- sexed.nm %>% 
  filter(sex == "F") #N=265
#males only
male.nm <- sexed.nm %>% 
  filter(sex == "M") #N=234
```
<br>

### Create the female mass~tarsus residual index
```{r female mass~tarsus}
femaleIndex.lm <- lm(mass~tarsus, female.nm)
summary(femaleIndex.lm)
```
<br>

<b>Check residual distributions</b>
<br>

*Q-Q plot looks a little non-normal, probably seeing the effects of reduced sample size by separating sexes.
```{r plot female model residuals}
plot(femaleIndex.lm)
```
<br>

<br>
### Create male mass~tarsus residual index
```{r male mass~tarsus}
maleIndex.lm <- lm(mass~tarsus, male.nm)
summary(maleIndex.lm)
```
<br>

<b>Plot residuals</b>
```{r plot male model residuals}
plot(maleIndex.lm)
```
<br>


<br>
<b>Create dataframes containing id and residuals</b>
```{r residual dataframes}
#male residuals pulled from lm() output
male.nm$resids <- maleIndex.lm$residuals
#female residuals pulled from lm() output
female.nm$resids <- femaleIndex.lm$residuals

#dataframes containing male and female ids and residuals for the join with mc
joinMaleResidual <- data.frame(id = male.nm$id,
                               resids = male.nm$resids)
joinFemaleResidual <- data.frame(id = female.nm$id,
                                 resids = female.nm$resids)
```
<br>

<b>Join residuals with male and female mouth color data by common id</b>
```{r join residuals from sex-specific models}
#left join with female mc
female.mc <- left_join(female.mc,joinFemaleResidual, by="id")

#left join with male mc
male.mc <- left_join(male.mc,joinMaleResidual, by="id")

#left join with both sexes (full mc) 
bothSexResid <- data.frame(rbind(joinMaleResidual,joinFemaleResidual))
mc <- left_join(mc,bothSexResid, by="id")
```
<br>

<b>Distribution of residuals for both sexes combined</b>
```{r histogram of male and female residuals combined}
mc %>%
  ggplot(aes(x=resids, fill=sex))+
  geom_histogram(binwidth = 10)+
  scale_fill_manual(values = c("#1B9E77", "#D73027"),
                    name = "",
                    labels = c("Female","Male"))
```
<br>

## Mass and mass/tarsus indices for modeling
```{r mass and mass/tarsus ratios}
mc$ratio <- mc$mass/mc$tarsus
mc$cubeMass <- mc$mass^(1/3)
mc$cubeRatio <- ((mc$mass^(1/3))/mc$tarsus)*100
```
<br>

### Permutation test to assess independence of male and female ratios
reference: https://stats.stackexchange.com/questions/23152/test-for-significant-difference-in-ratios-of-normally-distributed-random-variabl 
```{r mass/tarsus ratio permutation test}
independence_test(ratio~as.factor(sex), data = mc)
```


<b>Distribution of mass/tarsus ratio for both sexes combined</b>
```{r histogram of male and female ratios combined}
mc %>%
  ggplot(aes(x=ratio, fill=sex))+
  geom_histogram(binwidth = 0.4)+
  scale_fill_manual(values = c("#1B9E77", "#D73027"),
                    name = "",
                    labels = c("Female","Male"))
```
<br>

```{r histogram of mass}
mc %>%
  ggplot(aes(x=mass, fill=sex))+
  geom_histogram(binwidth = 20)+
  scale_fill_manual(values = c("#1B9E77", "#D73027"),
                    name = "",
                    labels = c("Female","Male"))
```

```{r histogram of cubeMass}
mc %>%
  ggplot(aes(x=cubeMass, fill=sex))+
  geom_histogram(binwidth = 0.1)+
  scale_fill_manual(values = c("#1B9E77", "#D73027"),
                    name = "",
                    labels = c("Female","Male"))
```
<br> 

```{r histogram of cubeMassRatio}
mc %>%
  ggplot(aes(x=cubeRatio, fill=sex))+
  geom_histogram(binwidth = 0.3)+
  scale_fill_manual(values = c("#1B9E77", "#D73027"),
                    name = "",
                    labels = c("Female","Male"))
```

## SATURATION 1 MODELS
<br>

Plot saturation by age
```{r sat1~age plot}
mc %>% 
  ggplot(aes(x=sat1,y=age)) +
  geom_point()+
  geom_smooth()
```
<br>

Plot saturation by mass
```{r sat1~mass plot}
satMass.plot <- mc %>% 
  ggplot(aes(x=sat1,y=mass, label = id)) +
  geom_point()+
  geom_smooth()
ggplotly(satMass.plot) 
```
<br>

Plot age by mass
```{r age~mass plot}
ageMass.plot <- mc %>% 
  ggplot(aes(x=age, y=mass, label = id)) +
  geom_point()+
  geom_smooth()+
  geom_boxplot()
ggplotly(ageMass.plot) 
```
<br>

### <b>Sat1 ~ mass/tarsus residual model</b>
```{r sat1 residual model}
sat1Residual.mdl <- lmer(sat1 ~ age + resids + sex + 
                           bodTemp1 + ambTemp1 + timeOut1 + (1|family), 
                    data = mc, REML = FALSE)
summary(sat1Residual.mdl)
```
<br>

Plot residual model
```{r plot sat1 residual model}
plot_model(sat1Residual.mdl,
           title = "Saturation 1 residual model",
           bpe = "median",
           vline.color = "black",
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1.2)
```
<br>

### <b>Sat1 ~ mass/tarsus ratio model</b>
```{r sat1 ratio model}
sat1Ratio.mdl <- lmer(sat1 ~ age + ratio + sex + 
                        bodTemp1 + ambTemp1 + timeOut1 + (1|family), 
                    data = mc, REML = FALSE)
summary(sat1Ratio.mdl)
```

Plot ratio model
```{r plot sat1 ratio model}
sat1RatioMdl.plot <- plot_model(sat1Ratio.mdl,
           title = "Saturation 1 ratio model",
           bpe = "median",
           vline.color = "black",
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1.2)
sat1RatioMdl.plot
```
<br>

### <b>Sat1 ~ mass model</b>
```{r sat1 mass model}
sat1Mass.mdl <- lmer(sat1 ~ age + mass + sex + 
                        bodTemp1 + ambTemp1 + timeOut1 + (1|family), 
                    data = mc, REML = FALSE)
summary(sat1Mass.mdl)
```

Plot mass model
```{r plot sat1 mass model}
sat1MassMdl.plot <- plot_model(sat1Mass.mdl,
           title = "Saturation 1 mass model",
           bpe = "median",
           vline.color = "black",
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1.2)
sat1MassMdl.plot
```
<br>

### <b>Sat1 ~ cube mass model</b>
```{r sat 1 cube mass model}
sat1CubeMass.mdl <- lmer(sat1 ~ age + cubeMass + sex + 
                        bodTemp1 + ambTemp1 + timeOut1 + (1|family), 
                    data = mc, REML = FALSE)
summary(sat1CubeMass.mdl)
```

Plot cube mass model
```{r plot sat 1 cube mass model}
sat1CubeMassMdl.plot <- plot_model(sat1CubeMass.mdl,
           title = "Saturation 1 cube mass model",
           bpe = "median",
           vline.color = "black",
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1.2)
sat1CubeMassMdl.plot
```
<br>

### <b>Sat1 ~ cube ratio model</b>
```{r sat1 cube ratio model}
sat1CubeRatio.mdl <- lmer(sat1 ~ age + cubeRatio + sex + 
                        bodTemp1 + ambTemp1 + timeOut1 + (1|family), 
                    data = mc, REML = FALSE)
summary(sat1CubeRatio.mdl)
```

Plot cube mass model
```{r plot sat1 cube ratio model}
sat1CubeRatioMdl.plot <- plot_model(sat1CubeRatio.mdl,
           title = "Saturation 1 cube ratio model",
           bpe = "median",
           vline.color = "black",
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1.2)
sat1CubeRatioMdl.plot
```
<br>


<br>
### Now let's compare the fit of models with different condition indices
```{r indices model comparison}
indices.mdls <- c(sat1Residual.mdl, sat1Ratio.mdl, sat1Mass.mdl, sat1CubeMass.mdl, sat1CubeRatio.mdl)
indices.modnames <- c("Residual", "Ratio", "Mass", "Cube Mass", "Cube Ratio")
confset(indices.mdls, modnames = indices.modnames, method = "ordinal")
```
<br>

Using AICc Weight (AICcWt), the confset() function calculates the probability of each model given the data and the other candidate models. So in this case, we have more confidence in the ratio model's ability to explain the variation in the data, even though AICc values are only slightly different.
<br>


## HUE 1 MODELS
<br>

```{r hue1 ratio model}
hue1.mdl <- lmer(hue1*100 ~ age + ratio + sex + bodTemp1 + ambTemp1 + (1|family), 
                    data = mc, REML = FALSE)
```
<br>

```{r plot hue1 ratio model}
hue1Mdl.plot <- plot_model(hue1.mdl,
           title = "hue 1 model",
           bpe = "median",
           vline.color = "black",
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1.2)
hue1Mdl.plot
```
<br>


## TIME 2 DATA FRAME
<br>

```{r time2 data frame}
#create a time 2 data frame (N=103)
time2.mc <- mc %>% select(row:sex, ends_with("2"), ambFinal, broodSize, date:skull, resids, ratio)

#I'm dropping ambTemp2 from data frame before dropping NAs. 
#ambTemp2 has many more NAs. We can use ambFinal instead.
#This boosts sample size from 32 to 99 obs. 
time2.mc <- time2.mc %>% select(!ambTemp2) 

#Now drop NAs after removing ambTemp2
time2.mc <- drop_na(time2.mc)
```
<br>

At time 1, we have 78 females and 55 males.
At time 2, we have 64 females and 39 males. 

<br>

### SATURATION 2 MODELS
<br>

```{r sat2 ratio model}
sat2.mdl <- lmer(sat2 ~ age + ratio + sex + bodTemp2 + ambFinal + timeOut2 + (1|family), 
                    data = time2.mc, REML = FALSE)
summary(sat2.mdl)
```

Plot sat2 model
```{r plot sat2 ratio model}
sat2Mdl.plot <- plot_model(sat2.mdl,
           title = "Saturation 2 ratio model",
           bpe = "median",
           vline.color = "black",
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1.2)
sat2Mdl.plot
```
<br>

### HUE 2 MODELS
<br>

```{r hue2 ratio model}
hue2.mdl <- lmer(hue2*100 ~ age + ratio + sex + bodTemp2 + ambFinal + timeOut2 + (1|family), 
                    data = time2.mc, REML = FALSE)
summary(hue2.mdl)
```
<br>

Plot hue 2 model
```{r plot hue2 ratio model}
hue2Mdl.plot <- plot_model(hue2.mdl,
           title = "hue 2 model",
           bpe = "median",
           vline.color = "black",
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1.2)
hue2Mdl.plot
```
<br>

Wrap sat and hue model plots
```{r wrap model plots, out.width='100%'}
ratioMdlWrap <- ggarrange(sat1RatioMdl.plot, hue1Mdl.plot, sat2Mdl.plot, hue2Mdl.plot)
ratioMdlWrap
#ggsave("ratioMdlWrap.png", plot = ratioMdlWrap, device = "png", dpi = 300, width = 10, height = 8)
```
<br>

### Birds with both time1 and time2 data ONLY
<br>

The semi_join() function returns all rows from mc where there are matching IDs in time2.mc, keeping just columns from mc. 
```{r both times (BT) data frame}
bothTimes.mc <- semi_join(mc,time2.mc, by="id") #N=103
```
<br>

### BOTH TIMES SAT1 RATIO MODEL
<br>

```{r BT sat1 model}
sat1.BT.mdl <- lmer(sat1 ~ age + ratio + sex + 
                        bodTemp1 + ambTemp1 + timeOut1 + (1|family), 
                    data = bothTimes.mc, REML = FALSE)
summary(sat1.BT.mdl)
```

Plot both times sat1 model
```{r plot BT sat1 ratio model}
sat1.BT.mdl.plot <- plot_model(sat1.BT.mdl,
           title = "Both times sat1 model",
           bpe = "median",
           vline.color = "black",
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1.2)
sat1.BT.mdl.plot
```

<br>

### Both times hue1 ratio model
<br>

```{r BT hue1 ratio model}
hue1.BT.mdl <- lmer(hue1*100 ~ age + ratio + sex + bodTemp1 + ambTemp1 + timeOut1 + (1|family), 
                    data = bothTimes.mc, REML = FALSE)
```
<br>

Plot both times hue1 model
```{r plot BT hue1 ratio model}
hue1.BT.mdl.plot <- plot_model(hue1.BT.mdl,
           title = "Both times hue1 model",
           bpe = "median",
           vline.color = "black",
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1.2)
hue1.BT.mdl.plot
```
<br>

Wrap both times model plots

```{r wrap both time model plots, out.width='100%'}
bothTimes.mdlWrap <- ggarrange(sat1.BT.mdl.plot, hue1.BT.mdl.plot, sat2Mdl.plot, hue2Mdl.plot)
bothTimes.mdlWrap
#ggsave("bothTimesMdlWrap.png", plot = bothTimes.mdlWrap, device = "png", dpi = 300, width = 10, height = 8)
```
<br>

## WHAT RESPONSE VARIABLES TO USE?
<br>

Plot saturation by hue
```{r}
mc %>% ggplot(aes(x=sat1, y=hue1))+
  geom_jitter()+
  geom_smooth()
```
<br>


### Separate yellow and magenta models for time 1
<br>

Mean yellow 1 model
```{r meanY1 model}
meanY.mdl <- lmer(meanY1 ~ age + ratio + sex + 
                        bodTemp1 + ambTemp1 + (1|family), 
                    data = mc, REML = FALSE)
```

Plot mean yellow 1 model
```{r plot meanY1 model}
meanY.plot <- plot_model(meanY.mdl,
           title = "mean yellow 1 model",
           bpe = "median",
           vline.color = "black",
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1.2)
```
<br>

Mean magenta 1 model
```{r meanM1 model time1}
meanM.mdl <- lmer(meanM1 ~ age + ratio + sex + 
                        bodTemp1 + ambTemp1 + (1|family), 
                    data = mc, REML = FALSE)
```
<br>

Plot mean magenta 1 model
```{r plot meanM1 model time1}
meanM.plot <- plot_model(meanM.mdl,
           title = "mean magenta 1 model",
           bpe = "median",
           vline.color = "black",
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1.2)
```
<br>

Wrap plot of mean Y1 & mean M1 models
```{r wrap plots of mean Y1 & M1 models}
ggarrange(meanY.plot,meanM.plot)
```
<br>


### Separate yellow and magenta models for time 2
<br>

Mean yellow 2 model
```{r meanY2 model}
meanY2.mdl <- lmer(meanY2 ~ age + ratio + sex + 
                        bodTemp2 + ambFinal + timeOut2 + (1|family), 
                    data = time2.mc, REML = FALSE)
```

Plot mean yellow 2 model 
```{r plot meanY2 model}
meanY2.plot <- plot_model(meanY2.mdl,
           title = "mean yellow 2 model",
           bpe = "median",
           vline.color = "black",
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1.2)
```
<br>

Mean magenta 2 model
```{r meanM2 model}
meanM2.mdl <- lmer(meanM2 ~ age + ratio + sex + 
                        bodTemp2 + ambFinal + timeOut2 + (1|family), 
                    data = time2.mc, REML = FALSE)
```

Plot mean magenta 2 model 
```{r plot meanM2 model}
meanM2.plot <- plot_model(meanM2.mdl,
           title = "mean magenta 2 model",
           bpe = "median",
           vline.color = "black",
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1.2)
```
<br>

Wrap plots of mean Y2 & M2 models  
```{r wrap plots for mean Y & M at time2}
ggarrange(meanY2.plot,meanM2.plot)
```
<br>

### Wrap model plots for mean colors and hue at time1 and time2
```{r wrap plots for mean colors and hue, out.width='100%'}
meanColorMdlWrap <- ggarrange(meanY.plot,meanM.plot,hue1Mdl.plot, meanY2.plot,meanM2.plot,hue2Mdl.plot)
meanColorMdlWrap
#ggsave("meanColorMdlWrap.png", plot = meanColorMdlWrap, device = "png", dpi = 300, width = 10, height = 8)
```
<br>


### Include older birds at time 1
<br> 

Data frame including birds 23-33 days old
```{r older birds (23-33) dataframe}
older.mc <- allAges.mc %>% filter(between(age,23,33))
#create mass/tarsus ratio column
older.mc$ratio <- older.mc$mass/older.mc$tarsus
```
<br>

Mean yellow 1 model with older birds
```{r older birds meanY1 model}
olderMeanY.mdl <- lmer(meanY1 ~ age + ratio + sex + 
                        bodTemp1 + ambTemp1 + timeOut1 + (1|family), 
                    data = older.mc, REML = FALSE)
```

Plot mean yellow 1 model with older birds
```{r plot older birds meanY1 model}
olderMeanY.plot <- plot_model(olderMeanY.mdl,
           title = "mean yellow model with older birds",
           bpe = "median",
           vline.color = "black",
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1.2)
```
<br>

Mean magenta 1 model with older birds
```{r older birds meanM1 model}
olderMeanM.mdl <- lmer(meanM1 ~ age + ratio + sex + 
                        bodTemp1 + ambTemp1 + (1|family), 
                    data = older.mc, REML = FALSE)
```

Plot mean magenta 1 model with older birds
```{r plot older birds meanM1 model}
olderMeanM.plot <- plot_model(olderMeanM.mdl,
           title = "mean magenta model with older birds",
           bpe = "median",
           vline.color = "black",
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1.2)
```
<br>

Wrap mean colors with older birds models
```{r wrap plots of older birds mean models}
ggarrange(olderMeanY.plot,olderMeanM.plot,meanY.plot,meanM.plot)
```
<br>

## Create age bins factor for older bird data frame
<br>

```{r age bins for older}
#define bin breaks
binBreaks <- c(22,25,28,33) #define breaks
#name bins
bins <- c("bin1","bin2","bin3") #label bins
#assign age variable to bins
older.mc$ageBins <- cut(older.mc$age,breaks = binBreaks,labels = bins) #vectorize
#create a new column for age bins
older.mc$ageBins <- as.factor(older.mc$ageBins)
#checkBins <- data.frame(older.mc$id, older.mc$age, older.mc$ageBins)
```
<br>


```{r meanY ageBin model}
ageBinsMeanY.mdl <- lmer(meanY1 ~ ageBins + ratio + sex + 
                        bodTemp1 + ambTemp1 + timeOut1 + (1|family), 
                    data = older.mc, REML = FALSE)
```

```{r plot meanY model}
ageBinsMeanY.plot <- plot_model(ageBinsMeanY.mdl,
           title = "age bin mean yellow model",
           bpe = "median",
           vline.color = "black",
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1.2)
```

```{r wrap plots for age bin models}
ggarrange(olderMeanY.plot, ageBinsMeanY.plot)
```
<br>

Birds in the oldest category (29-33) are driving the negative age effect. 
<br>


Comparison of model fit for continuous age and age bin models
```{r age bin model comparison}
ageBins.mdls <- c(olderMeanY.mdl, ageBinsMeanY.mdl)
ageBins.modnames <- c("continuous age", "age bins")
confset(ageBins.mdls, modnames = ageBins.modnames, method = "ordinal")
```
There's no difference in the model probabilities. 
<br>




