---
title: "CB-mouthColor_junk"
output: html_document
---

```{r libraries, message=FALSE, warning=FALSE}
library(RColorBrewer); #brewer.pal(n=8, name = "Dark2") #;display.brewer.pal(n = 8, name = "Dark2")
library(tidyverse); theme_set(theme_classic()) #ggplot2, dplyr, tibble, etc.
library(plotly) #use ggplotly() for interactive plots with scoll-over IDs
library(knitr) #use kable() to make formatted tables
library(kableExtra)
library(Rtsne)
library(glmmTMB)
library(lme4)
library(sjPlot)
library(ggpubr) #ggarrange() figure wraps
library(plyr)
library(ggeffects) #ggpredict
library(rstanarm) #stan models
library(shinystan) #stan model evaluation >launch_shinystan_demo()
library(loo) #loo() to compare fits between bayesian models
library(MuMIn) #dredge, model averaging
library(AICcmodavg) #aictab() for AICc model comparisons
library(coin) #permutation test for ratios with independence_test()
library(janitor) #get_dupes() finds and prints duplicates
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
olderBirds <- mc %>% filter(age>28)

olderBirds <- olderBirds %>% 
  select(id, age, bodTemp1, ambTemp1)

summary(lm(bodTemp1~ambTemp1, data = olderBirds))

olderBirds %>%  
  ggplot(aes(x=ambTemp1, y=bodTemp1))+
  geom_point()

mean(olderBirds$bodTemp1)
```

### <b>Read in mouth color data (mc)</b>
<br>
<b>Replace zeros with NAs, sort and filter by age (23-27)</b>
```{r mouth color dataframe}
mc=tibble(read.csv("CB-mouthColor.csv", h=T)) #N=225
#replace zeros with NAs in morphometrics 
mc[mc==0] <- NA
#sort by year > family > id
mc <- mc %>% arrange(year, family, id) #N=225
#filter to include only ages 23-27
mc <- mc %>% filter(between(age,23,27)) #N=141
mc <- mc %>% drop_na(sex) #N=138
```
<br>

<b>Identify duplicate records in mc</b>
```{r find and remove duplicate records in mc}
mc %>% get_dupes(id)
```
For these duplicate records, one record for each individual is missing time 2 measurements. Therefore, I am keeping
only the complete record for each individual.
Removed = 42 ROWA04 (row 137), 53 ROWA04 (row 138), 64 ROWA04 (row 139), 75 ROWA04 (row 140)
```{r}
mc <- mc[-c(62,67,72,78),]#N=134
#mc %>% get_dupes() #double check...yep, no duplicates
```

<b>Create subsets of mc for females (N=80) and males (N=54) only</b>
```{r subset mc by sex}
#females only
female.mc <- mc %>% 
  filter(sex == "F") #N=80
#males only
male.mc <- mc %>% 
  filter(sex == "M") #N=54
```
<br>

### <b>Read in nestling morphometrics data (nm)</b>
<br>
<b>Nestling morphometrics are being used here to boost sample size for calculating mass/tarsus residuals</b>
<br>
<b>Replace zeros with NAs, sort and filter by age (23-27)</b> 
```{r nestling morphometrics dataframe}
nm=tibble(read.csv("nestlingMorph.csv", h=T))
#replace zeros with NAs in morphometrics 
nm[nm==0] <- NA
#remove nestlingMeasurementNumber
nm <- nm[,-1]
#sort by year > nestName > id
nm <- nm %>% arrange(year, nestName ,id)
#filter to include only ages 23-27
nm <- nm %>% filter(between(age, 23, 27)) 
```
<br>

<b>Create subset of nm including only sexed birds (N=503; females=268; males=235)</b>
```{r subset nm for sexed birds}
#subset nm to include only sexed birds and remove NAs from mass & tarsus
sexed.nm <- nm %>% drop_na(sex, tarsus, mass) #N=503
#make sex a factor rather than character
sexed.nm$sex <- as.factor(sexed.nm$sex)
#females only 
female.nm <- sexed.nm %>% 
  filter(sex == "F") #N=268
#males only
male.nm <- sexed.nm %>% 
  filter(sex == "M") #N=235
```
<br>

### <b>Do we need to control for repeated measurements of birds in mass~tarsus.mdl?</b>
<br>
The code below compares a linear model (lm) and a linear mixed effects model (lmer), which controls for repeated
measurements of the same birds during multiple climbs.  
<br>

### 1. Use lm() to run linear model with no random effects
<br>

<b>Run lm() and plot residuals</b>
```{r do we control repeated id}
noRandId.mdl_outliers <- lm(mass~tarsus, data = nm)
plot(noRandId.mdl_outliers)
```
<br>

Residual plots identify the following individuals as outliers.
```{r}
nm[c(437,743,1012,1038,1514),c(5,10,22)] %>% 
  kbl() %>% 
  kable_paper("hover", full_width = F, position = "left")
```
<br>

<b>Remove the identified outliers, rerun lm() and plot residuals again</b>
```{r do we control repeated id (remove outliers)}
tarsusMass.nm <- nm[-c(437,743,1012,1038,1514),] #n=1531 (five birds removed confirmed)
#drop NAs from tarsus and mass
tarsusMass.nm <- drop_na(tarsusMass.nm, tarsus, mass) #N=1513
noRandId.mdl2 <- lm(mass~tarsus, data = tarsusMass.nm)
plot(noRandId.mdl2)
```
<br>
Residual distributions improved

<br>
<b>Model summary</b>
```{r}
summary(noRandId.mdl2)
#   kbl(caption = "Linear Model: mass tarsus index") %>% 
#   kable_classic(full_width = F, position = "left", html_font = "Cambria")
```
<br>

### 2. Use lmer() to run a mixed effects model that controls for birds with repeated measurements
<br>
We can only directly compare results from a linear model and a linear mixed effects model by using regular Maximum Likelihood (ML). However, the default likelihood estimation for lmer() models Random Effects Maximum Likelihood (REML). 
<br>
https://stackoverflow.com/questions/24019807/how-to-compare-a-model-with-no-random-effects-to-a-model-with-a-random-effect-us 

<br>
The lmer() argument 'REML=FALSE' implements ML estimation instead. 

<b>We use the same dataframe as above, age filtered, no NAs and outliers already removed</b>
```{r}
randId.mdl <- lmer(mass~tarsus + (1|id), data = tarsusMass.nm, REML = FALSE)
plot(randId.mdl, col="black")
```

Residual distribution looks good.


<br>
<b>Summary of mixed effect model</b>
```{r}
summary(randId.mdl)
```
<br>

<b>Now, directly compare the lm() and lmer() models</b>
```{r}
AIC(noRandId.mdl2,randId.mdl) %>% 
  kbl(caption = "lm() vs. lmer(): mass~tarsus") %>% 
  kable_classic(full_width = F, position = "left", html_font = "Cambria")
```
<br>
lmer() model does a better job at explaining variance with the inclusion of a random effect 

<br>
### Plot--weight by tarsus: no sex filter (N=1513)
```{r Plot--weight~tarsus}
tarsusMass.nm %>% 
  ggplot(aes(x=tarsus,y=mass,color=as.factor(age)))+
  geom_point(alpha=0.5)+
  scale_color_brewer(palette = "Set1")
```
<br>

## Sex specific saturation models
<br>

### Female only saturation 1 model
```{r}
femaleSat1.mdl <- lmer(sat1 ~ age + residuals + bodTemp1 + ambTemp1 + timeOut1 + (1|family), 
                       data = female.mc)
summary(femaleSat1.mdl)
```
<br>
```{r}
plot_model(femaleSat1.mdl,
           title = "Female saturation 1 model",
           bpe = "median",
           vline.color = "black",
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1.2)
```
```{r female sat1 model confint}
confint(femaleSat1.mdl)
```
<br>

### Bayesian female sat1 model
```{r female sat 1 stan_glmer}
stan_femaleSat1.mdl <- stan_glmer(sat1~age + residuals + 
                                    bodTemp1 + ambTemp1 + timeOut1 + (1|family), 
           data = female.mc, algorithm = "sampling",iter = 6000,
           prior = normal(), prior_intercept = normal(),chains = 10,seed = 12345)
```

```{r}
summary(stan_femaleSat1.mdl)
```

```{r}
plot_model(stan_femaleSat1.mdl,
           title = "Bayesian female sat1 model",
           bpe = "median",
           vline.color = "black",
           prob.inner = .50,
           prob.outer = .80,
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1)
```


### Male only saturation 1 model
```{r male sat1 model}
maleSat1.mdl <- lmer(sat1~age + residuals + 
                       bodTemp1 + ambTemp1 + timeOut1 + (1|family), data = male.mc)
summary(maleSat1.mdl)
```
<br>

```{r male saturation 1 plot_model}
plot_model(maleSat1.mdl,
           title = "Male saturation 1 model",
           bpe = "median",
           vline.color = "black",
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1.2)
```
<br>
```{r male sat1 model confint}
confint(maleSat1.mdl)
```
<br>


### Bayesian male saturation 1 model
```{r sat 1 model both sexes}
stan_maleSat1.mdl <- stan_glmer(sat1~age + residuals + bodTemp1 + ambTemp1 + timeOut1 + (1|family), 
           data = male.mc, algorithm = "sampling", iter = 5000,
           prior = normal(), prior_intercept = normal(),chains = 10,seed = 12345)
summary(stan_maleSat1.mdl)
```

```{r}
plot_model(stan_maleSat1.mdl,
           title = "Bayesian male sat1 model",
           bpe = "median",
           vline.color = "black",
           prob.inner = .50,
           prob.outer = .80,
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1)
```
<br>

### Bayesian sat 1 model with sexes combined (sex included as a random effect)

```{r}
stan_Sat1.mdl <- stan_glmer(sat1~age + residuals + bodTemp1 + ambTemp1 + (1|family) + (1|sex), 
           data = mc, algorithm = "sampling",iter = 6000,
           prior = normal(), prior_intercept = normal(),chains = 10,seed = 12345)
```

```{r}
summary(stan_Sat1.mdl)
```

```{r}
plot_model(stan_Sat1.mdl,
           title = "Bayesian sat1 model",
           bpe = "median",
           vline.color = "black",
           prob.inner = .50,
           prob.outer = .80,
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1)
```
```{r}
plot_model(stan_Sat1.mdl,
           terms = "residuals",
           title = "Bayesian sat1 model",
           bpe = "median",
           vline.color = "black",
           prob.inner = .50,
           prob.outer = .80,
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1)
```
```{r}
checkParms(stan_Sat1.mdl)
```


```{r}
write.csv(mc, "CB-mouthColor_040521.csv")
```

```{r}
sat2_stan.mdl <- stan_glmer(sat2 ~ age + ratio + sex + bodTemp2 + ambFinal + timeOut2 + (1|family), 
                    data = time2.df, algorithm = "sampling", iter = 5000,
           prior = normal(), prior_intercept = normal(),chains = 10,seed = 12345)
```
<br>

```{r}
plot_model(sat2_stan.mdl)
```

```{r}
hue2_stan.mdl <- stan_glmer(hue2*100 ~ age + ratio + sex + bodTemp2 + ambTemp2 + timeOut2 + (1|family), 
                    data = time2.df, algorithm = "sampling", iter = 5000,
           prior = normal(), prior_intercept = normal(),chains = 10,seed = 12345)
```

```{r}
plot_model(hue2_stan.mdl)
```
<br>

Modeling the difference between body temp and 41 degrees, which is the mean body temp for birds > 28 days old. We chose this age range since these mature nestlings should have had an easier time maintaining an 'ideal' body temp. 
```{r bodyTemp-41 model}
#calculate the difference between each birds body temp and 41 degrees (mean of birds >28 days of age)
mc$tempDiff <- mc$bodTemp1-41
#model including tempDiff
diffTemp.mdl <- lmer(sat1 ~ age + resids + tempDiff + (1|family), data = mc, REML = FALSE)
summary(diffTemp.mdl)
```
```{r bodyTemp-41 plot_model}
plot_model(diffTemp.mdl,
           title = "Both sexes saturation 1",
           bpe = "median",
           vline.color = "black",
           show.values = TRUE, 
           value.offset = .3,
           line.size = 1.2)
```


<b>Examine whether brood size affects body temp</b>
<br>

Plotting body temp by brood size
```{r Does brood size affect body temp}
bodyTempByBroodSize.plot <- mc %>% 
  ggplot(aes(x=broodSize,y=bodTemp1, 
             group=as.factor(broodSize), color=as.factor(broodSize),
             label=id))+
  geom_boxplot()+
  geom_jitter()+
  scale_color_brewer(palette = "Dark2")
ggplotly(bodyTempByBroodSize.plot)
```

<br>
```{r brood size model}
summary(lm(bodTemp1~as.factor(broodSize), data = mc))
```
<br>

Plotting relationship between sat and hue
```{r}
mc$satT <- mc$sat1/155
mc$hueT <- mc$hue1/0.765

```

```{r}
hueSat.plot <- mc %>% ggplot(aes(x=satT, y=hueT, color=sex,label=id))+
  geom_jitter()+
  geom_smooth()
ggplotly(hueSat.plot)
```

```{r}
hueSex.plot <-mc %>% ggplot(aes(x=sex, y=hueT, label=id))+
  geom_jitter()+
  geom_boxplot()
ggplotly(hueSex.plot)
```
