---
title: "CB-mouthColor"
author: "Justin Mann"
date: "3/19/2021"
output: html_document
---

```{r libraries, message=FALSE, warning=FALSE}
library(tidyverse) #ggplot2, dplyr, tibble, etc.
library(plotly) #use ggplotly() for interactive plots with scoll-over IDs
library(knitr) #use kable() to make formatted tables
library(Rtsne)
library(glmmTMB)
library(lme4)
library(sjPlot)
library(ggpubr) #ggarrange() figure wraps
library(plyr)
library(ggeffects) #ggpredict
library(rstanarm) #stan models
library(shinystan) #stan model evaluation >launch_shinystan_demo()
library(loo) #loo() to compare fits between bayesian models
library(MuMIn) #dredge, model averaging
library(AICcmodavg) #aictab() for AICc model comparisons
library(RColorBrewer)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
brewer.pal(n=8, name = "Dark2"); #display.brewer.pal(n = 8, name = "Dark2")
theme_set(theme_classic())
```

## full dataset (df)

```{r dataframe}
df=tibble(read.csv("CB-mouthColor.csv", h=T))
```
<br>

Full model for Saturation 1
```{r full saturation 1 model}
#checked age * tarsus interaction...not significant
sat1_full.mdl <- lmer(sat1 ~ weight + age + tarsus + sex + bodTemp1 + ambTemp1 + timeOut1 + (1|family), 
                 data = df, REML = FALSE)

summary(sat1_full.mdl)
```

Confidence intervals for Full Saturation 1 model
```{r}
confint(sat1_full.mdl)
```


```{r}
#plot model with sex
plot_model(sat1_full.mdl,
           title = "Saturation 1")
```
<br>

```{r}
#plot model without sex to view the smaller confidence intervals 
plot_model(sat1_full.mdl, 
           title = "Saturation 1",
           rm.terms = c("sex [F]","sex [M]"))
```
<br>

Reduced models: fixed effects removed based on confidence intervals from the full model
```{r reduced models}
#sex random effect 
sat1_rsex.mdl <- lmer(sat1 ~ weight + age + tarsus + bodTemp1 + ambTemp1 + (1|sex), 
                 data = df, REML = FALSE)
#remove timeOut
sat1_r1.mdl <- lmer(sat1 ~ weight + age + tarsus + sex + bodTemp1 + ambTemp1 + (1|family), 
                 data = df, REML = FALSE)
#remove ambTemp
sat1_r2.mdl <- lmer(sat1 ~ weight + age + tarsus + sex + bodTemp1 + (1|family), 
                 data = df, REML = FALSE)
#remove bodTemp
sat1_r3.mdl <- lmer(sat1 ~ weight + age + tarsus + sex + (1|family), 
                 data = df, REML = FALSE)
sat1_candset <- c(sat1_full.mdl,sat1_rsex.mdl,sat1_r1.mdl,sat1_r2.mdl,sat1_r3.mdl)
mdls <- c("full", "randSex", "r1", "r2", "r3")
aictab(sat1_candset, modnames = mdls, sort = TRUE)
```
AICc model selection shows that the full model is better fit than any of the reduced models. 
<br> 

In summary, weight is positively associated with saturation 1. Age and tarsus are both negatively associated with saturation 1. Sex, ambient temp, and body temp are not significantly associated with saturation 1.
