---
title: "CrowBase: exploring nestling morphometrics"
author: "Justin Mann"
date: "3/4/2021"
output: html_document
---

```{r message=FALSE, warning=FALSE}
library(tidyverse) #ggplot2, dplyr, tibble, etc.
library(knitr)
library(Rtsne)
library(usethis) #git integration
library(glmmTMB)
library(lme4)
library(ggpubr) #ggarrange() figure wraps
library(plyr)
library(ggeffects) #ggpredict
library(rstanarm) #stan models
library(shinystan) #stan model evaluation >launch_shinystan_demo()
library(loo) #loo() to compare fits between bayesian models
library(MuMIn) #dredge, model averaging
library(RColorBrewer) ; brewer.pal(n=8, name = "Dark2")#; display.brewer.pal(n = 8, name = "Dark2")
theme_set(theme_classic())
```


### Create full dataframe (df). 
```{r}
df <- tibble(read.csv("Nestlings1989-2018_no2011_WITH_AdultMeasurements_2001-2015.csv", h=T))
```

Add a new column with the number of occurrences of each individual in the dataset.
```{r}
df$indivCounts <- as.numeric(ave(df$id, df$id, FUN = length))
#sorted by ascending year and lifeStage (add sorting conditions with: ', variableName')
df <- df %>% arrange(year, lifeStage)
#make lifeStage a factor
df$lifeStage <- as.factor(df$lifeStage)
#check n for both life stages
length(df$lifeStage[df$lifeStage == "nestling"]) #4086 nestlings
length(df$lifeStage[df$lifeStage == "adult"]) #286 adults
```


### Create dataframe subsets.
```{r}
#only individuals with multiple measurements (mm) 
mm <- subset(df, df$indivCounts>1)
#only nestlings (ne)
ne <- subset(df, df$lifeStage == "nestling")
#only adults (ad)
ad <- subset(df, df$lifeStage == "adult")
```






# tSNE plots for morphometrics
```{r}
#subset morphometric data from .ne
nestlMorph.ne <- ne[,c(1:23)] #n=4086
#drop NAs
nestlMorph.ne <- drop_na(nestlMorph.ne)#n=1413
#filter ages
nestlMorph.ne <- nestlMorph.ne %>% filter(between(age, 20, 30))#n=1237
#create morphometric matrix
nestlMorph.mat <- as.matrix(nestlMorph.ne[,-c(1:10,22)])
#run tSNE
nestlMorph.tsne <- Rtsne(nestlMorph.mat)
```

```{r}
nestlMorphTsne.plot <- data.frame(x=nestlMorph.tsne$Y[,1],
                                 y=nestlMorph.tsne$Y[,2],
                                 nest=nestlMorph.ne$nest,
                                 population=nestlMorph.ne$population,
                                 sex=nestlMorph.ne$sexSummary,
                                 year=nestlMorph.ne$year)
```



### Clustering by year
```{r}
ggplot(nestlMorphTsne.plot, aes(x=x,y=y,color=as.factor(year)))+
  geom_point(size = 2)+
  xlab("Dimension 1")+
  ylab("Dimension 2")+
  theme(#legend.position="none",
        legend.title = element_text(size = 18, face = "bold"),
        axis.title.x = element_text(size = 18, face = "bold"),
        axis.text = element_text(size = 16),
        axis.title.y = element_text(size = 18, face = "bold"))
```



### Clustering by sex
```{r, echo=FALSE}
ggplot(nestlMorphTsne.plot, aes(x=x,y=y,color=sex))+
  geom_point(size = 2)+
  xlab("Dimension 1")+
  ylab("Dimension 2")+
  theme(#legend.position="",
        legend.title = element_text(size = 18, face = "bold"),
        axis.title.x = element_text(size = 18, face = "bold"),
        axis.text = element_text(size = 16),
        axis.title.y = element_text(size = 18, face = "bold"))
```



### Clustering by population
```{r, echo=FALSE}
ggplot(nestlMorphTsne.plot, aes(x=x,y=y,color=population))+
  geom_point(size = 2)+
  xlab("Dimension 1")+
  ylab("Dimension 2")+
  theme(#legend.position="",
        legend.title = element_text(size = 18, face = "bold"),
        axis.title.x = element_text(size = 18, face = "bold"),
        axis.text = element_text(size = 16),
        axis.title.y = element_text(size = 18, face = "bold"))
```



### Clustering by nest ID
```{r, echo=FALSE}
ggplot(nestlMorphTsne.plot, aes(x=x,y=y,color=nest))+
  geom_point(size = 2)+
  xlab("Dimension 1")+
  ylab("Dimension 2")+
  theme(legend.position="none",
        legend.title = element_text(size = 18, face = "bold"),
        axis.title.x = element_text(size = 18, face = "bold"),
        axis.text = element_text(size = 16),
        axis.title.y = element_text(size = 18, face = "bold"))
```


# Relationships between calculated ages and morphometrics


## CalcAge by weight  
```{r}
cAge_morphs.ne <- ne %>% filter(between(calcAge, 1,50))
cAge_morphs.ne$year <- as.factor(cAge_morphs.ne$year)

#filter out weights <=1
cAge_morphs.filter.ne <- cAge_morphs.ne %>% filter(weight >=1)
summary(cAge_morphs.ne$calcAge)
summary(cAge_morphs.filter.ne$weight)
#ageWtCheck <- as.data.frame(cbind(Wt = cAge_morphs.ne$weight, cAge = cAge_morphs.ne$calcAge))
```

```{r}
cAge_morphs.filter.ne %>% 
  ggplot(aes(x = calcAge, y = weight, color = as.factor(year)))+
  geom_point(shape = 1)+
  theme(legend.position = "none")
```


### Zoom in on cluster in the 24-30 day range
```{r}
wtMidCluster <- cAge_morphs.filter.ne %>% filter(between(calcAge, 24,30))
wtMidCluster %>% 
  ggplot(aes(x = calcAge, y = weight, color = as.factor(year)))+
  geom_point(shape = 1)+
  theme(legend.position = "none")

```

Decimal points come from the formula for age calculation. Should we be rounding to nearest day?



## CalcAge by tail length
```{r}
cAge_morphs.ne %>% 
  ggplot(aes(x = calcAge, y = tailLength, color = as.factor(year)))+
  geom_point(shape = 1)+
  theme(legend.position = "none")
  
```


### Zoom in on cluster in the 24-30 day range
```{r}
tailMidCluster <- cAge_morphs.ne %>% filter(between(calcAge, 24,30))
tailMidCluster %>% 
  ggplot(aes(x = calcAge, y = tailLength, color = year))+
  geom_point(shape = 1)+
  theme(legend.position = "none")

```



## CalcAge by 7th primary
```{r}
cAge_morphs.ne %>% 
  ggplot(aes(x = calcAge, y = sevenPrimary, color = as.factor(year)))+
  geom_point(shape = 1)+
  theme(legend.position = "none")
  
```


### Zoom in on cluster in the 24-30 day range
```{r}
primMidCluster <- cAge_morphs.ne %>% filter(between(calcAge, 24,30))
primMidCluster %>% 
  ggplot(aes(x = calcAge, y = sevenPrimary, color = year))+
  geom_point(shape = 1)+
  theme(legend.position = "none")

```



## CalcAge by tarsus
```{r}
cAge_morphs.ne %>% 
  ggplot(aes(x = calcAge, y = tarsus, color = as.factor(year)))+
  geom_point(shape = 1)+
  theme(legend.position = "none")
  
```


### Zoom in on cluster in the 24-30 day range
```{r}
tarsMidCluster <- cAge_morphs.ne %>% filter(between(calcAge, 24,30))
tarsMidCluster.filter <- tarsMidCluster %>% filter(between(tarsus, 20,100))
tarsMidCluster.filter %>% 
  ggplot(aes(x = calcAge, y = tarsus, color = year))+
  geom_point(shape = 1)+
  theme(legend.position = "none")

```
