---
title: "Nestlings and Climate"
author: "Justin Mann"
date: "2022-09-27"
output: html_document
---

```{r libraries, include=FALSE}
library(tidyverse)
library(dplyr)
library(zoo)
```

## CLIMOD2 Data for Cornell University Weather Station

<http://www.nrcc.cornell.edu/>

<http://climod2.nrcc.cornell.edu/>

```{r data frame}
df <- read.csv("IthacaWeatherData1990_2020.csv", h=TRUE)

#coerce climate variables to class numeric 
df$MaxTemp <- as.numeric(df$MaxTemp)
df$Precip <- as.numeric(df$Precip)
df$HDD <- as.numeric(df$HDD)
df$CDD <- as.numeric(df$CDD)
df$GDD <- as.numeric(df$GDD)
```

## Climate Metrics

Objective: to match data on climate conditions during:

-   Incubation (conditions for 19 days prior to hatch date)

-   Post-hatch (conditions for 1-11, 12-22, 23-33, and 34-44 days after hatch date)

### Metric 1: Post-hatch Max Temp

```{r MaxTempMean1_11}
#zoo::rollapply(): align = 'left' applies to the succeeding days, while align = 'right' applies to the preceding days  
?zoo::rollapply()

#An 11-day rolling window calculates the mean of MaxTemp for the next 11 days
df$MaxTempMean1_11 <- zoo::rollapply(df$MaxTemp, width=11, FUN=mean, align = 'left', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(mean=mean(df[1:11,7]),metric=df[1,16])
#mean() calculation should match metric
```

```{r}
print(df[1:11,7])
```

```{r MaxTempMean12_22}
#MaxTempMean for days 12-22
df$MaxTempMean12_22 <- dplyr::lead(df$MaxTempMean1_11, n = 11)

#Code check
c(mean=mean(df[12:22,7]), metric=df[1,17])#mean() calculation should match metric
```

```{r}
print(df[12:22,7])#11 values
```

```{r MaxTempMean23_33}
#MaxTempMean for days 23-33
df$MaxTempMean23_33 <- dplyr::lead(df$MaxTempMean12_22, n = 11)

#Code check
c(mean=mean(df[23:33,7]), metric=df[1,18])#mean() calculation should match metric
```

```{r}
print(df[23:33,7])#11 values
```

```{r MaxTempMean34_44}
#MaxTempMean for days 34-44
df$leadMax34_44 <- dplyr::lead(df$MaxTempMean23_33, n = 11)

#Code check
c(mean=mean(df[34:44,7]), metric=df[1,19])#mean() calculation should match metric
```

```{r}
print(df[34:44,7])#11 values
```

### Metric 2: Incubation Max Temp

```{r MaxTempMeanIncubation}
#MaxTemp mean for 19 days prior to hatch date
df$MeanMaxTempIncubation <- zoo::rollapply(df$MaxTemp, width=19, FUN=mean, align = 'right', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(mean=mean(df[1:19,7]), metric=df[19,20]) #mean() calculation should match metric
```

```{r}
print(df[1:19,7])#19 values
```

### Metric 3: Post-hatch Precipitation

```{r PrecipSum1_11}
df$PrecipSum1_11 <- zoo::rollapply(df$Precip, width=11, FUN=sum, align = 'left', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check 
c(sum=sum(df[1:11,10], na.rm = TRUE), metric=df[1,21]) #sum() calculation should match metric
```

```{r}
print(df[1:11,10])#11 values)
```

```{r PrecipSum12_22}
#PrecipSum column that is 11 days ahead
df$PrecipSum12_22 <- dplyr::lead(df$PrecipSum1_11, n = 11)

#Code check
c(sum=sum(df[12:22,10], na.rm = TRUE), metric=df[1,22]) #sum() calculation should match metric
```

```{r}
print(df[12:22,10])
```

```{r PrecipSum23_33}
#PrecipSum column that is 22 days ahead
df$PrecipSum23_33 <- dplyr::lead(df$PrecipSum12_22, n = 11)

#Code check
c(sum=sum(df[23:33,10], na.rm = TRUE), metric=df[1,23]) #sum() calculation should match metric
```

```{r}
print(df[23:33,10])#11 values
```

```{r PrecipSum34_44}
#PrecipSum column that is 33 days ahead
df$PrecipSum34_44 <- dplyr::lead(df$PrecipSum23_33, n = 11)

#Code check
c(sum=sum(df[34:44,10]), metric=df[1,24]) #sum() calculation should match metric
```

```{r}
print(df[34:44,10])#11 values
```

### Metric 4: Incubation Precipitation

```{r PrecipSumIncubation}
#PrecipSum column that looks back 19 days from hatch date
df$PrecipSumIncubation <- zoo::rollapply(df$Precip, width=19, FUN=sum, align = 'right', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(sum=sum(df[1:19,10], na.rm = TRUE), metric=df[19,25]) #sum() calculation should match metric
```

```{r}
print(df[1:19,10])#19 values
```

### Metric 5: Post-hatch Growing Degree Days

```{r GDDSum1_11}
#GDDSum column the first 11 days 
df$GDDSum1_11 <- zoo::rollapply(df$GDD, width=11, FUN=sum, align = 'left', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(sum=sum(df[112:122,15], na.rm = TRUE), metric=df[112,26]) #sum() calculation should match metric
```
```{r}
print(df[112:122,15])
```


```{r GDDSum12_22}
#GDDSum column that is 11 days ahead
df$GDDSum12_22 <- dplyr::lead(df$GDDSum1_11, n = 11)

#Code check
c(sum=sum(df[66:76,15], na.rm = TRUE), metric=df[55,27]) #sum() calculation should match metric
```
```{r}
print(df[66:76,15])
```


```{r GDDSum23_33}
#GDDSum column that is 22 days ahead
df$GDDSum23_33 <- dplyr::lead(df$GDDSum12_22, n = 11)

#Code check
c(sum=sum(df[66:76,15], na.rm = TRUE), metric=df[44,28]) #sum() calculation should match metric
```


```{r GDDSum34_44}
#GDDSum column that is 33 days ahead
df$GDDSum34_44 <- dplyr::lead(df$GDDSum23_33, n = 11)

#Code check
c(sum=sum(df[66:76,15], na.rm = TRUE), metric=df[33,29]) #sum() should match metric
```


### Metric 6: Incubation Growing Degree Days

```{r GDDSumIncubation}
#GDDSum for the 19 days preceding hatch date
df$GDDSumIncubation <- zoo::rollapply(df$GDD, width=19, FUN=sum, align = 'right', fill = NA, partial = TRUE, na.rm = TRUE)

#code check
c(sum=sum(df[111:129,15], na.rm = TRUE), metric=df[129,30]) #sum() should match metric
```
```{r}
print(df[111:129,15])#19 values
```


### Metric 7: Post-hatch Cooling Degree Days

```{r CDDSum1_11}
#CDDSum column the first 11 days 
df$CDDSum1_11 <- zoo::rollapply(df$CDD, width=11, FUN=sum, align = 'left', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(sum=sum(df[112:122,14], na.rm = TRUE), metric=df[112,31]) #sum() calculation should match metric
```
```{r}
print(df[112:122,14])#11 values
```


```{r CDDSum12_22}
#CDDSum column that is 11 days ahead
df$CDDSum12_22 <- dplyr::lead(df$CDDSum1_11, n = 11)

#Code check
c(sum=sum(df[66:76,14], na.rm = TRUE), metric=df[55,32]) #sum() calculation should match metric
```
```{r}
print(df[66:76,14])
```


```{r CDDSum23_33}
#CDDSum column that is 22 days ahead
df$CDDSum23_33 <- dplyr::lead(df$CDDSum12_22, n = 11)

#Code check
c(sum=sum(df[66:76,14], na.rm = TRUE), metric=df[44,33]) #sum() calculation should match metric
```


```{r CDDSum34_44}
#CDDSum column that is 33 days ahead
df$CDDSum34_44 <- dplyr::lead(df$CDDSum23_33, n = 11)

#Code check
c(sum=sum(df[66:76,14], na.rm = TRUE), metric=df[33,34]) #sum() should match metric
```


### Metric 8: Incubation Cooling Degree Days

```{r CDDSumIncubation}
#CDDSum for the 19 days preceding hatch date
df$CDDSumIncubation <- zoo::rollapply(df$CDD, width=19, FUN=sum, align = 'right', fill = NA, partial = TRUE, na.rm = TRUE)

#code check
c(sum=sum(df[111:129,14], na.rm = TRUE), metric=df[129,35]) #sum() should match metric
```
```{r}
print(df[111:129,14])#19 values
```



```{r new dataframe}
#New dataframe with the derived climate metrics
ClimateMetrics.df <- as.data.frame(df[60:11514,c(1:7,10,14:35)])
```

```{r}
# write.csv(ClimateMetrics.df, "C:\\Users\\Justin Mann\\Documents\\RProjects\\CrowBase\\ClimateMetrics.csv",
#            row.names = FALSE)
```
