---
title: American Crow nestling morphology responds to yearly fluctuations in temperature
  and precipitation
author: "Justin Mann"
date: "`r Sys.Date()`"
output: html_document
---

```{r libraries, results="hide", warning=FALSE, message=FALSE}
library(tidyverse)
library(ggpubr) #ggarrange for plot wraps
library(bbmle) #AICtab() for model comparison
library(DHARMa) #model validation functions
library(DHARMa) #Model validation
library(mgcv)
library(mgcViz)

theme_set(theme_classic()) #default plots with no gridlines
```


This color palette was developed to ensure that individuals with colorblindness can see the contrast between all color combinations.

```{r colorblind accessible pallet}
colorBlindPal  <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
                       "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```


## Import Nestling Data

```{r unscaled data}
df <- read.csv("CrowNestlingClimate_UnscaledData_7.8.23.csv", h=TRUE)
# n=2030 nestlings
df$TBSWeightRatio <- df$TBS/df$Weight # adding a vector to hold the ratio of Total Bill Surface Area (TBS) to Weight
head(df)
```


## Import Weather Data

```{r clim.df}
clim_df <- read.csv("ClimateMetrics_AllMonths1989-2022.csv", h=T)
```


## Data Scaling

### Normalize Continuous Data

For each continuous vector, subtract each value from the mean (center) and divide it by the standard deviation. Since the continuous data were collected in a variety of units with different orders of magnitude, scaling the continuous data results in better fit models.

```{r scaling}
#categorical data  
categorical_df <- df[,1:11]

#continuous data
continuous_df <- df[,12:47]

#scale continuous data
#?scale()
scaled_mat <- scale(continuous_df, center = TRUE, scale = TRUE)

#join unscaled and scaled data
scaled_df <- cbind(categorical_df,scaled_mat)
```

## Data frames for males, females and unknown sex

I then subset the full data frame by sex to allow for modeling of the sexes separately.

```{r sexes data frames}
#Males scaled
M_scaled_df <- subset(scaled_df, Sex=="M")
#Males unscaled
M_df <- subset(df, Sex=="M")

#Females scaled
F_scaled_df <- subset(scaled_df, Sex=="F")
#Females unscaled
F_df <- subset(df, Sex=="F")

#Unsexed scaled
U_scaled_df <- subset(scaled_df, Sex=="U")
#Unsexed unscaled
U_df <- subset(df, Sex=="U")

#Both sexes scaled
B_scaled_df <- rbind(F_scaled_df,M_scaled_df)
#Both sexes unscaled
B_df <- rbind(F_df,M_df)
```


## Summarizing Weather across Years

Here, I use dplyr functions to manipulated the climate data frame and create a subset that includes the months when crows are breeding in Ithaca.

```{r breedingClim_df}
clim_df$Date <- as.Date(clim_df$Date)
clim_df$Month <- lubridate::month(clim_df$Date)
clim_df <- clim_df %>% 
  relocate(Month, .after = Year)
breedingClim_df <- clim_df %>% #filtering weather data to include only 1 March-30 June
  filter(between(Month, 3,6)) %>% 
  filter(between(JulDay, 60,181))
```

## Plotting minimum temperature and precipitation during the breeding season across years

```{r plot median min temp}
median(breedingClim_df$MinC, na.rm=TRUE)
min_plot <- ggplot(data = breedingClim_df, aes(x=as.factor(Year), y=MinC))+
  geom_boxplot()+
  geom_hline(yintercept = 3.89, color = "red", linetype = "dotted", linewidth = 1)+
  ylab("Minimum Temperature (C)")+
  xlab("")+
  theme(axis.text.x = element_text(angle = 90))
```


```{r plot precip}
median(breedingClim_df$PrecipCM, na.rm=TRUE)
precip_plot <- ggplot(data = clim_df, aes(x=as.factor(Year), y=PrecipCM))+
  geom_boxplot()+
  geom_hline(yintercept = 0.025, color = "red", linetype = "dotted", linewidth = 1)+
  ylab("Precipitation (cm)")+
  xlab("")+
  theme(axis.text.x = element_text(angle = 90))
```

```{r wrap climate plots, out.width='100%'}
BreedingClimate_wrap <- ggarrange(min_plot,precip_plot, ncol = 1)
BreedingClimate_wrap
```


### Weight by Minimum Temperature Plot

```{r WeightMinC_plot}
WeightMinC_plot <- ggplot(data = df, aes(x = MinC8_22, y = Weight, color = Sex))+
  geom_jitter(width = 0.2, shape = 1, size = 1.8)+
  geom_smooth(method="lm", aes(fill = Sex), alpha = 0.2)+
  scale_color_manual(name="",
                    values=c("#E69F00","#56B4E9","#000000"),
                    labels=c("Female","Male","Unsexed"))+
  scale_fill_manual(values = c("#E69F00","#56B4E9","#000000"), guide = "none")+
  ylab("Weight (g)")+
  xlab("Average minimum temperature (C)")+
  theme(plot.title = element_text(size = 16),
          axis.text.x = element_text(size = 12),
          axis.title.x = element_text(size = 14),
          axis.text.y = element_text(size = 14),
          axis.title.y = element_text(size = 14),
          legend.position = "top",
          plot.margin = margin(15,15,15,15))
suppressWarnings(print(WeightMinC_plot))
#cowplot::save_plot("Plots/WeightMinC_plot.png", WeightMinC_plot, base_height = 4, base_width = 7)
```


### Male Weight Model

```{r M_Weight_mdl}
M_Weight_mdl <- lm(Weight ~ MinC8_22 * PrecipSum8_22, data = M_scaled_df)
summary(M_Weight_mdl)
```


```{r M_Weight model validation}
M_Weight_simres <- simulateResiduals(M_Weight_mdl, n = 1000, plot = TRUE)
```

The nonsignificant KS test verifies that the distribution of the residuals is sufficiently normal (p = 0.0536); the nonsignificant Dispersion test verifies that the data are not over or under dispersed (0.932); and the nonsignificant Outlier test verifies that any outliers in the data are not significantly impacting the model results.


### Female Weight Model

```{r F_Weight_mdl}
F_Weight_mdl <- lm(Weight ~ MinC8_22 * PrecipSum8_22, data = F_scaled_df)
summary(F_Weight_mdl)
```


```{r F_Weight model validation}
F_Weight_simres <- simulateResiduals(F_Weight_mdl, n = 1000, plot = TRUE)
```


### All Nestlings Weight Model

```{r A_Weight_mdl}
A_Weight_mdl <- lm(Weight ~ MinC8_22 * PrecipSum8_22, data = scaled_df)
summary(A_Weight_mdl)
```


```{r A_Weight_mdl validation}
A_Weight_simres <- simulateResiduals(A_Weight_mdl, n = 1000, plot = TRUE)
```
