---
title: American Crow nestling morphology responds to yearly fluctuations in temperature
  and precipitation
author: "Justin Mann"
date: "`r Sys.Date()`"
output: html_document
---

```{r libraries, results="hide", warning=FALSE, message=FALSE}
library(tidyverse)
library(broom) #tidy() to create tibbles from model summaries
library(ggpubr) #ggarrange for plot wraps
library(bbmle) #AICtab() for model comparison
library(DHARMa) #model validation functions
library(mgcv)
library(mgcViz)

theme_set(theme_classic()) #default plots with no gridlines
```


This color palette was developed to ensure that individuals with colorblindness can see the contrast between all color combinations.

```{r colorblind accessible pallet}
colorBlindPal  <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
                       "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```


A function to created data frames needed to produce forest plots.

```{r dfs for fplot function}
fplot_df <- function(model, dataset, metric) {
  df <- tidy(model, quick = FALSE)
  ci <- as_tibble(confint(model))
  df$ci.lower <- ci$`2.5 %`
  df$ci.upper <- ci$`97.5 %`
  df$Dataset <- dataset
  df$Metric <- metric
  df <- df[-1,]
  return(df)
}
```


A function to create the forest plots.

```{r fplot function}
fplot <- function(metric) {
    ggplot(data = metric) +
        geom_errorbar(aes(x = term, ymin = ci.lower, ymax = ci.upper, color = Dataset),
                      linewidth = 1, width = 0.3, position = position_dodge(width = 0.4)) +
        geom_point(aes(x = term, y = estimate, color = Dataset), 
                   shape = 16, size = 3, position = position_dodge(width = 0.4)) +
        scale_color_manual(name = "", values = c("#000000", "#E69F00", "#56B4E9"),
                           labels = c("All", "Female", "Male")) +
        coord_flip() +
        geom_hline(yintercept = 0, color = "red", size = 1, linetype = "dotted") +
        scale_x_discrete(labels = c("Min Temp", "Min Temp * Precip", "Precip","Weight")) +
        ylab("Parameter estimate") +
        theme(plot.title = element_text(size = 16),
              axis.text.x = element_text(size = 12),
              axis.title.x = element_text(size = 14),
              axis.text.y = element_text(size = 14),
              axis.title.y = element_blank(),
              legend.position = "top",
              plot.margin = margin(15, 15, 15, 15))
}
```


## Import Nestling Data

```{r unscaled data}
df <- read.csv("CrowNestlingClimate_UnscaledData_7.8.23.csv", h=TRUE)
# n=2030 nestlings
df$TBSWeightRatio <- df$TBS/df$Weight # adding a vector to hold the ratio of Total Bill Surface Area (TBS) to Weight
head(df)
```


## Import Weather Data

```{r clim.df}
clim_df <- read.csv("ClimateMetrics_AllMonths1989-2022.csv", h=T)
```


## Data Scaling

### Normalize Continuous Data

For each continuous vector, subtract each value from the mean (center) and divide it by the standard deviation. Since the continuous data were collected in a variety of units with different orders of magnitude, scaling the continuous data results in better fit models.

```{r scaling}
#categorical data  
categorical_df <- df[,1:11]

#continuous data
continuous_df <- df[,12:47]

#scale continuous data
#?scale()
scaled_mat <- scale(continuous_df, center = TRUE, scale = TRUE)

#join unscaled and scaled data
scaled_df <- cbind(categorical_df,scaled_mat)
```

## Data frames for males, females and unknown sex

I then subset the full data frame by sex to allow for modeling of the sexes separately.

```{r sexes data frames}
#Males scaled
M_scaled_df <- subset(scaled_df, Sex=="M")
#Males unscaled
M_df <- subset(df, Sex=="M")

#Females scaled
F_scaled_df <- subset(scaled_df, Sex=="F")
#Females unscaled
F_df <- subset(df, Sex=="F")

#Unsexed scaled
U_scaled_df <- subset(scaled_df, Sex=="U")
#Unsexed unscaled
U_df <- subset(df, Sex=="U")

#Both sexes scaled
B_scaled_df <- rbind(F_scaled_df,M_scaled_df)
#Both sexes unscaled
B_df <- rbind(F_df,M_df)
```


## Summarizing Weather across Years

Here, I use dplyr functions to manipulated the climate data frame and create a subset that includes the months when crows are breeding in Ithaca.

```{r breedingClim_df}
clim_df$Date <- as.Date(clim_df$Date)
clim_df$Month <- lubridate::month(clim_df$Date)
clim_df <- clim_df %>% 
  relocate(Month, .after = Year)
breedingClim_df <- clim_df %>% #filtering weather data to include only 1 March-30 June
  filter(between(Month, 3,6)) %>% 
  filter(between(JulDay, 60,181))
```

## Plotting minimum temperature and precipitation during the breeding season across years

```{r plot median min temp}
median(breedingClim_df$MinC, na.rm=TRUE)
min_plot <- ggplot(data = breedingClim_df, aes(x=as.factor(Year), y=MinC))+
  geom_boxplot()+
  geom_hline(yintercept = 3.89, color = "red", linetype = "dotted", linewidth = 1)+
  ylab("Minimum Temperature (C)")+
  xlab("")+
  theme(axis.text.x = element_text(angle = 90))
```


```{r plot precip}
median(breedingClim_df$PrecipCM, na.rm=TRUE)
precip_plot <- ggplot(data = clim_df, aes(x=as.factor(Year), y=PrecipCM))+
  geom_boxplot()+
  geom_hline(yintercept = 0.025, color = "red", linetype = "dotted", linewidth = 1)+
  ylab("Precipitation (cm)")+
  xlab("")+
  theme(axis.text.x = element_text(angle = 90))
```

```{r wrap climate plots, out.width='100%'}
BreedingClimate_wrap <- ggarrange(min_plot,precip_plot, ncol = 1)
BreedingClimate_wrap
```


### Weight by Minimum Temperature Plot

```{r WeightMinC_plot}
WeightMinC_plot <- ggplot(data = df, aes(x = MinC8_22, y = Weight, color = Sex))+
  geom_jitter(width = 0.2, shape = 1, size = 1.8)+
  geom_smooth(method="lm", aes(fill = Sex), alpha = 0.2)+
  scale_color_manual(name="",
                    values=c("#E69F00","#56B4E9","#000000"),
                    labels=c("Female","Male","Unsexed"))+
  scale_fill_manual(values = c("#E69F00","#56B4E9","#000000"), guide = "none")+
  ylab("Weight (g)")+
  xlab("Average minimum temperature (C)")+
  theme(plot.title = element_text(size = 16),
          axis.text.x = element_text(size = 12),
          axis.title.x = element_text(size = 14),
          axis.text.y = element_text(size = 14),
          axis.title.y = element_text(size = 14),
          legend.position = "top",
          plot.margin = margin(15,15,15,15))
suppressWarnings(print(WeightMinC_plot))
#cowplot::save_plot("Plots/WeightMinC_plot.png", WeightMinC_plot, base_height = 4, base_width = 7)
```


### Male Weight Model

```{r M_Weight_mdl}
M_Weight_mdl <- lm(Weight ~ MinC8_22 * PrecipSum8_22, data = M_scaled_df)
summary(M_Weight_mdl)
```


```{r M_Weight model validation}
M_Weight_simres <- simulateResiduals(M_Weight_mdl, n = 1000, plot = TRUE)
```

The nonsignificant KS test verifies that the distribution of the residuals is sufficiently normal (p = 0.0536); the nonsignificant Dispersion test verifies that the data are not over or under dispersed (0.932); and the nonsignificant Outlier test verifies that any outliers in the data are not significantly impacting the model results.


### Female Weight Model

```{r F_Weight_mdl}
F_Weight_mdl <- lm(Weight ~ MinC8_22 * PrecipSum8_22, data = F_scaled_df)
summary(F_Weight_mdl)
```


```{r F_Weight model validation}
F_Weight_simres <- simulateResiduals(F_Weight_mdl, n = 1000, plot = TRUE)
```


### All Nestlings Weight Model

```{r A_Weight_mdl}
A_Weight_mdl <- lm(Weight ~ MinC8_22 * PrecipSum8_22, data = scaled_df)
summary(A_Weight_mdl)
```


```{r A_Weight_mdl validation}
A_Weight_simres <- simulateResiduals(A_Weight_mdl, n = 1000, plot = TRUE)
```


### Data frames for Weight Forest Plot

```{r Weight_dfs for fplot}
M_Weight_df <- fplot_df(M_Weight_mdl, "Male", "Weight")
F_Weight_df <- fplot_df(F_Weight_mdl, "Female", "Weight")
A_Weight_df <- fplot_df(A_Weight_mdl, "All", "Weight")

Weight_df <- rbind(M_Weight_df, F_Weight_df, A_Weight_df)
```

### Weight Forest Plot

```{r Weight_fplot}
Weight_fplot <- fplot(Weight_df)
Weight_fplot
```


### Weight Plots Wrapped

```{r Weight_wrap, out.width='100%'}
Weight_wrap <- ggarrange(WeightMinC_plot, Weight_fplot, ncol = 2, labels = c("A","B"), widths = c(1.6,1.4))
Weight_wrap
```

## How does weather affect nestling tarsus growth?

### Tarsus by Minimum Temperature Plot

```{r TarsusMinC_plot}
TarsusMinC_plot <- ggplot(data = df, aes(x = MinC8_22, y = Tarsus, color = Sex))+
  geom_jitter(width = 0.2, shape = 1, size = 1.8)+
  geom_smooth(method="loess", aes(fill = Sex), alpha = 0.2)+
  scale_color_manual(name="",
                    values=c("#E69F00","#56B4E9","#000000"),
                    labels=c("Female","Male","Unsexed"))+
  scale_fill_manual(values = c("#E69F00","#56B4E9","#000000"), guide = "none")+
  ylab("Tarsus (mm)")+
  xlab("Average minimum temperature (C)")+
  theme(plot.title = element_text(size = 16),
          axis.text.x = element_text(size = 12),
          axis.title.x = element_text(size = 14),
          axis.text.y = element_text(size = 14),
          axis.title.y = element_text(size = 14),
          legend.position = "top",
          plot.margin = margin(15,15,15,15))
suppressWarnings(print(TarsusMinC_plot))
```


### Male Tarsus Model

```{r M_Tarsus_mdl}
M_Tarsus_mdl <- glm(Tarsus ~ MinC8_22 * PrecipSum8_22 + Weight, data = M_scaled_df)
summary(M_Tarsus_mdl)
```

```{r M_Tarsus_mdl validation}
M_Tasus_simres <- simulateResiduals(M_Tarsus_mdl, n = 1000, plot = TRUE)
```
The male tarsus model fails the DHARMa outlier test. 


```{r M_Tarsus_gam_mdl}
M_Tarsus_gam_mdl <- gam(Tarsus ~ s(MinC8_22) + s(PrecipSum8_22) + te(MinC8_22, PrecipSum8_22) + s(Weight), family = scat, data = M_scaled_df)
summary(M_Tarsus_gam_mdl)
```
The GAM model recognizes a significantly non-linear effect of precipitation on male tarsus growth.


Using the getViz function from mgcViz package to view the partial effects of each model parameter.
```{r M_Tarsus_gam_mdl viz}
M_Tarsus_gam_viz <- getViz(M_Tarsus_gam_mdl)
plot(M_Tarsus_gam_viz)
```


