---
title: "Testing climwin"
author: "Justin Mann"
date: "`r Sys.Date()`"
output: html_document
---

```{r libraries, include=FALSE}
library(climwin)
library(tidyverse)
library(lubridate)
library(sjPlot) #plot_model & tab_model 
library(car) #vif
library(AICcmodavg) #aictab() for AICc model comparisons
```

## Testing sliding window approach used in Liu et al. 2023 J of Avian Biol

The goal is to identify the window of time that best explains variation in nestling morphometrics. In the context of our project, this program will detect the post-hatch time period ('window' of days) over which our nestling's bills are most responsive to climatic conditions. Mathematically, it's simply running the same model, with every possible sequence of days inside a user-defined window of time, and then comparing AIC values across all models.

```{r climwin packaged data}
egC.df <- MassClimate
egB.df <- Mass 
```
<br>

Anne has identified some more dubious nestlings. Waiting to hear back about which nestlings to remove, so the following analyses are just prototypes and could change. 

```{r our data}
#Nestling data sheet with updated climate metrics (C5-C20)
df <- read.csv("CrowNestlingClimate_AllNestlingsCleaned&ClimateJoinedNEW.csv", h=TRUE)

#coerce our date vector to an R date
df$Date <- as.Date(df$Date, format = "%m/%d/%Y")

#create a date that is 22 days post-hatch (climwin is built to look backwards from a specified date, not forwards)
df$PostHatch22Date <- df$Date + 22

#move variables in prep for scaling
df <- df %>% 
  relocate(CalcAge, .after = AllSex) %>% 
  relocate(PostHatch22Date, .after = Date)

#our climate data for 1989-2022
clim.df <- read.csv("ClimateMetrics_AllMonths1989-2022.csv", h=T)
#scale continuous 
clim.mat <- scale(clim.df[,5:14])
clim.scaled.df <- cbind(clim.df[,1:4],clim.mat)
```
<br>


## Normalizing continuous data

R's scale function subtracts each value from the mean (centers) and divide it by the standard deviation (scales).

```{r scaling data}

#?scale()

#Nestlings:
#separate categorical and continous data
categorical.df <- df[,1:10]
continuous.df <- df[,11:40]

#scale continuous data
scaled.mat <- scale(continuous.df, center = TRUE, scale = TRUE)

#rejoin unscaled and scaled data
scaled.df <- cbind(categorical.df,scaled.mat)

#data frame with only nestling data
nestl.scaled.df <- scaled.df[,1:22]

#Climate:
#scale continuous 
clim.mat <- scale(clim.df[,5:14])
clim.scaled.df <- cbind(clim.df[,1:4],clim.mat)
```
<br>


We want to identify the correct baseline model for the sliding window function to use. One outstanding question is whether the model should include weight AND age or just weight. Anne is concerned that age and weight might be explaining the same variation.
<br>


```{r date formatting for climwin compatability}

#1. format dates to dd/mm/yyyy with no leading zero on single digit days
#2. make cDate for climate data and bDate (biological date) for nestling data

clim.scaled.df$Date <- as.Date(clim.scaled.df$Date, format = "%m/%d/%Y")
clim.scaled.df$cDate <- format(strptime(clim.scaled.df$Date, format = "%Y-%m-%d"), "%d/%m/%Y")

#remove leading zero
clim.scaled.df$cDate <- str_remove(clim.scaled.df$cDate, "^0+")
#clim.scaled.df$cDate <- as.factor(clim.scaled.df$cDate)
clim.scaled.df <- clim.scaled.df %>% 
  relocate(cDate, .after = Date)

nestl.scaled.df$PostHatch22Date <- as.Date(nestl.scaled.df$PostHatch22Date, format = "%m/%d/%Y")
nestl.scaled.df$bDate <- format(strptime(nestl.scaled.df$PostHatch22Date, format = "%Y-%m-%d"), "%d/%m/%Y") 

#remove leading zero
nestl.scaled.df$bDate <- str_remove(nestl.scaled.df$bDate, "^0+")
#nestl.scaled.df$bDate <- as.factor(nestl.scaled.df$bDate)
nestl.scaled.df <- nestl.scaled.df %>% 
  relocate(bDate, .before = AllSex)
```
<br>


```{r data frame with only sexed nestlings}
#Males Scaled
M.scaled.df <- subset(scaled.df, AllSex=="M")
#Males Unscaled
M.df <- subset(df, AllSex=="M")

#Females Scaled
F.scaled.df <- subset(scaled.df, AllSex=="F")
#Females Unscaled
F.df <- subset(df, AllSex=="F")

#Both sexes scaled
B.scaled.df <- rbind(F.scaled.df,M.scaled.df)
#Both sexes unscaled
B.df <- rbind(F.df,M.df)
```
<br>


```{r female baseline models}
F.weight.mdl <- lm(data = F.scaled.df, BD ~ Weight)
F.age.mdl <- lm(data = F.scaled.df, BD ~ CalcAge)
F.ageWeight.mdl <- lm(data = F.scaled.df, BD ~ Weight + CalcAge)
F.ageWeightInter.mdl <- lm(data = F.scaled.df, BD ~ Weight * CalcAge)

F.null.mdls <- list(F.weight.mdl,F.age.mdl,F.ageWeight.mdl,F.ageWeightInter.mdl)
F.null.modnames <- c("F.weight.mdl","F.age.mdl","F.ageWeight.mdl","F.ageWeightInter.mdl")
aictab(cand.set = F.null.mdls, modnames = F.null.modnames)

#The model including age and weight shows no signs of variance inflation due to covariance 
vif(F.ageWeight.mdl)

F.plot_model(F.ageWeightInter.mdl,type = "int")
summary(F.ageWeightInter.mdl)
```
<br>

```{r male baseline models}
M.weight.mdl <- lm(data = M.scaled.df, BD ~ Weight)
M.age.mdl <- lm(data = M.scaled.df, BD ~ CalcAge)
M.ageWeight.mdl <- lm(data = M.scaled.df, BD ~ Weight + CalcAge)
M.ageWeightInter.mdl <- lm(data = M.scaled.df, BD ~ Weight * CalcAge)

M.null.mdls <- list(M.weight.mdl,M.age.mdl,M.ageWeight.mdl,M.ageWeightInter.mdl)
M.null.modnames <- c("M.weight.mdl","M.age.mdl","M.ageWeight.mdl","M.ageWeightInter.mdl")
aictab(cand.set = M.null.mdls, modnames = M.null.modnames)

#The model including age and weight shows no signs of variance inflation due to covariance 
vif(M.ageWeight.mdl)

plot_model(M.ageWeightInter.mdl,type = "int")
summary(M.ageWeightInter.mdl)
```
<br>


```{r tarsus slidingwin}
tarsus.window <- slidingwin(xvar = list(C10 = clim.df$C10),
           exclude = c(4,0), #exclude windows shorter than 4 days
           cdate = clim.scaled.df$cDate,
           bdate = nestl.scaled.df$bDate,
           baseline = lm(Tarsus ~ Weight + CalcAge, data = nestl.scaled.df),
           cinterval = "day",
           #k = 10, #cross validation improves confidence in Beta values, but drastically narrows delta AIC
           range = c(22,0),
           type = "relative",
           stat = "mean",
           func = "lin")
tarsus.window.out <- tarsus.window[[1]]$Dataset
tarsus.window$combos
tarsus.window[[1]]$Dataset
tarsus.window[[1]]$BestModel
medwin(dataset = tarsus.window.out, cw = 0.95)
```

```{r tarsus.window plot weights}
plotweights(dataset = tarsus.window[[1]]$Dataset, cw1 = 0.95, cw2 = 0.75, cw3 = 0.25)
```

<br>

```{r bill depth slidingwin}
bd.window <- slidingwin(xvar = list(C10 = clim.df$C10),
           exclude = c(4,0), #exclude windows shorter than 4 days
           cdate = clim.scaled.df$cDate,
           bdate = nestl.scaled.df$bDate,
           baseline = lm(BD ~ Weight + CalcAge, data = nestl.scaled.df),
           cinterval = "day",
           #k = 10, #cross validation improves confidence in Beta values, but drastically narrows delta AIC
           range = c(22,0),
           type = "relative",
           stat = "mean",
           func = "lin")
bd.window.out <- bd.window[[1]]$Dataset
bd.window$combos
bd.window[[1]]$Dataset
bd.window[[1]]$BestModel
medwin(dataset = bd.window.out, cw = 0.95)
```

```{r bd.window plot weights}
plotweights(dataset = bd.window[[1]]$Dataset, cw1 = 0.95, cw2 = 0.75, cw3 = 0.25)
```
<br>


```{r bill depth random window}
bd.randwindow <- randwin(xvar = list(C10 = clim.df$C10),
           exclude = c(4,0), #exclude windows shorter than 4 days
           window = "sliding",
           repeats = 50,
           cdate = clim.scaled.df$cDate,
           bdate = nestl.scaled.df$bDate,
           baseline = lm(BD ~ Weight, data = nestl.scaled.df),
           cinterval = "day",
           #k = 10, #cross validation improves confidence in Beta values, but drastically narrows delta AIC
           range = c(22,0),
           type = "relative",
           stat = "mean",
           func = "lin")
bd.randwindow
bd.window
```
<br>


```{r BD climwin pvalue}
data(MassRand)
MassRand
pvalue(datasetrand = bd.randwindow, dataset = bd.window, metric = "AIC",sample.size = 29)
```



```{r upper bill slidingwin}
ub.window <- slidingwin(xvar = list(C10 = clim.df$C10),
           exclude = c(4,0), #exclude windows shorter than 4 days
           cdate = clim.scaled.df$cDate,
           bdate = nestl.scaled.df$bDate,
           baseline = lm(UB ~ Weight, data = nestl.scaled.df),
           cinterval = "day",
           #k = 10, #cross validation improves confidence in Beta values, but drastically narrows delta AIC
           range = c(22,0),
           type = "relative",
           stat = "mean",
           func = "lin")
ub.window[[1]]$Dataset
ub.window[[1]]$BestModel
```
<br>

```{r upper bill surface area slidingwin}
ubs.window <- slidingwin(xvar = list(C10 = clim.df$C10),
           exclude = c(4,0), #exclude windows shorter than 4 days
           cdate = clim.scaled.df$cDate,
           bdate = nestl.scaled.df$bDate,
           baseline = lm(UBS ~ Weight, data = nestl.scaled.df),
           cinterval = "day",
           #k = 10, #cross validation improves confidence in Beta values, but drastically narrows delta AIC
           range = c(22,0),
           type = "relative",
           stat = "mean",
           func = "lin")
ubs.window[[1]]$Dataset
ubs.window[[1]]$BestModel
```
<br>


```{r bill nares to tip slidingwin}
bnt.window <- slidingwin(xvar = list(C10 = clim.df$C10),
           exclude = c(4,0), #exclude windows shorter than 4 days
           cdate = clim.scaled.df$cDate,
           bdate = nestl.scaled.df$bDate,
           baseline = lm(BNT ~ Weight, data = nestl.scaled.df),
           cinterval = "day",
           #k = 10, #cross validation improves confidence in Beta values, but drastically narrows delta AIC
           range = c(22,0),
           type = "relative",
           stat = "mean",
           func = "lin")
bnt.window$combos
bnt.window[[1]]$Dataset
bnt.window[[1]]$BestModel
```
<br>
