---
title: "Climate Metric Model Selection"
author: "Justin Mann"
date: "`r Sys.Date()`"
output: html_document
---

```{r libraries, include=FALSE}
library(tidyverse)
library(broom) #tidy() to create tibbles from model summaries
library(car) #vif (variance inflation factor for measuring covariance)
library(cowplot)
library(lme4) #frequentist models  
library(sjPlot) #plot_model & tab_model (blue = #377EB8)
library(ggpubr) #ggarrange for plot wraps
library(lmerTest) #lmerTest::step
library(ggeffects) #ggpredict
library(plotly) #ggplotly() to make interactive plots with scroll over ids
library(MuMIn) #dredge() for unsupervised model selection
library(AICcmodavg) #aictab() for AICc model comparisons
library(DHARMa) #model validation functions
library(DescTools) #Entropy() and MutInf()

#Libraries for Bayesian Models
library(rstanarm) #stan models
library(shinystan) #stan model evaluation
#launch_shinystan_demo()
library(loo) #use loo() to compare fits between bayesian models

#Clustering libraries
library(umap)
library(tsne)
library(ggfortify)#use autoplot() to visualize PCAs
library(stpm)#stochastic process model
theme_set(theme_classic()) #default plots with no gridlines
```

<br>

## Nestling Data and Climate metrics

```{r dataframe}
df <- read.csv("CrowNestlingClimate_AllNestlingsCleaned&ClimateJoined.csv", h=TRUE)
df <- df[,-1]
#n=2035 nestlings, 39 variables
```

<br>

A column to hold decade bins for plotting

```{r creating decade bins}
df$Decades <- cut(df$Year, breaks = c(1988,1999,2010,2018), labels = c("89-99","00-10","11-18"))
df <- df %>% relocate(Decades, .before = Year)
```

<br>

## Normalize Continuous Data

Subtract each value from the mean (center) and divide it by the standard deviation

```{r scaling}
#categorical data  
unScaled.df <- df[,1:11]

#continuous data
dataToScale.df <- df[,12:40]

#scale continuous data
#?scale()
scaled.mat <- scale(dataToScale.df, center = TRUE, scale = TRUE)

#join unscaled and scaled data
scaled.df <- cbind(unScaled.df,scaled.mat)
```

<br>

Summarize the unscaled data

```{r data summary }
summary(df)
```

<br>

Summarize the scaled data

```{r scaled data summary}
summary(scaled.df)
```

<br>

```{r data frame with only sexed nestlings}
#Males Scaled
M.scaled.df <- subset(scaled.df, AllSex=="M")
#Males Unscaled
M.df <- subset(df, AllSex=="M")

#Females Scaled
F.scaled.df <- subset(scaled.df, AllSex=="F")
#Females Unscaled
F.df <- subset(df, AllSex=="F")

#Both sexes scaled
B.scaled.df <- rbind(F.scaled.df,M.scaled.df)
#Both sexes unscaled
B.df <- rbind(F.df,M.df)
```

<br>

## Unsupervised model selection

### What climate metrics best explain variation in bill shape?

Since the strongest effects thus far have shown up in Time Period 2 (12-22 days post hatching), I'm going to use Time 2 for model selection tests.

```{r bill depth time 2 model selection}
#Min
MinTempBD.mdl <- lm(BD ~ MinTempMean12_22 * PrecipSum12_22 + CalcAge + Weight, data = scaled.df, na.action = "na.fail")
MaxTempBD.mdl <- lm(BD ~ MaxTempMean12_22 * PrecipSum12_22 + CalcAge + Weight, data = scaled.df, na.action = "na.fail")
GDDBD.mdl <- lm(BD ~ GDDSum12_22 * PrecipSum12_22 + CalcAge + Weight, data = scaled.df, na.action = "na.fail")
CDDBD.mdl <- lm(BD ~ CDDSum12_22 * PrecipSum12_22 + CalcAge + Weight, data = scaled.df, na.action = "na.fail")
HDDBD.mdl <- lm(BD ~ HDDSum12_22 * PrecipSum12_22 + CalcAge + Weight, data = scaled.df, na.action = "na.fail")
```

```{r bill depth time 2 model comparison}
BDTime2Models <- list(MinTempBD.mdl,MaxTempBD.mdl,GDDBD.mdl,CDDBD.mdl,HDDBD.mdl)
BDTime2ModelNames <- c('MinTempBD.mdl','MaxTempBD.mdl','GDDBD.mdl','CDDBD.mdl','HDDBD.mdl')
aictab(cand.set = BDTime2Models, modnames = BDTime2ModelNames, sort = TRUE)
```

Minimum Temperature Model fits the data best. GDD is second best, but the delta AICc is 11.43 between the two.

```{r MinTempBD.mdl summary}
summary(MinTempBD.mdl)
```

```{r MinTempBD prediction}
MinTemp.pred <- ggpredict(MinTempBD.mdl, type = "fe", terms = ~ MinTempMean12_22)
MinTemp.pred
```

```{r MinTempBD prediction plot}
ggplot(data = MinTemp.pred, aes(x,predicted))+
  geom_point(data = scaled.df, aes(x=MinTempMean12_22, y=BD))+
  geom_line(color = "red")+
  geom_ribbon(aes(ymin=conf.low,ymax=conf.high), fill = "red", alpha = 0.1)+
  scale_y_continuous(limits = c(-4,4))+
  xlab("Scaled Minimum Temperature")+
  ylab("Scaled Bill Depth")
```

<br>

```{r GDDBD.mdl summary}
summary(GDDBD.mdl)
```

```{r GDDBD prediction}
GDDBD.pred <- ggpredict(GDDBD.mdl, type = "fe", terms = ~ GDDSum12_22)
GDDBD.pred
```

```{r GDDBD prediction plot}
ggplot(data = GDDBD.pred, aes(x,predicted))+
  geom_point(data = scaled.df, aes(x=GDDSum12_22, y=BD))+
  geom_line(color = "red")+
  geom_ribbon(aes(ymin=conf.low,ymax=conf.high), fill = "red", alpha = 0.1)+
  ylab("Scaled Bill Depth")+
  xlab("Scaled GDD")

```
