---
title: "Morphometric comparison by sex"
author: "Justin Mann"
date: "`r Sys.Date()`"
output: html_document
---

```{r libraries, include=FALSE}
library(tidyverse)
library(broom) #tidy() to create tibbles from model summaries
library(car) #vif (variance inflation factor for measuring covariance)
library(cowplot)
library(lme4) #frequentist models  
library(sjPlot) #plot_model & tab_model (blue = #377EB8)
library(ggpubr) #ggarrange for plot wraps
library(lmerTest) #lmerTest::step
library(ggeffects) #ggpredict
library(plotly) #ggplotly() to make interactive plots with scroll over ids
library(MuMIn) #dredge() for unsupervised model selection
library(AICcmodavg) #aictab() for AICc model comparisons
library(DHARMa) #model validation functions
library(DescTools) #Entropy() and MutInf()

#Libraries for Bayesian Models
library(rstanarm) #stan models
library(shinystan) #stan model evaluation
#launch_shinystan_demo()
library(loo) #use loo() to compare fits between bayesian models

#Clustering libraries
library(umap)
library(tsne)
library(ggfortify)#use autoplot() to visualize PCAs
library(stpm)#stochastic process model
theme_set(theme_classic()) #default plots with no gridlines
```
<br>

## Nestling data and climate metrics

```{r dataframe}
df <- read.csv("CrowNestlingClimate_AllNestlingsCleaned&ClimateJoinedNEW.csv", h=TRUE)
df <- df[,-1]
#n=1786 nestlings, 46 variables
```
<br>

## Normalize Continuous Data

Subtract each value from the mean (center) and divide it by the standard deviation

```{r scaling}
#categorical data  
categorical.df <- df[,1:10]

#continuous data
continuous.df <- df[,11:46]

#scale continuous data
#?scale()
scaled.mat <- scale(continuous.df, center = TRUE, scale = TRUE)

#join unscaled and scaled data
scaled.df <- cbind(categorical.df,scaled.mat)
```
<br>


```{r data frame with only sexed nestlings}
#Males Scaled
M.scaled.df <- subset(scaled.df, AllSex=="M")
#Males Unscaled
M.df <- subset(df, AllSex=="M")

#Females Scaled
F.scaled.df <- subset(scaled.df, AllSex=="F")
#Females Unscaled
F.df <- subset(df, AllSex=="F")

#Both sexes scaled
B.scaled.df <- rbind(F.scaled.df,M.scaled.df)
#Both sexes unscaled
B.df <- rbind(F.df,M.df)
```
<br>

## Bill depth comparison between sexes

What is the mean bill depth of males and females?

```{r unscaled bill depth t test}
t.test(B.df$BD[B.df$AllSex=="M"], B.df$BD[B.df$AllSex=="F"])
```

<br>

Plot unscaled bill depth distributions for males and females with verticle lines showing the mean values.

```{r unscaled bill depth by sex plot}
ggplot(data = B.df, aes(x=BD, fill = AllSex))+
  geom_histogram(colour = "black", bins = 50)+
  geom_vline(xintercept = 12.55, color="#009E73", linetype="dashed", size=1)+
  geom_vline(xintercept = 12.98, color="#E69F00", linetype="dashed", size=1)+
  scale_fill_manual(values = c("#009E73","#E69F00"), labels = c("Female","Male"))
```

<br>

Plot the residuals of a scaled model showing how weight and age explain bill depth.

```{r scaled bill depth residuals by sex}
#Scaled BD 
BDNoSex.scaled.mdl <- lm(data = B.scaled.df, BD ~ Weight + CalcAge)
BDNoSex.summ <- summary(BDNoSex.scaled.mdl)
B.scaled.df$BDNoSex.resids <- BDNoSex.summ$residuals

ggplot(data = B.scaled.df, aes(x=BDNoSex.resids,fill=AllSex))+
  geom_histogram(colour = "black", bins = 100)+
  scale_fill_manual(values = c("#009E73","#E69F00"), labels = c("Female","Male"))+
  theme(plot.title = element_text(size = 22),
          axis.text.x = element_text(size = 12),
          axis.title.x = element_text(size = 14),
          axis.text.y = element_text(size = 12),
          axis.title.y = element_text(size = 14),
          legend.position = "top",
          plot.margin = margin(15,15,15,15))
```

```{r bill depth by weight scaled}
ggplot(data = B.scaled.df, aes(x=BD,y=BDNoSex.resids,color=AllSex))+
  geom_point()+
  scale_color_manual(values = c("#009E73","#E69F00"), labels = c("Female","Male"))+
  theme(plot.title = element_text(size = 22),
          axis.text.x = element_text(size = 12),
          axis.title.x = element_text(size = 14),
          axis.text.y = element_text(size = 12),
          axis.title.y = element_text(size = 14),
          legend.position = "top",
          plot.margin = margin(15,15,15,15))
```

```{r t test scaled bill depth residuals}
mean(B.scaled.df$BDNoSex.resids[B.scaled.df$AllSex=="M"])
mean(B.scaled.df$BDNoSex.resids[B.scaled.df$AllSex=="F"])
t.test(B.scaled.df$BDNoSex.resids[B.scaled.df$AllSex=="M"],B.scaled.df$BDNoSex.resids[B.scaled.df$AllSex=="F"])
```

<br>

```{r truncated bill depth residuals}
TruncBD.df <- B.scaled.df %>% filter(between(BD,-1,1))
t.test(TruncBD.df$BDNoSex.resids[TruncBD.df$AllSex=="M"],TruncBD.df$BDNoSex.resids[TruncBD.df$AllSex=="F"])
```

```{r truncated bill depth by bill depth residuals scaled}
ggplot(data = TruncBD.df, aes(x=BD,y=BDNoSex.resids,color=AllSex))+
  geom_point()+
  geom_jitter(width = 0.5)+
  scale_color_manual(values = c("#009E73","#E69F00"), labels = c("Female","Male"))+
  theme(plot.title = element_text(size = 22),
          axis.text.x = element_text(size = 12),
          axis.title.x = element_text(size = 14),
          axis.text.y = element_text(size = 12),
          axis.title.y = element_text(size = 14),
          legend.position = "top",
          plot.margin = margin(15,15,15,15))
```
<br>

## Tarsus comparisons between sexes

```{r unscaled tarsus t test}
t.test(B.df$Tarsus[B.df$AllSex=="M"], B.df$Tarsus[B.df$AllSex=="F"])
```

```{r unscaled tarsus by sex plot}
ggplot(data = B.df, aes(x=Tarsus, fill = AllSex))+
  geom_histogram(colour = "black", bins = 100)+
  geom_vline(xintercept = 58.006, color="#009E73", linetype="dashed", size=1)+
  geom_vline(xintercept = 59.9, color="#E69F00", linetype="dashed", size=1)+
  scale_fill_manual(values = c("#009E73","#E69F00"), labels = c("Female","Male"))
```

```{r scaled tarsus residuals by sex}
#Scaled tarsus 
TarsusNoSex.scaled.mdl <- lm(data = B.scaled.df, Tarsus ~ Weight + CalcAge)
TarsusNoSex.summ <- summary(TarsusNoSex.scaled.mdl)
B.scaled.df$TarsusNoSex.resids <- TarsusNoSex.summ$residuals

ggplot(data = B.scaled.df, aes(x=TarsusNoSex.resids,fill=AllSex))+
  geom_histogram(colour = "black", bins = 100)+
  scale_fill_manual(values = c("#009E73","#E69F00"), labels = c("Female","Male"))+
  theme(plot.title = element_text(size = 22),
          axis.text.x = element_text(size = 12),
          axis.title.x = element_text(size = 14),
          axis.text.y = element_text(size = 12),
          axis.title.y = element_text(size = 14),
          legend.position = "top",
          plot.margin = margin(15,15,15,15))
```

```{r tarsus by weight scaled}
ggplot(data = B.scaled.df, aes(x=Tarsus,y=TarsusNoSex.resids,color=AllSex))+
  geom_point()+
  scale_color_manual(values = c("#009E73","#E69F00"), labels = c("Female","Male"))+
  theme(plot.title = element_text(size = 22),
          axis.text.x = element_text(size = 12),
          axis.title.x = element_text(size = 14),
          axis.text.y = element_text(size = 12),
          axis.title.y = element_text(size = 14),
          legend.position = "top",
          plot.margin = margin(15,15,15,15))
```

```{r t test scaled tarsus residuals}
t.test(B.scaled.df$TarsusNoSex.resids[B.scaled.df$AllSex=="M"],B.scaled.df$TarsusNoSex.resids[B.scaled.df$AllSex=="F"])
```
<br>
