---
title: "Calculating Climate Metrics: conversions to metric, rolling means and sliding windows, oh my!"
author: "Justin Mann"
date: "2022-09-27"
output: html_document
---

```{r libraries, include=FALSE}
library(tidyverse)
library(dplyr)
library(zoo)
library(lubridate)
```

## CLIMOD2 Data for Cornell University Weather Station
8 Game Farm Rd, Ithaca, NY 14850
Station IDs:
304174 (Coop)
USC00304174 (GHCN)
ITHN6 (NWS LI)

<http://www.nrcc.cornell.edu/>

<http://climod2.nrcc.cornell.edu/>

```{r raw data}
# #Raw text file downloaded from climod2
# rawclim.df <- read.table("climod2data1989-2022.txt", sep = ",", header = TRUE)
# 
# #Make variables numeric (will coerce NAs where data are missing)
# rawclim.df$MaxTemp <- as.numeric(rawclim.df$MaxTemperature)
# which(is.na(rawclim.df$MaxTemp))#[1] 1535
# rawclim.df$MinTemp <- as.numeric(rawclim.df$MinTemperature)
# which(is.na(rawclim.df$MinTemp))#[1] 1440 1536 1853 4401
# 
# rawclim.df$Precip <- as.numeric(rawclim.df$Precipitation)
# rawclim.df$Snowfall <- as.numeric(rawclim.df$Snowfall)
# rawclim.df$SnowDepth <- as.numeric(rawclim.df$SnowDepth)  
```

```{r metric and celcius conversions}
# f2c <- function(x){
#   x <- (5/9) * (x-32)
#   return(x)
# }
# f2c(33)#[1] 0.556
# 
# rawclim.df$MaxC <- mapply(f2c, rawclim.df$MaxTemp)
# rawclim.df$MinC <- mapply(f2c, rawclim.df$MinTemp)
# 
# in2cm <- function(x){
#   x <- x * 2.54
#   return(x)
# }
# in2cm(0.1)#[1] 0.254
# 
# rawclim.df$PrecipCM <- mapply(in2cm, rawclim.df$Precip)
# rawclim.df$SnowfallCM <- mapply(in2cm, rawclim.df$Snowfall)
# rawclim.df$SnowDepthCM <- mapply(in2cm, rawclim.df$SnowDepth)
```


```{r new data frame}
# clim.df <- rawclim.df %>% 
#   select(Date,MaxC,MinC,
#          PrecipCM,SnowfallCM,SnowDepthCM)
# #add year column
# clim.df$Year <- lubridate::year(clim.df$Date)
# #add Julian Day
# clim.df$JulDay <- lubridate::yday(clim.df$Date)
# #pad Julian Day with zeros
# clim.df$JulDay <- str_pad(clim.df$JulDay, 3, pad = "0")
# #join padded Julian Days with Year
# my_cols <- c("Year", "JulDay")
# clim.df$HatchDateJulYear <- do.call(paste, c(clim.df[my_cols], sep = ""))
```
<br>


## Climate thesholds

Create biologically-relevant temperature thresholds  
```{r temperature thesholds}
#add daily mean column
# clim.df$MeanC <- (clim.df$MaxC + clim.df$MinC)/2
# 
# #add GDD column where daily mean temperatures are set relative to #10C
# clim.df$GDD10C <- clim.df$MeanC - 10
# 
# #add column where minimum temp relative to 1 C without mean
# clim.df$OneCMinusMinC <- 1 - clim.df$MinC
# 
# #make maximum temp relative to 10 C without mean
# clim.df$MaxCMinus10C <- clim.df$MaxC - 10

```

```{r move temp variables together}
# clim.df <- clim.df %>% 
#   relocate(c(MinC, MaxC), .after = SnowDepthCM) %>% 
#   relocate(c(Year, JulDay, HatchDateJulYear), .after = Date)
```

```{r write a new climate metric csv}
#write.csv(clim.df, "ClimateMetrics_AllMonths1989-2022.csv", row.names = FALSE)
```

```{r read in new climate metric csv}
clim.df <- read.csv("ClimateMetrics_AllMonths1989-2022.csv", h=T)
```
<br>

## Original first eleven days/second eleven days

### Maximum C rolling means
```{r Mean MaxC1_11}
#An 11-day rolling window calculates the mean of MaxC for post-hatch days 1-11
clim.df$MaxC1_11 <- zoo::rollapply(clim.df$MaxC, width=11, FUN=mean, align = 'left', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(mean=mean(clim.df[1:11,9]),metric=clim.df[1,14])
#mean() calculation should match metric
```

```{r Mean MaxC12_22}
#An 11-day rolling window calculates the mean of MaxC for post-hatch days 12-22
clim.df$MaxC12_22 <- dplyr::lead(clim.df$MaxC1_11, n = 11)

#Code check
c(mean=mean(clim.df[12:22,9]), metric=clim.df[1,15])#mean() calculation should match metric
```

```{r Mean MaxCIncubation}
#MaxC mean for 19 days prior to hatch date
clim.df$MaxCIncubation <- zoo::rollapply(clim.df$MaxC, width=19, FUN=mean, align = 'right', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(mean=mean(clim.df[1:19,9]), metric=clim.df[19,16]) #mean() calculation should match metric
```
<br>


### Minimum C rolling means
```{r MinC1_11}
#An 11-day rolling window calculates the mean of MinC for post-hatch days 1-11
clim.df$MinC1_11 <- zoo::rollapply(clim.df$MinC, width=11, FUN=mean, align = 'left', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(mean=mean(clim.df[1:11,8]),metric=clim.df[1,17])
#mean() calculation should match metric
```

```{r Mean MinC12_22}
#An 11-day rolling window calculates the mean of MinC for post-hatch days 12-22
clim.df$MinC12_22 <- dplyr::lead(clim.df$MinC1_11, n = 11)

#Code check
c(mean=mean(clim.df[12:22,8]), metric=clim.df[1,18])#mean() calculation should match metric
```

```{r MinCIncubation}
#MinC mean for 19 days prior to hatch date
clim.df$MinCIncubation <- zoo::rollapply(clim.df$MinC, width=19, FUN=mean, align = 'right', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(mean=mean(clim.df[1:19,8]), metric=clim.df[19,19]) #mean() calculation should match metric
```
<br>


### GDD10C rolling sums
```{r GDD10CSum1_11}
#An 11-day rolling window calculates the mean of GDDC10 for post-hatch days 1-11
clim.df$GDD10CSum1_11 <- zoo::rollapply(clim.df$GDD10C, width=11, FUN=sum, align = 'left', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(sum=sum(clim.df[1:11,11]),metric=clim.df[1,20])
#mean() calculation should match metric
```

```{r GDD10CSum12_22}
#An 11-day rolling window calculates the mean of GDDC10 for post-hatch days 12-22
clim.df$GDD10CSum12_22 <- dplyr::lead(clim.df$GDD10CSum1_11, n = 11)

#Code check
c(sum=sum(clim.df[12:22,11]), metric=clim.df[1,21])#mean() calculation should match metric
```

```{r GDD10CSumIncubation}
#C10 mean for 19 days prior to hatch date
clim.df$GDD10CSumIncubation <- zoo::rollapply(clim.df$GDD10C, width=19, FUN=sum, align = 'right', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(sum=sum(clim.df[1:19,11]), metric=clim.df[19,22]) #mean() calculation should match metric
```
<br>


### Precip rolling sums
```{r PrecipSum1_11}
#An 11-day rolling window calculates the mean of PrecipCM for post-hatch days 1-11
clim.df$PrecipSum1_11 <- zoo::rollapply(clim.df$PrecipCM, width=11, FUN=sum, align = 'left', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(sum=sum(clim.df[1:11,5], na.rm = T),metric=clim.df[1,23])
#mean() calculation should match metric
```

```{r PrecipSum12_22}
#An 11-day rolling window calculates the mean of PrecipCM for post-hatch days 12-22
clim.df$PrecipSum12_22 <- dplyr::lead(clim.df$PrecipSum1_11, n = 11)

#Code check
c(sum=sum(clim.df[12:22,5], na.rm = T), metric=clim.df[1,24])#mean() calculation should match metric
```

```{r PrecipSumIncubation}
#PrecipCM mean for 19 days prior to hatch date
clim.df$PrecipSumIncubation <- zoo::rollapply(clim.df$PrecipCM, width=19, FUN=sum, align = 'right', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(sum=sum(clim.df[1:19,5], na.rm = T), metric=clim.df[19,25]) #mean() calculation should match metric
```
<br>


### MaxCMinus10C rolling means
```{r Mean MaxCMinus10C1_11}
#An 11-day rolling window calculates the mean of MaxCMinus10C for post-hatch days 1-11
clim.df$MaxCMinus10C1_11 <- zoo::rollapply(clim.df$MaxCMinus10C, width=11, FUN=mean, align = 'left', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(mean=mean(clim.df[1:11,13]),metric=clim.df[1,26])
#mean() calculation should match metric
```

```{r Mean MaxCMinus10C12_22}
#An 11-day rolling window calculates the mean of MaxCMinus10C for post-hatch days 12-22
clim.df$MaxCMinus10C12_22 <- dplyr::lead(clim.df$MaxCMinus10C1_11, n = 11)

#Code check
c(mean=mean(clim.df[12:22,13]), metric=clim.df[1,27])#mean() calculation should match metric
```

```{r Mean MaxCMinus10CIncubation}
#MaxCMinus10C mean for 19 days prior to hatch date
clim.df$MaxCMinus10CIncubation <- zoo::rollapply(clim.df$MaxCMinus10C, width=19, FUN=mean, align = 'right', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(mean=mean(clim.df[1:19,13]), metric=clim.df[19,28]) #mean() calculation should match metric
```
<br>

### OneCMinusMinC rolling means
```{r Mean OneCMinusMinC1_11}
#An 11-day rolling window calculates the mean of OneCMinusMinC for post-hatch days 1-11
clim.df$OneCMinusMinC1_11 <- zoo::rollapply(clim.df$OneCMinusMinC, width=11, FUN=mean, align = 'left', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(mean=mean(clim.df[1:11,12]),metric=clim.df[1,29])
#mean() calculation should match metric
```

```{r Mean OneCMinusMinC12_22}
#An 11-day rolling window calculates the mean of OneCMinusMinC for post-hatch days 12-22
clim.df$OneCMinusMinC12_22 <- dplyr::lead(clim.df$OneCMinusMinC1_11, n = 11)

#Code check
c(mean=mean(clim.df[12:22,12]), metric=clim.df[1,30])#mean() calculation should match metric
```

```{r Mean OneCMinusMinCIncubation}
#OneCMinusMinC mean for 19 days prior to hatch date
clim.df$OneCMinusMinCIncubation <- zoo::rollapply(clim.df$OneCMinusMinC, width=19, FUN=mean, align = 'right', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(mean=mean(clim.df[1:19,12]), metric=clim.df[19,31]) #mean() calculation should match metric
```
<br>

## Averaged best bill metric window from climwin analysis: Six days post hatching to 19 days post hatching

### MaxC climwin best window
```{r MaxC.win (6-19)}
#New vector to contain the mean MaxC of days 6-19
clim.df$MaxC.win <- dplyr::lead(clim.df$MaxC, n = 5)
clim.df$MaxC.win <- zoo::rollapply(clim.df$MaxC.win, width=14, FUN=mean, align = 'left', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(mean=mean(clim.df[6:19,9]),metric=clim.df[1,32])
#mean() calculation should match metric
```
<br>

### MinC climwin best window
```{r MinC.win (6-19)}
#New vector to contain the mean MinC of days 6-19
clim.df$MinC.win <- dplyr::lead(clim.df$MinC, n = 5)
clim.df$MinC.win <- zoo::rollapply(clim.df$MinC.win, width=14, FUN=mean, align = 'left', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(mean=mean(clim.df[6:19,8]),metric=clim.df[1,33])
#mean() calculation should match metric
```
<br>


### GDD10C climwin best window
```{r GDD10CSum.win (6-19)}
#New vector to contain the mean value of days 6-19
clim.df$GDD10CSum.win <- dplyr::lead(clim.df$GDD10C, n = 5)
clim.df$GDD10CSum.win <- zoo::rollapply(clim.df$GDD10CSum.win, width=14, FUN=mean, align = 'left', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(mean=mean(clim.df[6:19,11]),metric=clim.df[1,34])
#mean() calculation should match metric
```
<br>


### PrecipSum climwin best window
```{r PrecipSum.win (6-19)}
#New vector to contain the mean value of days 6-19
clim.df$PrecipSum.win <- dplyr::lead(clim.df$PrecipCM, n = 5)
clim.df$PrecipSum.win <- zoo::rollapply(clim.df$PrecipSum.win, width=14, FUN=sum, align = 'left', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(mean=sum(clim.df[6:19,5], na.rm = T),metric=clim.df[1,35])
#mean() calculation should match metric
```
<br>

### MaxCMinus10C climwin best window
```{r MaxCMinus10C.win (6-19)}
#New vector to contain the mean MaxCMinus10C of days 6-19
clim.df$MaxCMinus10C.win <- dplyr::lead(clim.df$MaxCMinus10C, n = 5)
clim.df$MaxCMinus10C.win <- zoo::rollapply(clim.df$MaxCMinus10C.win, width=14, FUN=mean, align = 'left', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(mean=mean(clim.df[6:19,13]),metric=clim.df[1,36])
#mean() calculation should match metric
```
<br>

### OneCMinusMinC rolling means
```{r OneCMinusMinC.win}
#New vector to contain the mean OneCMinusMinC of days 6-19
clim.df$OneCMinusMinC.win <- dplyr::lead(clim.df$OneCMinusMinC, n = 5)
clim.df$OneCMinusMinC.win <- zoo::rollapply(clim.df$OneCMinusMinC.win, width=14, FUN=mean, align = 'left', fill = NA, partial = TRUE, na.rm = TRUE)

#Code check
c(mean=mean(clim.df[6:19,12]),metric=clim.df[1,37])
#mean() calculation should match metric
```
<br>

```{r simplified df for analysis}
#New dataframe with the derived climate metrics
clim.df <- clim.df[,c(1,4,14:37)]
```

```{r write metrics csv for joining with nestling data}
#write.csv(clim.df, "ClimateMetrics_ForJoining.csv", row.names = FALSE)
```



