---
title: "Testing climwin"
author: "Justin Mann"
date: "`r Sys.Date()`"
output: html_document
---

```{r libraries, include=FALSE}
library(climwin)
library(tidyverse)
library(lubridate)
library(sjPlot) #plot_model & tab_model 
library(car) #vif
library(AICcmodavg) #aictab() for AICc model comparisons
library(ggpubr)
```

## Testing sliding window approach used in Liu et al. 2023 J of Avian Biol

The goal is to identify the window of time that best explains variation in nestling morphometrics. In the context of our project, this program will detect the post-hatch time period ('window' of days) over which our nestling's bills are most responsive to climatic conditions. Mathematically, it's simply running the same model, with every possible sequence of days inside a user-defined window of time, and then comparing AIC values across all models.

```{r climwin packaged data}
# egC.df <- MassClimate
# egB.df <- Mass 
```
<br>

 

```{r our data}
#Nestling data sheet with updated climate metrics
df <- read.csv("CrowNestlingClimate_UnscaledData_7.8.23.csv", h=TRUE)

#coerce our date vector to an R date
# df$Date <- as.Date(df$MeasurementDate)

#create a date that is 22 days post-hatch (climwin is built to look backwards from a specified date, not forwards)
df$HatchDatePlus22JulYear <- df$HatchDateJulYear + 22

#move variables in prep for scaling
df <- df %>%
  relocate(HatchDatePlus22JulYear, .after = HatchDateJulYear)

# Function to convert Julian days to calendar dates
julian_to_date <- function(julian_days) {
  # Extract year and day of year from Julian days
  year <- as.numeric(substr(julian_days, 1, 4))
  day_of_year <- as.numeric(substr(julian_days, 5, 7))
  
  # Convert Julian days to calendar dates
  date <- as.Date(paste0(year, "-01-01")) + as.difftime(day_of_year - 1, units = "days")
  return(date)
}

# Convert Julian days to calendar dates
calendar_dates <- julian_to_date(julian_days)

#our climate data for 1989-2022
clim.df <- read.csv("ClimateMetrics_AllMonths1989-2022.csv", h=T)
```
<br>


## Normalizing continuous data

R's scale function subtracts each value from the mean (centers) and divide it by the standard deviation (scales).

```{r scaling data}

#?scale()

#Nestlings:
#separate categorical and continous data
categorical.df <- df[,1:12]
continuous.df <- df[,13:47]

#scale continuous data
scaled.mat <- scale(continuous.df, center = TRUE, scale = TRUE)

#rejoin unscaled and scaled data
scaled.df <- cbind(categorical.df,scaled.mat)

#data frame with only nestling data
nestl.scaled.df <- scaled.df[,1:27]

#Climate:
#scale continuous 
clim.mat <- scale(clim.df[,5:11])
clim.scaled.df <- cbind(clim.df[,1:4],clim.mat)
```
<br>


We want to identify the correct baseline model for the sliding window function to use. One outstanding question is whether the model should include weight AND age or just weight. Anne is concerned that age and weight might be explaining the same variation.
<br>


```{r date formatting for climwin compatability}

#1. format dates to dd/mm/yyyy with no leading zero on single digit days
#2. make cDate for climate data and bDate (biological date) for nestling data

clim.scaled.df$cDate <- format(strptime(clim.scaled.df$Date, format = "%Y-%m-%d"), "%d/%m/%Y")

#remove leading zero
clim.scaled.df$cDate <- str_remove(clim.scaled.df$cDate, "^0+")
#clim.scaled.df$cDate <- as.factor(clim.scaled.df$cDate)
clim.scaled.df <- clim.scaled.df %>% 
  relocate(cDate, .after = Date)

nestl.scaled.df$HatchDatePlus22 <-  

as.Date(nestl.scaled.df$HatchDatePlus22JulYear, format = "%m/%d/%Y")
nestl.scaled.df$bDate <- format(strptime(nestl.scaled.df$PostHatch22Date, format = "%Y-%m-%d"), "%d/%m/%Y") 

#remove leading zero
nestl.scaled.df$bDate <- str_remove(nestl.scaled.df$bDate, "^0+")
#nestl.scaled.df$bDate <- as.factor(nestl.scaled.df$bDate)
nestl.scaled.df <- nestl.scaled.df %>% 
  relocate(bDate, .before = AllSex)
```
<br>


```{r data frame with only sexed nestlings}
#Males Scaled
M.scaled.df <- subset(scaled.df, AllSex=="M")
#Males Unscaled
M.df <- subset(df, AllSex=="M")

#Females Scaled
F.scaled.df <- subset(scaled.df, AllSex=="F")
#Females Unscaled
F.df <- subset(df, AllSex=="F")

#Both sexes scaled
B.scaled.df <- rbind(F.scaled.df,M.scaled.df)
#Both sexes unscaled
B.df <- rbind(F.df,M.df)
```
<br>


```{r female baseline models}
F.weight.mdl <- lm(data = F.scaled.df, BD ~ Weight)
F.age.mdl <- lm(data = F.scaled.df, BD ~ CalcAge)
F.ageWeight.mdl <- lm(data = F.scaled.df, BD ~ Weight + CalcAge)
F.ageWeightInter.mdl <- lm(data = F.scaled.df, BD ~ Weight * CalcAge)

F.null.mdls <- list(F.weight.mdl,F.age.mdl,F.ageWeight.mdl,F.ageWeightInter.mdl)
F.null.modnames <- c("F.weight.mdl","F.age.mdl","F.ageWeight.mdl","F.ageWeightInter.mdl")
aictab(cand.set = F.null.mdls, modnames = F.null.modnames)

#The model including age and weight shows no signs of variance inflation due to covariance 
vif(F.ageWeight.mdl)

plot_model(F.ageWeightInter.mdl,type = "int")
summary(F.ageWeightInter.mdl)
```
<br>

```{r male baseline models}
M.weight.mdl <- lm(data = M.scaled.df, BD ~ Weight)
M.age.mdl <- lm(data = M.scaled.df, BD ~ CalcAge)
M.ageWeight.mdl <- lm(data = M.scaled.df, BD ~ Weight + CalcAge)
M.ageWeightInter.mdl <- lm(data = M.scaled.df, BD ~ Weight * CalcAge)

M.null.mdls <- list(M.weight.mdl,M.age.mdl,M.ageWeight.mdl,M.ageWeightInter.mdl)
M.null.modnames <- c("M.weight.mdl","M.age.mdl","M.ageWeight.mdl","M.ageWeightInter.mdl")
aictab(cand.set = M.null.mdls, modnames = M.null.modnames)

#The model including age and weight shows no signs of variance inflation due to covariance 
vif(M.ageWeight.mdl)

plot_model(M.ageWeightInter.mdl,type = "int")
summary(M.ageWeightInter.mdl)
```
<br>


```{r climate metric model comparison}
MinC.null.mdl <- lm(data = scaled.df, BD ~ MinC12_22 * PrecipSum12_22 + Weight)
MaxC.null.mdl <- lm(data = scaled.df, BD ~ MaxC12_22 * PrecipSum12_22 + Weight)
GDD10C.null.mdl <- lm(data = scaled.df, BD ~ GDD10CSum12_22 * PrecipSum12_22 + Weight)

clim.null.mdls <- list(MinC.null.mdl,MaxC.null.mdl,GDD10C.null.mdl)
clim.null.modnames <- c("MinC.null.mdl","MaxC.null.mdl","GDD10C.null.mdl")
aictab(cand.set = clim.null.mdls, modnames = clim.null.modnames, sort = TRUE)

summary(MinC.null.mdl)
```

## Tarsus sliding windows

MinC
```{r tarsus.window.min}
tarsus.window.min <- slidingwin(xvar = list(MinC = clim.scaled.df$MinC),
           exclude = c(4,0), #exclude windows shorter than 4 days
           cdate = clim.scaled.df$cDate,
           bdate = nestl.scaled.df$bDate,
           baseline = lm(Tarsus ~ Weight, data = nestl.scaled.df),
           cinterval = "day",
           #k = 10, #cross validation improves confidence in Beta values, but drastically narrows delta AIC
           range = c(22,0),
           type = "relative",
           stat = "mean",
           func = "lin")
tarsus.window.min.out <- tarsus.window.min[[1]]$Dataset
tarsus.window.min$combos
tarsus.window.min[[1]]$Dataset
tarsus.window.min[[1]]$BestModel
medwin(dataset = tarsus.window.min.out, cw = 0.80)
```
```{r tarsus.window.min plot weights}
TarsusWindow.plots <- ggarrange(plotweights(dataset = tarsus.window.min[[1]]$Dataset, cw1 = 0.95, cw2 = 0.75, cw3 = 0.25), plotdelta(dataset = tarsus.window.min.out))
TarsusWindow.plots <- annotate_figure(TarsusWindow.plots, bottom = text_grob("Tarsus", face = "bold", size = 16))
```


MaxC
```{r tarsus.window.max}
tarsus.window.max <- slidingwin(xvar = list(MaxC = clim.scaled.df$MaxC),
           exclude = c(4,0), #exclude windows shorter than 4 days
           cdate = clim.scaled.df$cDate,
           bdate = nestl.scaled.df$bDate,
           baseline = lm(Tarsus ~ Weight, data = nestl.scaled.df),
           cinterval = "day",
           #k = 10, #cross validation improves confidence in Beta values, but drastically narrows delta AIC
           range = c(22,0),
           type = "relative",
           stat = "mean",
           func = "lin")
tarsus.window.max.out <- tarsus.window.max[[1]]$Dataset
tarsus.window.max$combos
tarsus.window.max[[1]]$Dataset
tarsus.window.max[[1]]$BestModel
medwin(dataset = tarsus.window.max.out, cw = 0.80)
```
```{r tarsus.window.max plot weights}
ggarrange(plotweights(dataset = tarsus.window.max[[1]]$Dataset, cw1 = 0.95, cw2 = 0.75, cw3 = 0.25), plotdelta(dataset = tarsus.window.max.out))
```
<br>


## BD sliding window
```{r bd.window.max}
bd.window.max <- slidingwin(xvar = list(MaxC= clim.scaled.df$MaxC),
           exclude = c(4,0), #exclude windows shorter than 4 days
           cdate = clim.scaled.df$cDate,
           bdate = nestl.scaled.df$bDate,
           baseline = lm(BD ~ Weight, data = nestl.scaled.df),
           cinterval = "day",
           #k = 10, #cross validation improves confidence in Beta values, but drastically narrows delta AIC
           range = c(22,0),
           type = "relative",
           stat = "mean",
           func = "lin")
bd.window.max.out <- bd.window.max[[1]]$Dataset
bd.window.max$combos
bd.window.max[[1]]$Dataset
bd.window.max[[1]]$BestModel
medwin(dataset = bd.window.max.out, cw = 0.8)
```
<br>

```{r bd.window.max plots}
ggarrange(plotweights(dataset = bd.window.max.out, cw1 = 0.95, cw2 = 0.75, cw3 = 0.25),
plotdelta(dataset = bd.window.max.out))
```

```{r bd.window.min}
bd.window.min <- slidingwin(xvar = list(MinC= clim.scaled.df$MinC),
           exclude = c(4,0), #exclude windows shorter than 4 days
           cdate = clim.scaled.df$cDate,
           bdate = nestl.scaled.df$bDate,
           baseline = lm(BD ~ GDD10CSum12_22*PrecipSum12_22 + Weight, data = scaled.df),
           cinterval = "day",
           #k = 10, #cross validation improves confidence in Beta values, but drastically narrows delta AIC
           range = c(22,0),
           type = "relative",
           stat = "mean",
           func = "lin")
bd.window.min.out <- bd.window.min[[1]]$Dataset
bd.window.min$combos
bd.window.min[[1]]$Dataset
bd.window.min[[1]]$BestModel
medwin(dataset = bd.window.min.out, cw = 0.80)
```
<br>

```{r bd.window.min plots}
BDWindow.plots <- ggarrange(plotweights(dataset = bd.window.min.out, cw1 = 0.95, cw2 = 0.75, cw3 = 0.25),
plotdelta(dataset = bd.window.min.out))
BDWindow.plots <- annotate_figure(BDWindow.plots, bottom = text_grob("Bill Depth", face = "bold", size = 16))
```

```{r window comparison plots}
WindowComparison.wrap <- ggarrange(TarsusWindow.plots,BDWindow.plots, nrow = 2)
WindowComparison.wrap
#cowplot::save_plot("Plots/WindowComparison.wrap.png", WindowComparison.wrap, base_height = 9, base_width = 8)
```


<br>

```{r bd.window.gdd}
bd.window.gdd <- slidingwin(xvar = list(GDD= clim.scaled.df$GDD10C),
           exclude = c(4,0), #exclude windows shorter than 4 days
           cdate = clim.scaled.df$cDate,
           bdate = nestl.scaled.df$bDate,
           baseline = lm(BD ~ Weight, data = nestl.scaled.df),
           cinterval = "day",
           #k = 10, #cross validation improves confidence in Beta values, but drastically narrows delta AIC
           range = c(22,0),
           type = "relative",
           stat = "mean",
           func = "lin")
bd.window.gdd.out <- bd.window.gdd[[1]]$Dataset
bd.window.gdd$combos
bd.window.gdd[[1]]$Dataset
bd.window.gdd[[1]]$BestModel
medwin(dataset = bd.window.gdd.out, cw = 0.8)
```

```{r bd.window.gdd plots}
ggarrange(plotweights(dataset = bd.window.gdd.out, cw1 = 0.95, cw2 = 0.75, cw3 = 0.25), plotdelta(dataset = bd.window.gdd.out))
```
<br>


Randomized bill depth window
```{r bill depth random window}
bd.randwindow <- randwin(xvar = list(MaxC= clim.scaled.df$MaxC),
           exclude = c(4,0), #exclude windows shorter than 4 days
           window = "sliding",
           repeats = 100,
           cdate = clim.scaled.df$cDate,
           bdate = nestl.scaled.df$bDate,
           baseline = lm(BD ~ Weight, data = nestl.scaled.df),
           cinterval = "day",
           #k = 10, #cross validation improves confidence in Beta values, but drastically narrows delta AIC
           range = c(22,0),
           type = "relative",
           stat = "mean",
           func = "lin")

bd.randwindow.out <- as.data.frame(bd.randwindow)
```
<br>

```{r BD climwin pvalue}
plothist(bd.window.max.out,bd.randwindow)
pvalue(datasetrand = bd.randwindow, dataset = bd.window.max.out, metric = "AIC", sample.size = 29)
```
<br>


## BW sliding window
```{r BW MaxMinus10 slidingwin}
bw.window.max <- slidingwin(xvar = list(MaxMinus10= clim.scaled.df$MaxMinus10),
           exclude = c(4,0), #exclude windows shorter than 4 days
           cdate = clim.scaled.df$cDate,
           bdate = nestl.scaled.df$bDate,
           baseline = lm(BW ~ Weight, data = nestl.scaled.df),
           cinterval = "day",
           #k = 10, #cross validation improves confidence in Beta values, but drastically narrows delta AIC
           range = c(22,0),
           type = "relative",
           stat = "mean",
           func = "lin")
bw.window.max.out <- bw.window.max[[1]]$Dataset
bw.window.max.out
bw.window.max[[1]]$BestModel
medwin(bw.window.max.out, cw = 0.80)
```
<br>

```{r bw.window.max plots}
ggarrange(plotweights(dataset = bw.window.max.out, cw1 = 0.95, cw2 = 0.75, cw3 = 0.25),
plotdelta(dataset = bw.window.max.out))
```
<br>


```{r BW OneMinusMin slidingwin}
bw.window.min <- slidingwin(xvar = list(MinC= clim.scaled.df$MinC),
           exclude = c(4,0), #exclude windows shorter than 4 days
           cdate = clim.scaled.df$cDate,
           bdate = nestl.scaled.df$bDate,
           baseline = lm(BW ~ GDD10CSum12_22*PrecipSum12_22 + Weight, data = scaled.df),
           cinterval = "day",
           #k = 10, #cross validation improves confidence in Beta values, but drastically narrows delta AIC
           range = c(22,0),
           type = "relative",
           stat = "mean",
           func = "lin")
bw.window.min.out <- bw.window.min[[1]]$Dataset
bw.window.min.out
bw.window.min[[1]]$BestModel
medwin(bw.window.min.out, cw = 0.80)
```
<br>

```{r bw.window.min plots}
ggarrange(plotweights(dataset = bw.window.min.out, cw1 = 0.95, cw2 = 0.75, cw3 = 0.25),
plotdelta(dataset = bw.window.min.out))
```
<br>


## TEC sliding window
```{r TEC MaxMinus10 slidingwin}
tec.window.gdd <- slidingwin(xvar = list(GDD= clim.scaled.df$GDD10C),
           exclude = c(4,0), #exclude windows shorter than 4 days
           cdate = clim.scaled.df$cDate,
           bdate = nestl.scaled.df$bDate,
           baseline = lm(TEC ~ Weight, data = nestl.scaled.df),
           cinterval = "day",
           #k = 10, #cross validation improves confidence in Beta values, but drastically narrows delta AIC
           range = c(22,0),
           type = "relative",
           stat = "mean",
           func = "lin")
tec.window.gdd.out <- tec.window.max[[1]]$Dataset
tec.window.gdd[[1]]$BestModel
medwin(tec.window.gdd.out, cw = 0.80)
```
<br>


```{r tec.window.max plots}
ggarrange(plotweights(dataset = tec.window.gdd.out, cw1 = 0.95, cw2 = 0.75, cw3 = 0.25),
plotdelta(dataset = tec.window.gdd.out))
```
<br>


```{r TEC OneMinusMin slidingwin}
tec.window.min <- slidingwin(xvar = list(MinC= clim.scaled.df$MinC),
           exclude = c(4,0), #exclude windows shorter than 4 days
           cdate = clim.scaled.df$cDate,
           bdate = nestl.scaled.df$bDate,
           baseline = lm(TEC ~ GDD10CSum12_22 * PrecipSum12_22 + Weight, data = scaled.df),
           cinterval = "day",
           #k = 10, #cross validation improves confidence in Beta values, but drastically narrows delta AIC
           range = c(22,0),
           type = "relative",
           stat = "mean",
           func = "lin")
tec.window.min.out <- tec.window.min[[1]]$Dataset
tec.window.min[[1]]$BestModel
medwin(tec.window.min.out, cw = 0.80)
```
<br>

```{r tec.window.min plots}
ggarrange(plotweights(dataset = tec.window.min.out, cw1 = 0.95, cw2 = 0.75, cw3 = 0.25),
plotdelta(dataset = tec.window.min.out))
```
<br>


## BNT sliding window
```{r BNT MaxMinus10 slidingwin}
bnt.window.max <- slidingwin(xvar = list(MaxMinus10= clim.scaled.df$MaxMinus10),
           #exclude = c(4,0), #exclude windows shorter than 4 days
           cdate = clim.scaled.df$cDate,
           bdate = nestl.scaled.df$bDate,
           baseline = lm(BNT ~ Weight, data = nestl.scaled.df),
           cinterval = "day",
           #k = 10, #cross validation improves confidence in Beta values, but drastically narrows delta AIC
           range = c(22,0),
           type = "relative",
           stat = "mean",
           func = "lin")
bnt.window.max$combos
bnt.window.max.out <- bnt.window.max[[1]]$Dataset
bnt.window.max.out
bnt.window.max[[1]]$BestModel
medwin(bnt.window.max.out, cw = 0.80)
```
<br>

```{r bnt.window.max plots}
ggarrange(plotweights(dataset = bnt.window.max.out, cw1 = 0.95, cw2 = 0.75, cw3 = 0.25),
plotdelta(dataset = bnt.window.max.out))
```
<br>

```{r BNT OneMinusMin slidingwin}
bnt.window.min <- slidingwin(xvar = list(MinC= clim.scaled.df$MinC),
           #exclude = c(4,0), #exclude windows shorter than 4 days
           cdate = clim.scaled.df$cDate,
           bdate = nestl.scaled.df$bDate,
           baseline = lm(BNT ~ Weight, data = nestl.scaled.df),
           cinterval = "day",
           #k = 10, #cross validation improves confidence in Beta values, but drastically narrows delta AIC
           range = c(22,0),
           type = "relative",
           stat = "mean",
           func = "lin")
bnt.window.min$combos
bnt.window.min.out <- bnt.window.min[[1]]$Dataset
bnt.window.min.out
bnt.window.min[[1]]$BestModel
medwin(bnt.window.min.out, cw = 0.80)
```
<br>

```{r bnt.window.min plots}
ggarrange(plotweights(dataset = bnt.window.min.out, cw1 = 0.95, cw2 = 0.75, cw3 = 0.25),
plotdelta(dataset = tec.window.min.out))
```
<br>

I reran the directly-measured bill metric sliding windows (BD, BW, BNT, TEC) using the MaxMinus10 and OneMinusMin climate metrics. I averaged the median windows from 80% confidence sets for each bill metric. The average window opened 6 days post-hatch and closed 19 days post-hatch. I'm going to add this window to our 1_11 and 12_22 metrics for modeling.




# Derived bill metrics

## UB sliding window
```{r upper bill slidingwin}
ub.window <- slidingwin(xvar = list(MinC= clim.scaled.df$MinC),
           exclude = c(4,0), #exclude windows shorter than 4 days
           cdate = clim.scaled.df$cDate,
           bdate = nestl.scaled.df$bDate,
           baseline = lm(UB ~ Weight, data = nestl.scaled.df),
           cinterval = "day",
           #k = 10, #cross validation improves confidence in Beta values, but drastically narrows delta AIC
           range = c(22,0),
           type = "relative",
           stat = "mean",
           func = "lin")
ub.window.out <- ub.window[[1]]$Dataset
ub.window[[1]]$BestModel
medwin(ub.window.out, cw = 0.8)
```
<br>


## UBS sliding window
```{r upper bill surface area slidingwin}
ubs.window <- slidingwin(xvar = list(MaxMinus10= clim.scaled.df$MaxMinus10),
           exclude = c(4,0), #exclude windows shorter than 4 days
           cdate = clim.scaled.df$cDate,
           bdate = nestl.scaled.df$bDate,
           baseline = lm(UBS ~ Weight, data = nestl.scaled.df),
           cinterval = "day",
           #k = 10, #cross validation improves confidence in Beta values, but drastically narrows delta AIC
           range = c(22,0),
           type = "relative",
           stat = "mean",
           func = "lin")
ubs.window.out <- ubs.window[[1]]$Dataset
ubs.window[[1]]$BestModel
medwin(ubs.window.out, cw = 0.95)
```
<br>



