---
title: "Testing climwin"
author: "Justin Mann"
date: "`r Sys.Date()`"
output: html_document
---

```{r libraries, include=FALSE}
library(climwin)
library(tidyverse)
library(lubridate)
library(sjPlot) #plot_model & tab_model 
library(car) #vif
library(AICcmodavg) #aictab() for AICc model comparisons
library(ggpubr)
```

## Testing sliding window approach used in Liu et al. 2023 J of Avian Biol

The goal is to identify the window of time that best explains variation in nestling morphometrics. In the context of our project, this program will detect the post-hatch time period ('window' of days) over which our nestling's bills are most responsive to climatic conditions. Mathematically, it's simply running the same model, with every possible sequence of days inside a user-defined window of time, and then comparing AIC values across all models.

```{r climwin packaged data}
# egC.df <- MassClimate
# egB.df <- Mass 
```
<br>

 

```{r data}
# Nestling data sheet with updated climate metrics
df <- read.csv("CrowNestlingClimate_UnscaledData_7.8.23.csv", h=TRUE)
# 2030 nestlings 

# Climate data for 1989-2022
clim.df <- read.csv("ClimateMetrics_AllMonths1989-2022.csv", h=TRUE)
# 12418 daily observations
```
<br>


```{r date conversions}
# Create a date that is 22 days post-hatch (climwin is programmed to look backwards in time from a specified date, not forwards)
df$HatchDatePlus22JulYear <- df$HatchDateJulYear + 22

# Relocate
df <- df %>%
  relocate(HatchDatePlus22JulYear, .after = HatchDateJulYear)

# Function to convert Julian days to calendar dates
julian_to_date <- function(julian_days) {
  # Extract year and day of year from Julian days
  year <- as.numeric(substr(julian_days, 1, 4))
  day_of_year <- as.numeric(substr(julian_days, 5, 7))
  
  # Convert Julian days to calendar dates
  date <- as.Date(paste0(year, "-01-01")) + as.difftime(day_of_year - 1, units = "days")
  return(date)
}

# Convert Julian days to calendar dates
df$HatchDatePlus22 <- julian_to_date(df$HatchDatePlus22JulYear)

# Relocate
df <- df %>% 
  relocate(HatchDatePlus22, .after = HatchDatePlus22JulYear)
```


## Normalizing continuous data

R's scale function subtracts each value from the mean (centers) and divide it by the standard deviation (scales).


```{r scaling data}

# ?scale()

# Nestlings:
# separate categorical and continous data
categorical.df <- df[,1:13]
continuous.df <- df[,14:48]

#scale continuous data
scaled.mat <- scale(continuous.df, center = TRUE, scale = TRUE)

#rejoin unscaled and scaled data
scaled.df <- cbind(categorical.df,scaled.mat)

#data frame with only nestling data
nestl.scaled.df <- scaled.df[,1:28]

#Climate:
#scale continuous 
clim.mat <- scale(clim.df[,5:11])
clim.scaled.df <- cbind(clim.df[,1:4],clim.mat)
```
<br>


```{r formatting dates for climwin compatability}

#1. format dates to dd/mm/yyyy with no leading zero on single digit days
#2. make cDate for climate data and bDate (biological date) for nestling data

clim.scaled.df$cDate <- format(strptime(clim.scaled.df$Date, format = "%Y-%m-%d"), "%d/%m/%Y")

#remove leading zero
clim.scaled.df$cDate <- str_remove(clim.scaled.df$cDate, "^0+")
#clim.scaled.df$cDate <- as.factor(clim.scaled.df$cDate)
clim.scaled.df <- clim.scaled.df %>% 
  relocate(cDate, .after = Date)

nestl.scaled.df$bDate <- as.Date(nestl.scaled.df$HatchDatePlus22, format = "%m/%d/%Y")

nestl.scaled.df$bDate <- format(strptime(nestl.scaled.df$HatchDatePlus22, format = "%Y-%m-%d"), "%d/%m/%Y") 

#remove leading zero
nestl.scaled.df$bDate <- str_remove(nestl.scaled.df$bDate, "^0+")
#nestl.scaled.df$bDate <- as.factor(nestl.scaled.df$bDate)
nestl.scaled.df <- nestl.scaled.df %>% 
  relocate(bDate, .after = HatchDatePlus22)
nestl.scaled.df <- na.omit(nestl.scaled.df)
```
<br>

Here, we're using the interaction between mean temperature and summed precipitation for days 12-22 to compare Bill depth models to identify which temperature metric explains the most variation (comparing delta AICc). We used days 12-22 because Anne suspects, given earlier growth curves, that the second week is more relevant.

```{r temperature metric model comparison}
MinC.null.mdl <- lm(data = scaled.df, TBS ~ MinC12_22 * PrecipSum12_22 + Weight)
MaxC.null.mdl <- lm(data = scaled.df, TBS ~ MaxC12_22 * PrecipSum12_22 + Weight)
GDD10C.null.mdl <- lm(data = scaled.df, TBS ~ GDD10CSum12_22 * PrecipSum12_22 + Weight)

clim.null.mdls <- list(MinC.null.mdl,MaxC.null.mdl,GDD10C.null.mdl)
clim.null.modnames <- c("MinC.null.mdl","MaxC.null.mdl","GDD10C.null.mdl")
aictab(cand.set = clim.null.mdls, modnames = clim.null.modnames, sort = TRUE)
#MinC is the best fit model by 8.99 Delta AICc

summary(MinC.null.mdl)
```


Here, we're comparing different nestling measurements to see which should be used for the sliding window analysis. We'll use the measurement that explains the most variation (comparing r squared)


```{r bill metric model comparison}
MinC.BD.null.mdl <- lm(data = scaled.df, BD ~ MinC12_22 * PrecipSum12_22 + Weight)
MinC.TEC.null.mdl <- lm(data = scaled.df, TEC ~ MinC12_22 * PrecipSum12_22 + Weight)
MinC.BNT.null.mdl <- lm(data = scaled.df, BNT ~ MinC12_22 * PrecipSum12_22 + Weight)
MinC.BW.null.mdl <- lm(data = scaled.df, BW ~ MinC12_22 * PrecipSum12_22 + Weight)
MinC.UB.null.mdl <- lm(data = scaled.df, UB ~ MinC12_22 * PrecipSum12_22 + Weight)
MinC.UBS.null.mdl <- lm(data = scaled.df, UBS ~ MinC12_22 * PrecipSum12_22 + Weight)
MinC.TBS.null.mdl <- lm(data = scaled.df, TBS ~ MinC12_22 * PrecipSum12_22 + Weight)
 
summary(MinC.BD.null.mdl)$r.squared 
summary(MinC.TEC.null.mdl)$r.squared 
summary(MinC.BNT.null.mdl)$r.squared
summary(MinC.BW.null.mdl)$r.squared
summary(MinC.UB.null.mdl)$r.squared
summary(MinC.UBS.null.mdl)$r.squared
summary(MinC.TBS.null.mdl)$r.squared

MinC.BD1.null.mdl <- lm(data = scaled.df, BD ~ MinC1_11 * PrecipSum1_11 + Weight)
MinC.TEC1.null.mdl <- lm(data = scaled.df, TEC ~ MinC1_11 * PrecipSum1_11 + Weight)
MinC.BNT1.null.mdl <- lm(data = scaled.df, BNT ~ MinC1_11 * PrecipSum1_11 + Weight)
MinC.BW1.null.mdl <- lm(data = scaled.df, BW ~ MinC1_11 * PrecipSum1_11 + Weight)
MinC.UB1.null.mdl <- lm(data = scaled.df, UB ~ MinC1_11 * PrecipSum1_11 + Weight)
MinC.UBS1.null.mdl <- lm(data = scaled.df, UBS ~ MinC1_11 * PrecipSum1_11 + Weight)
MinC.TBS1.null.mdl <- lm(data = scaled.df, TBS ~ MinC1_11 * PrecipSum1_11 + Weight)
 
summary(MinC.BD1.null.mdl)$r.squared 
summary(MinC.TEC1.null.mdl)$r.squared 
summary(MinC.BNT1.null.mdl)$r.squared
summary(MinC.BW1.null.mdl)$r.squared
summary(MinC.UB1.null.mdl)$r.squared
summary(MinC.UBS1.null.mdl)$r.squared
summary(MinC.TBS1.null.mdl)$r.squared

```



## TBS sliding window

MinC
```{r TBS.window.min}
TBS.window.min <- slidingwin(xvar = list(MinC = clim.scaled.df$MinC),
           exclude = c(4,0), #exclude windows shorter than 4 days
           cdate = clim.scaled.df$cDate,
           bdate = nestl.scaled.df$bDate,
           baseline = lm(TBS ~ Weight, data = nestl.scaled.df),
           cinterval = "day",
           #k = 10, #cross validation improves confidence in Beta values, but drastically narrows delta AIC
           range = c(22,0),
           type = "relative",
           stat = "mean",
           func = "lin")
TBS.window.min.out <- TBS.window.min[[1]]$Dataset
TBS.window.min$combos
TBS.window.min[[1]]$Dataset
TBS.window.min[[1]]$BestModel
medwin(dataset = TBS.window.min.out, cw = 0.80)
```

```{r TBS.window.min plots}
ggarrange(plotweights(dataset = TBS.window.min.out, cw1 = 0.95, cw2 = 0.75, cw3 = 0.25),
plotdelta(dataset = TBS.window.min.out))
```

## BD sliding window
```{r bd.window.min}
bd.window.min <- slidingwin(xvar = list(MaxC= clim.scaled.df$MinC),
           exclude = c(4,0), #exclude windows shorter than 4 days
           cdate = clim.scaled.df$cDate,
           bdate = nestl.scaled.df$bDate,
           baseline = lm(BD ~ Weight, data = nestl.scaled.df),
           cinterval = "day",
           #k = 10, #cross validation improves confidence in Beta values, but drastically narrows delta AIC
           range = c(22,0),
           type = "relative",
           stat = "mean",
           func = "lin")
bd.window.min.out <- bd.window.min[[1]]$Dataset
bd.window.min$combos
bd.window.min[[1]]$Dataset
bd.window.min[[1]]$BestModel
medwin(dataset = bd.window.min.out, cw = 0.8)
```
<br>

```{r bd.window.min plots}
ggarrange(plotweights(dataset = bd.window.min.out, cw1 = 0.95, cw2 = 0.75, cw3 = 0.25),
plotdelta(dataset = bd.window.min.out))
```





