---
title: "Building Nestling Datasets"
author: "Justin Mann"
date: "`r Sys.Date()`"
output: html_document
---

```{r libraries, include=FALSE}
library(tidyverse)
library(broom) #tidy() to create tibbles from model summaries
library(car) #vif (variance inflation factor for measuring covariance)
library(cowplot)
library(lme4) #frequentist models  
library(sjPlot) #plot_model & tab_model (blue = #377EB8)
library(ggpubr) #ggarrange for plot wraps
library(lmerTest) #lmerTest::step
library(ggeffects) #ggpredict
library(plotly) #ggplotly() to make interactive plots with scroll over ids
library(MuMIn) #dredge() for unsupervised model selection
library(AICcmodavg) #aictab() for AICc model comparisons
library(DHARMa) #model validation functions
library(DescTools) #Entropy() and MutInf()

#Libraries for Bayesian Models
library(rstanarm) #stan models
library(shinystan) #stan model evaluation
#launch_shinystan_demo()
library(loo) #use loo() to compare fits between bayesian models

#Clustering libraries
library(umap)
library(tsne)
library(ggfortify)#use autoplot() to visualize PCAs
library(stpm)#stochastic process model
theme_set(theme_classic()) #default plots with no gridlines
```

# Building the nestling dataset

<br>

## Nestling data from CrowBase (Filemaker database)

The original data used for nestling analyses were exported from Filemaker as ["Nestlings1989-2018_no2011_WITH_AdultMeasurements_2001-2015.xlsx"](https://github.com/justinthomasmann/CrowBase/blob/main/OldDocs/Nestlings1989-2018_no2011_WITH_AdultMeasurements_2001-2015.xlsx) in February 2021 during JTM's employment as database manager. The first exploration of nestling morphometrics by JTM and ABC using those data are documented in ["CB-NestlingsAndAdults.Rmd"](https://github.com/justinthomasmann/CrowBase/blob/main/CB-NestlingsAndAdults.Rmd).

```{r import Nestlings1989-2018_no2011_WITH_AdultMeasurements_2001-2015.xlsx}
FMExport.df <- read.csv("OldDocs/Nestlings1989-2018_no2011_WITH_AdultMeasurements_2001-2015.csv", h=TRUE)
summary(FMExport.df)
```

<br>

```{r create a FMNestling.df}
#only American crow nestlings from Ithaca (n=3924)
FMNestling.df <- FMExport.df %>% 
  filter(lifeStage=="nestling") %>% 
  filter(population=="Ithaca") %>%
  filter(species=="AMCR") %>% 
  select(year,id,age,sexSummary,tarsus,sevenPrimary,tailLength,calcAge,billNT,billD,billW,TEC,head,skull,wingChord,exp7Primary,weight,measurmentDate,hatchDate) %>% 
  rename(sex=sexSummary)
```

```{r count NAs in FMNestling.df}
sapply(FMNestling.df, function(x) sum(is.na(x)))
```

```{r duplicate IDs in FMNestling.df}
FMNestling.Duplicates.df <- FMNestling.df %>% 
  group_by(id) %>% filter(n()>1) %>% 
  arrange(year,id)
```

```{r age filtered FMNestling.df}
FMNestling.AgeFilter.df <- FMNestling.df %>% 
  filter(age > 23) %>% 
  filter(between(calcAge, 24,29))
```

The file ["nestlingMorph.csv"](https://github.com/justinthomasmann/CrowBase/blob/main/nestlingMorph.csv) was created in April 2021 as a nestling-only subset (lifestage = "nestling") of the original Filemaker export that's linked above.

```{r import nestlingMorph.csv}
nestlingMorph.df <- read.csv("nestlingMorph.csv", h=T)#n=4081 nestlings
summary(nestlingMorph.df)
```

```{r filter nestlingMorph.df by population and species}
#only American crow nestlings from Ithaca (n=3919)
nestlingMorph.df <- nestlingMorph.df %>% 
  filter(population=="Ithaca") %>%
  filter(species=="AMCR") %>% 
  rename(weight=mass)
```

```{r drop unused columns}
nestlingMorph.df <- nestlingMorph.df %>% 
  select(year, id, age, sex, tarsus, sevenPrimary, tailLength, calcAge, billNT, billD, billW, TEC, head, skull, wingChord, exp7Primary, weight, measurmentDate, hatchDate)
```

```{r duplicate IDs in nestlingMorph.df}
nestlingMorph.Duplicates.df <- nestlingMorph.df %>% 
  group_by(id) %>% filter(n()>1) %>% 
  arrange(year,id)
```

```{r count NAs in simplified nestlingMorph.df}
countNAs <- sapply(nestlingMorph.df, function(x) sum(is.na(x)))
countNAs
```

```{r age filtered nestlingMorph.df}
nestlingMorph.AgeFilter.df <- nestlingMorph.df %>% 
  filter(age > 23) %>% 
  filter(between(calcAge, 24,29))
```

<br>

```{r anti_join nestlingMorph.AgeFilter.df and FMNestling.AgeFilter.df}
nestlingMorph.AntiJoin.df <- anti_join(nestlingMorph.AgeFilter.df,FMNestling.AgeFilter.df,by="id")
```

```{r anti_join nestlingMorph.AgeFilter.df and FMNestling.AgeFilter.df}
FMNestling.AntiJoin.df <- anti_join(FMNestling.AgeFilter.df,nestlingMorph.AgeFilter.df,by="id")
```

```{r import CrowNestlingClimate}
df <- read.csv("FullNestlingDataset.csv", h=T)
df2 <- read.csv("CrowNestlingClimate_AllNestlingsCleaned&ClimateJoinedNEW.csv", h=T)
df2 <- df2 %>% 
  select(ID,FieldAge,CalcAge,HatchDateJulYear,AllSex,BNT,BW,BD,TEC,UB,UBS,TBS,Skull,Tarsus,Weight) %>% 
  relocate(HatchDateJulYear, .before = ID)

fulljoin.df <- full_join(df,df2,by=c("HatchDateJulYear","ID","FieldAge","CalcAge","AllSex","BNT","BW","BD","TEC","UB","UBS","TBS","Skull","Tarsus","Weight"))

NestlingData.df <- fulljoin.df %>% 
  arrange(HatchDateJulYear)

#write.csv(NestlingData.df, "CleanedNestlingData_061423.csv", row.names = FALSE) 
#n = 1954

NestlingData.df <- read.csv("CleanedNestlingData_061423.csv", h=TRUE)
```

```{r excluded nestlings}
#trim some kids with impossible measurements (per Anne)
NestlingData.df <- NestlingData.df %>% 
  filter(Tarsus < 70) %>% 
  filter(between(CalcAge,24,29)) #1946
```

```{r excluding runts per Anne}
NestlingData.df <- NestlingData.df %>% filter(!ID %in% c("FFW-S DRIN02","B3 WINK98","GL JSUP05","Q4 CARE11","JC NDYC17","L-2 KRUM93","orange SWEG91","SWB-W BURP03","3 PINW00","4 PINW00","doa SEPG04","2-r HORC04","doa CLAR05","doa HOMC05","doa JUDD06","doa1 KAYS06","doa2 KAYS06","doa3 KAYS06","doa1 BROT07","doa2 BROT07","doa1 NMUR07","doa2 NMUR07","doa3 NMUR07","doa4 NMUR07","doa5 NMUR07","FE WCRI18","DOA RGBY00","X0 YFER00","dead fledgling USGS16", "EN WKAY05"))#new n=1942
```

```{r removing duplicates}
duplicates.df <- NestlingData.df %>% group_by(ID) %>% filter(n()>1)

duplicates.df <- duplicates.df %>%  group_by(HatchDateJulYear) %>% arrange(ID, FieldAge) %>% dplyr::distinct(ID, .keep_all = TRUE)

NestlingData.df <- NestlingData.df %>%  group_by(HatchDateJulYear) %>% arrange(ID, FieldAge) %>% dplyr::distinct(ID, .keep_all = TRUE)
```

```{r count NAs}
#Count NAs
sapply(NestlingData.df, function(x) sum(is.na(x)))
```

```{r import CleanedNestlingData_061423.csv}
CleanedNestlings.df <- read.csv("CleanedNestlingData_061423.csv", h=TRUE)
```
