---
title: "Unsexed Nestling Analysis"
author: "Justin Mann"
date: "`r Sys.Date()`"
output: html_document
---

```{r libraries}
library(tidyverse)
library(dplyr)
library(broom) #tidy() to create tibbles from model summaries
library(car) #vif
library(cowplot)
library(lme4) #frequentist models  
library(sjPlot) #plot_model & tab_model (blue = #377EB8)
library(ggpubr) #ggarrange
library(glmmTMB) #zi & overdispersed models
library(lmerTest) #lmerTest::step
library(ggeffects) #ggpredict
#PACKAGES FOR BAYESIAN MODELS
library(rstanarm) #stan models
library(shinystan) #stan model evaluation
#launch_shinystan_demo()
library(loo) #use loo() to compare fits between bayesian models
library(ggeffects)
library(plotly)
library(MuMIn) #dredge() for unsupervised model selection
library(AICcmodavg) #aictab() for AICc model comparisons
library(DHARMa)
library(DescTools)
library(umap)
library(tsne)
theme_set(theme_classic())
```
<br>

## Data

```{r dataframe}
df <- read.csv("CrowNestlingClimate_AllNestlingsCleaned&ClimateJoined.csv", h=TRUE)
df <- df[,-1]
#n=2035 nestlings, 39 variables
```
<br>

A column to hold decade bins for plotting
```{r creating decade bins}
df$Decades <- cut(df$Year, breaks = c(1988,1999,2010,2018), labels = c("89-99","00-10","11-18"))
df <- df %>% relocate(Decades, .before = Year)
```
<br>

## Normalize Continuous Data

Subtract each value from the mean (center) and divide it by the standard deviation
```{r scaling}
#categorical data  
unScaled.df <- df[,1:11]

#continuous data
dataToScale.df <- df[,12:40]

#scale continuous data
#?scale()
scaled.mat <- scale(dataToScale.df, center = TRUE, scale = TRUE)

#join unscaled and scaled data
scaled.df <- cbind(unScaled.df,scaled.mat)
```
<br>

Summarize the unscaled data
```{r data summary }
summary(df)
```
<br> 

Summarize the scaled data
```{r scaled data summary}
summary(scaled.df)
```
<br>

## Bill Depth Models

Bayesian Bill Depth GDD Incubation model
```{r BD Incubation bayes model}
BDIncub.bmdl <- stan_glm(BD ~ GDDSumIncubation * PrecipSumIncubation + Weight + CalcAge,
                              data = scaled.df,
                              family = gaussian(),
                              algorithm = "sampling",
                              prior = student_t(df = 7, 0, 5), 
                              prior_intercept = student_t(df = 7, 0, 5),
                              cores = 2, seed = 666)
print(summary(BDIncub.bmdl), digits = 3)
#launch_shinystan(BDTime1.bmdl)
```

```{r plot BD ~ GDD Incubation model}
BDGDDIncub.plot <- plot(BDIncub.bmdl, pars = c("GDDSumIncubation","PrecipSumIncubation","Weight","CalcAge","GDDSumIncubation:PrecipSumIncubation"))
#BDGDDIncub.plot
```
<br>

A Frequentist Bill Depth GDD Time 1 model to compare with the Bayesian version
```{r BD Time 1 model}
BDTime1.scaled.mdl <- lm(data = scaled.df, BD ~ GDDSum1_11 * PrecipSum1_11 + Weight + CalcAge)
summary(BDTime1.scaled.mdl)
```
<br>

Bayesian Bill Depth GDD Time 1 model
```{r BD Time 1 bayes model}
BDTime1.bmdl <- stan_glm(BD ~ GDDSum1_11 * PrecipSum1_11 + Weight + CalcAge,
                              data = scaled.df,
                              family = gaussian(),
                              algorithm = "sampling",
                              prior = student_t(df = 7, 0, 5), 
                              prior_intercept = student_t(df = 7, 0, 5),
                              cores = 2, seed = 666)
print(summary(BDTime1.bmdl), digits = 3)
#launch_shinystan(BDTime1.bmdl)
```

```{r plot BD time 1}
BDGDDTime1.plot <- plot(BDTime1.bmdl, pars = c("GDDSum1_11","PrecipSum1_11","Weight","CalcAge","GDDSum1_11:PrecipSum1_11"))
#BDGDDTime1.plot
```
<br>

Bayesian Bill Depth GDD Time 2
```{r BD Time 2 bayes model}
BDTime2.bmdl <- stan_glm(BD ~ GDDSum12_22 * PrecipSum12_22 + Weight + CalcAge,
                              data = scaled.df,
                              family = gaussian(),
                              algorithm = "sampling",
                              prior = student_t(df = 7, 0, 5), 
                              prior_intercept = student_t(df = 7, 0, 5),
                              cores = 2, seed = 666)
print(summary(BDTime2.bmdl), digits = 3)
#launch_shinystan(BDTime1.bmdl)
```

```{r plot BD Time 2 model}
BDGDDTime2.plot <- plot(BDTime2.bmdl, pars = c("GDDSum12_22","PrecipSum12_22","Weight","CalcAge","GDDSum12_22:PrecipSum12_22"))
#BDGDDTime2.plot
```
<br>

Arrange the Bill Depth model plots
```{r ggarrange BD ~ GDD plots}
BDModelPlots.wrap <- ggarrange(BDGDDIncub.plot,BDGDDTime1.plot,BDGDDTime2.plot, ncol = 1)
annotate_figure(BDModelPlots.wrap, top = "Bill Depth Models")
```
<br>

Plot the interaction between GDD and Precip during incubation
```{r BD GDD Incubation Inter plot}
BDGDDIncubInter.plot <- plot_model(BDIncub.bmdl, type = "int", mdrt.values = "quart")

BDGDDIncubInter.plot <- BDGDDIncubInter.plot +
  scale_color_discrete(name="Precip Levels", labels=c("25th Quartile","Median", "75th Quartile"))+
  ylab("Bill Depth")+
  xlab("GDD Incubation")+
  theme(plot.title = element_blank(),
          axis.text.x = element_text(size = 12),
          axis.title.x = element_text(size = 14),
          axis.text.y = element_text(size = 12),
          axis.title.y = element_text(size = 14),
          legend.position = "top",
          plot.margin = margin(15,15,15,15))
#BDGDDIncubInter.plot
```
<br>

Plot the interaction between GDD and Precip during Time 2
```{r BD GDD Time 2 Inter plot}
BDGDDTime2Inter.plot <- plot_model(BDTime2.bmdl, type = "int", mdrt.values = "quart")

BDGDDTime2Inter.plot <- BDGDDTime2Inter.plot +
  scale_color_discrete(name="Precip Levels", labels=c("25th Quartile","Median", "75th Quartile"))+
  ylab("Bill Depth")+
  xlab("GDD Time 2")+
  theme(plot.title = element_blank(),
          axis.text.x = element_text(size = 12),
          axis.title.x = element_text(size = 14),
          axis.text.y = element_text(size = 12),
          axis.title.y = element_text(size = 14),
          legend.position = "top",
          plot.margin = margin(15,15,15,15))
#BDGDDTime2Inter.plot
```
<br>

Arrange interaction plots
```{r BD arrange inter plots}
BDInterPlots.wrap <- ggarrange(BDGDDIncubInter.plot,BDGDDTime2Inter.plot, ncol = 2)
annotate_figure(BDInterPlots.wrap, top = "Bill Depth Interaction Models")
```
<br> 

## Upper Bill Models

Bayesian Upper Bill Incubation model
```{r UB Incubation bayes model}
UBIncub.bmdl <- stan_glm(UB ~ GDDSumIncubation * PrecipSumIncubation + Weight + CalcAge,
                              data = scaled.df,
                              family = gaussian(),
                              algorithm = "sampling",
                              prior = student_t(df = 7, 0, 5), 
                              prior_intercept = student_t(df = 7, 0, 5),
                              cores = 2, seed = 666)
print(summary(UBIncub.bmdl), digits = 3)
#launch_shinystan(UBTime1.bmdl)
```

```{r plot UB ~ GDD Incubation model}
UBGDDIncub.plot <- plot(UBIncub.bmdl, pars = c("GDDSumIncubation","PrecipSumIncubation","Weight","CalcAge","GDDSumIncubation:PrecipSumIncubation"))
#UBGDDIncub.plot
```
<br>

Bayesian Upper Bill GDD Time 1 model
```{r UB Time 1 bayes model}
UBTime1.bmdl <- stan_glm(UB ~ GDDSum1_11 * PrecipSum1_11 + Weight + CalcAge,
                              data = scaled.df,
                              family = gaussian(),
                              algorithm = "sampling",
                              prior = student_t(df = 7, 0, 5), 
                              prior_intercept = student_t(df = 7, 0, 5),
                              cores = 2, seed = 666)
print(summary(UBTime1.bmdl), digits = 3)
#launch_shinystan(UBTime1.bmdl)
```

```{r plot UB time 1}
UBGDDTime1.plot <- plot(UBTime1.bmdl, pars = c("GDDSum1_11","PrecipSum1_11","Weight","CalcAge","GDDSum1_11:PrecipSum1_11"))
#UBGDDTime1.plot
```
<br>

Bayesian Upper Bill GDD Time 2
```{r UB Time 2 bayes model}
UBTime2.bmdl <- stan_glm(UB ~ GDDSum12_22 * PrecipSum12_22 + Weight + CalcAge,
                              data = scaled.df,
                              family = gaussian(),
                              algorithm = "sampling",
                              prior = student_t(df = 7, 0, 5), 
                              prior_intercept = student_t(df = 7, 0, 5),
                              cores = 2, seed = 666)
print(summary(UBTime2.bmdl), digits = 3)
#launch_shinystan(UBTime1.bmdl)
```

```{r plot UB Time 2 model}
UBGDDTime2.plot <- plot(UBTime2.bmdl, pars = c("GDDSum12_22","PrecipSum12_22","Weight","CalcAge","GDDSum12_22:PrecipSum12_22"))
#UBGDDTime2.plot
```
<br>

Arrange the Upper Bill model plots
```{r ggarrange UB ~ GDD plots}
UBModelPlots.wrap <- ggarrange(UBGDDIncub.plot,UBGDDTime1.plot,UBGDDTime2.plot, ncol = 1)
annotate_figure(UBModelPlots.wrap, top = "Upper Bill Models")
```
<br>

## Upper Bill Surface Area Models

Bayesian Upper Bill Surface Area Incubation model
```{r UBS Incubation bayes model}
UBSIncub.bmdl <- stan_glm(UBS ~ GDDSumIncubation * PrecipSumIncubation + Weight + CalcAge,
                              data = scaled.df,
                              family = gaussian(),
                              algorithm = "sampling",
                              prior = student_t(df = 7, 0, 5), 
                              prior_intercept = student_t(df = 7, 0, 5),
                              cores = 2, seed = 666)
print(summary(UBSIncub.bmdl), digits = 3)
#launch_shinystan(UBSTime1.bmdl)
```

```{r plot UBS ~ GDD Incubation model}
UBSGDDIncub.plot <- plot(UBSIncub.bmdl, pars = c("GDDSumIncubation","PrecipSumIncubation","Weight","CalcAge","GDDSumIncubation:PrecipSumIncubation"))
#UBSGDDIncub.plot
```
<br>

Bayesian Upper Bill Surface Area GDD Time 1 model
```{r UBS Time 1 bayes model}
UBSTime1.bmdl <- stan_glm(UBS ~ GDDSum1_11 * PrecipSum1_11 + Weight + CalcAge,
                              data = scaled.df,
                              family = gaussian(),
                              algorithm = "sampling",
                              prior = student_t(df = 7, 0, 5), 
                              prior_intercept = student_t(df = 7, 0, 5),
                              cores = 2, seed = 666)
print(summary(UBSTime1.bmdl), digits = 3)
#launch_shinystan(UBSTime1.bmdl)
```

```{r plot UBS time 1}
UBSGDDTime1.plot <- plot(UBSTime1.bmdl, pars = c("GDDSum1_11","PrecipSum1_11","Weight","CalcAge","GDDSum1_11:PrecipSum1_11"))
#UBSGDDTime1.plot
```
<br>

Bayesian Upper Bill Surface Area GDD Time 2
```{r UBS Time 2 bayes model}
UBSTime2.bmdl <- stan_glm(UBS ~ GDDSum12_22 * PrecipSum12_22 + Weight + CalcAge,
                              data = scaled.df,
                              family = gaussian(),
                              algorithm = "sampling",
                              prior = student_t(df = 7, 0, 5), 
                              prior_intercept = student_t(df = 7, 0, 5),
                              cores = 2, seed = 666)
print(summary(UBSTime2.bmdl), digits = 3)
#launch_shinystan(UBSTime1.bmdl)
```

```{r plot UBS Time 2 model}
UBSGDDTime2.plot <- plot(UBSTime2.bmdl, pars = c("GDDSum12_22","PrecipSum12_22","Weight","CalcAge","GDDSum12_22:PrecipSum12_22"))
#UBSGDDTime2.plot
```
<br>

Arrange the Upper Bill Surface Area model plots
```{r ggarrange UBS GDD plots}
UBSModelPlots.wrap <- ggarrange(UBSGDDIncub.plot,UBSGDDTime1.plot,UBSGDDTime2.plot, ncol = 1)
annotate_figure(UBSModelPlots.wrap, top = "Upper Bill Surface Area Models")
```
<br>

## Tarsus Models

Bayesian Tarsus Incubation model
```{r Tarsus Incubation bayes model}
TarsusIncub.bmdl <- stan_glm(Tarsus ~ GDDSumIncubation * PrecipSumIncubation + Weight + CalcAge,
                              data = scaled.df,
                              family = gaussian(),
                              algorithm = "sampling",
                              prior = student_t(df = 7, 0, 5), 
                              prior_intercept = student_t(df = 7, 0, 5),
                              cores = 2, seed = 666)
print(summary(TarsusIncub.bmdl), digits = 3)
#launch_shinystan(TarsusIncub.bmdl)
```

```{r plot Tarsus GDD Incubation model}
TarsusGDDIncub.plot <- plot(TarsusIncub.bmdl, pars = c("GDDSumIncubation","PrecipSumIncubation","Weight","CalcAge","GDDSumIncubation:PrecipSumIncubation"))
#TarsusGDDIncub.plot
```
<br>

Bayesian Tarsus GDD Time 1 model
```{r Tarsus Time 1 bayes model}
TarsusTime1.bmdl <- stan_glm(Tarsus ~ GDDSum1_11 * PrecipSum1_11 + Weight + CalcAge,
                              data = scaled.df,
                              family = gaussian(),
                              algorithm = "sampling",
                              prior = student_t(df = 7, 0, 5), 
                              prior_intercept = student_t(df = 7, 0, 5),
                              cores = 2, seed = 666)
print(summary(TarsusTime1.bmdl), digits = 3)
#launch_shinystan(TarsusTime1.bmdl)
```

```{r plot Tarsus time 1}
TarsusGDDTime1.plot <- plot(TarsusTime1.bmdl, pars = c("GDDSum1_11","PrecipSum1_11","Weight","CalcAge","GDDSum1_11:PrecipSum1_11"))
#TarsusGDDTime1.plot
```
<br>

Bayesian Tarsus GDD Time 2
```{r Tarsus Time 2 bayes model}
TarsusTime2.bmdl <- stan_glm(Tarsus ~ GDDSum12_22 * PrecipSum12_22 + Weight + CalcAge,
                              data = scaled.df,
                              family = gaussian(),
                              algorithm = "sampling",
                              prior = student_t(df = 7, 0, 5), 
                              prior_intercept = student_t(df = 7, 0, 5),
                              cores = 2, seed = 666)
print(summary(TarsusTime2.bmdl), digits = 3)
#launch_shinystan(TarsusTime1.bmdl)
```

```{r plot Tarsus Time 2 model}
TarsusGDDTime2.plot <- plot(TarsusTime2.bmdl, pars = c("GDDSum12_22","PrecipSum12_22","Weight","CalcAge","GDDSum12_22:PrecipSum12_22"))
#TarsusGDDTime2.plot
```
<br>

Arrange the Tarsus model plots
```{r ggarrange Tarsus GDD plots}
TarsusModelPlots.wrap <-ggarrange(TarsusGDDIncub.plot,TarsusGDDTime1.plot,TarsusGDDTime2.plot, ncol = 1)
annotate_figure(TarsusModelPlots.wrap, top = "Tarsus Models")
```
<br>

