---
title: "CrowNestlingClimateModels"
author: "Justin Mann"
date: "2022-12-03"
output: html_document
---

```{r libraries}
library(tidyverse)
library(dplyr)
library(broom) #tidy() to create tibbles from model summaries
library(car)
library(lme4) #frequentist models  
library(sjPlot) #plot_model & tab_model (blue = #377EB8)
library(ggpubr) #ggarrange
library(glmmTMB) #zi & overdispersed models
library(lmerTest) #lmerTest::step
library(ggeffects) #ggpredict
#PACKAGES FOR BAYESIAN MODELS
# library(rstanarm) #stan models
# library(shinystan) #stan model evaluation
#launch_shinystan_demo()
# library(loo) #use loo() to compare fits between bayesian models
library(plotly)
library(MuMIn) #dredge() for unsupervised model selection
library(AICcmodavg) #aictab() for AICc model comparisons
library(DHARMa)
theme_set(theme_classic())
```


```{r forest.plot function}
forest.plot <- function(mdl){
  mdl.df <- tidy(mdl, quick = FALSE)
  ci <- as_tibble(confint(mdl))
  mdl.df$ci.lower <- ci$`2.5 %`
  mdl.df$ci.upper <- ci$`97.5 %`
  mdl.df <- mdl.df[-1,]
  
  ggplot(data = mdl.df)+
    geom_pointrange(aes(x=term, y=estimate, ymin=ci.lower, ymax=ci.upper), size=1.3, shape=20)+
    coord_flip()+
    geom_hline(yintercept = 0, color="red",size=1)+
    ggtitle("Parameter estimates")+
    theme(plot.title = element_text(size = 22),
        axis.text.x = element_text(size = 18),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 18),
        axis.title.y = element_blank(),
        plot.margin = margin(15,15,15,15))
  
}
```

```{r mdl.tbl function}
mdl.tbl <- function(mdl){
  mdl.df <- tidy(mdl, quick = FALSE)
  ci <- as_tibble(confint(mdl))
  mdl.df$ci.lower <- ci$`2.5 %`
  mdl.df$ci.upper <- ci$`97.5 %`
  mdl.df <- mdl.df[-1,]
  print(mdl.df)
}
```

<br> 



## Crow Nestling Climate Models 


### Read in data

```{r dataframes}
#Males
M.df <- read.csv("MaleNestlingClimateJoined.csv",h=TRUE)

#Females 
F.df <- read.csv("FemaleNestlingClimateJoined.csv",h=TRUE)

#Both sexes
B.df <- rbind(F.df,M.df)
```
<br>

### Deal with NAs and make sure variables are the correct class (numeric or factor)

```{r raw summary}
summary(B.df)
```


```{r prepare variables}
#some metrics aren't recognized as numeric, so we'll coerce them using the as.numeric function
is.numeric(B.df$TEC)
B.df$TEC <- as.numeric(B.df$TEC)
B.df$Skull <- as.numeric(B.df$Skull)

#Renaming some variables while we're at it

#UB = upper bill
B.df$UB <- as.numeric(B.df$UpperBill)
#UBS = upper bill surface area
B.df$UBS <- as.numeric(B.df$UBillSurface)
#TBS = total bill surface area
B.df$TBS <- as.numeric(B.df$TotBillSurface)

#Make Month a factor for plotting
B.df$Month <- as.factor(B.df$Month)

#There is one lower case f instead of upper case F in AllSex column for one female
B.df$AllSex <- gsub('f', 'F', B.df$AllSex)
B.df$AllSex <- as.factor(B.df$AllSex)

#Simplify the df
B.df <- B.df %>% 
  select(Month,ID,CalcAge,HatchDateJulYear,AllSex,BillDepth,BillWidth,BillNT,TEC,UB,UBS,TBS,
         Skull,Tarsus,Weight,
         MaxTempMean1_11,MaxTempMean12_22,MeanMaxTempIncubation,
         MinTempMean1_11,MinTempMean12_22,MeanMinTempIncubation,
         GDDSum1_11,GDDSum12_22,GDDSumIncubation,
         PrecipSum1_11,PrecipSum12_22,PrecipSumIncubation)

summary(B.df)
```


```{r fix NAs in months}
#6 individuals with HatchDateJulYear 2002099 and 2012099 are showing NAs, should be 4 (April)
B.df$Month <- B.df$Month %>% replace_na("4")

summary(B.df)
```
We could leave NAs in the dataframe, but the dredge function (for top model selection) will not work with NAs in the dataframe.

```{r remove NAs in morphometrics}
#7 more rows have NAs in morphometrics
sum(!complete.cases(B.df[-1]))

#Omit the remaining rows with NAs
B.df <- na.omit(B.df)

#One final summary to make sure everything is clean and correct
summary(B.df)
```
<br> 

## No more missing data. Ready for modelling!

Now, we'll regress our morphological metrics against age and make columns with the residuals for models that control for age. 

We'll include histograms of each set of residuals to check for funky distributions.

```{r create morphometric ~ CalcAge residuals}
#Bill Depth
BDAge.mdl <- lm(data = B.df, BillDepth ~ CalcAge)
B.df$BDAgeResids <- BDAge.mdl$residuals  
hist(B.df$BDAgeResids)

#Bill Width
BWAge.mdl <- lm(data = B.df, BillWidth ~ CalcAge)
B.df$BWAgeResids <- BWAge.mdl$residuals
hist(B.df$BWAgeResids)

#BillNT
BNTAge.mdl <- lm(data = B.df, BillNT ~ CalcAge)
B.df$BNTAgeResids <- BNTAge.mdl$residuals
hist(B.df$BNTAgeResids)

#TEC
TECAge.mdl <- lm(data = B.df, TEC ~ CalcAge)
B.df$TECAgeResids <- TECAge.mdl$residuals
hist(B.df$TECAgeResids)

#UpperBill
UBAge.mdl <- lm(data = B.df, UB ~ CalcAge)
B.df$UBAgeResids <- UBAge.mdl$residuals
hist(B.df$UBAgeResids)

#Upper Bill Surface Area
UBSAge.mdl <- lm(data = B.df, UBS ~ CalcAge)
B.df$UBSAgeResids <- UBSAge.mdl$residuals
hist(B.df$UBSAgeResids)

#Total Bill Surface Area
TBSAge.mdl <- lm(data = B.df, TBS ~ CalcAge)
B.df$TBSAgeResids <- TBSAge.mdl$residuals
hist(B.df$TBSAgeResids)

#Skull
SkullAge.mdl <- lm(data = B.df, Skull ~ CalcAge)
B.df$SkullAgeResids <- SkullAge.mdl$residuals
hist(B.df$SkullAgeResids)

#Tarsus
TarsusAge.mdl <- lm(data = B.df, Tarsus ~ CalcAge)
B.df$TarsusAgeResids <- TarsusAge.mdl$residuals
hist(B.df$TarsusAgeResids)
```

## Scaling continuous metrics for modeling 
```{r create B.scaled.df}
#?scale()
B.factors.df <- B.df[,1:5]
B.scaled.df <- scale(B.df[,6:36])
B.scaled.df <- cbind(B.factors.df,B.scaled.df)
```

Now that the dataframe is clean and residual columns are added, we'll recreate the separate male and female dataframes.

```{r recreate raw and scaled male and female dfs}
#Now that B.df is cleaned and bill metric ~ age residuals are added, recreate male and female dfs
F.df <- subset(B.df, AllSex=="F")
M.df <- subset(B.df, AllSex=="M")

#Create scaled M and F dfs
F.scaled.df <- subset(B.scaled.df, AllSex=="F")
M.scaled.df <- subset(B.scaled.df, AllSex=="M")
```
<br> 

## Female Models


### Female Bill Depth Models


Response = bill depth/age residuals
Independent = Main effects of Max temp 1, precipitation 1, and Weight
              Interactions between Max temp * Precip 
              
Note about coding interactions!   
  A colon (:) tells R to include only the interaction, without main effects.
  A asterisk (*) tells R to include the interaction AND the main effects. 


```{r female Bill Depth time period 1 models}
#Model with scaled data
F.BDMax1.scaled.mdl <- lm(data = F.scaled.df, BDAgeResids ~ MaxTempMean1_11*PrecipSum1_11 + Weight, na.action = "na.fail")
car::vif(F.BDMax1.scaled.mdl)
summary(F.BDMax1.scaled.mdl)
plot_model(F.BDMax1.scaled.mdl, type = "int", terms = c("MaxTempMean1_11", "PrecipSum1_11"))

#Same model with unscaled data
F.BDMax1.mdl <- lm(data = F.df, BDAgeResids ~ MaxTempMean1_11*PrecipSum1_11 + Weight, na.action = "na.fail")
car::vif(F.BDMax1.mdl) #VIF is uncomfortably high for some vars
summary(F.BDMax1.mdl)
plot_model(F.BDMax1.mdl, type = "int", terms = c("MaxTempMean1_11", "PrecipSum1_11"))

#?vif()

#dredge function applied to determine the best combination of variables
F.BDMax1.dredge <- dredge(F.BDMax1.scaled.mdl, rank = "AICc")

F.BDMax1.dredge #Top model is >2 delta AICc values from the next best model
#No model averaging needed
```
<br>

```{r}
forest.plot(F.BDMax1.scaled.mdl)
mdl.tbl(F.BDMax1.scaled.mdl)
forest.plot(F.BDMax1.mdl)
mdl.tbl(F.BDMax1.mdl)
```



```{r model.avg function}
#model.avg function averages all top models within 2 delta values of each other, as recommended in Burnham and Anderson (2002) Model Selection and Multimodel Inference: A Practical Information-Theoretic Approach
  
  #F.BDMax1.avg <- model.avg(F.BDMax1.dredge, subset = F.BDMax1.dredge$delta < 2, revised.var = TRUE, fit = TRUE)

##Summary of averaged model (See the second set of Conditionally Averaged Coefficients)
# summary(F.BDMax1.avg)
```
<br> 


```{r BDAgeResids and Weight plot}
F.df %>% ggplot(aes(x=PrecipSum1_11,y=BDAgeResids))+
  geom_point()
```
Yeah, definitely not negative. The negative main effect must result from the interaction term, but I'm confused by this.

```{r Temp 1 and Precip 1 plot}
F.df %>% ggplot(aes(x=MaxTempMean1_11,y=PrecipSum1_11))+
  geom_point()
```
<br> 



### Second bill metric model:
Same as the first, but with second period max temp and precip

```{r female Bill Depth time period 2 models}
F.BDMax2.mdl <- lm(data = F.df, BDAgeResids ~ MaxTempMean12_22*PrecipSum12_22 + Weight , na.action = "na.fail")
car::vif(F.BDMax2.mdl)
summary(F.BDMax2.mdl)

F.BDMax2.scaled.mdl <- lm(data = F.scaled.df, BDAgeResids ~ MaxTempMean12_22*PrecipSum12_22 + Weight , na.action = "na.fail")
car::vif(F.BDMax2.scaled.mdl)
summary(F.BDMax2.scaled.mdl)
forest.plot(F.BDMax2.scaled.mdl)


#Dredge to find top models
F.BDMax2.dredge <- dredge(F.BDMax2.scaled.mdl, rank = "AICc")
F.BDMax2.dredge
F.BDMax2.avg <- model.avg(F.BDMax2.dredge, subset = F.BDMax2.dredge$delta < 2, revised.var = TRUE, fit = TRUE)
summary(F.BDMax2.avg)


##Summary of averaged model (See the second set of Conditionally Averaged Coefficients)
# summary(F.BDMax1.avg)

```

### Female Tarsus Models

As a point of comparison, let's model tarsus~age residuals to decide whether climate is affecting bill shape more than a less plastic (?) trait.

```{r female tarsus time period 1 models}
F.TarsusMax1.mdl <- lm(data = F.scaled.df, TarsusAgeResids ~ MaxTempMean1_11*PrecipSum1_11 + Weight, na.action = "na.fail")

#Full model summary
summary(F.TarsusMax1.mdl)

#dredge function applied to determine the best combination of variables
F.TarsusMax1.dredge <- dredge(F.TarsusMax1.mdl, rank = "AICc")

#model.avg function averages all top models within 2 delta values of each other
F.TarsusMax1.avg <- model.avg(F.TarsusMax1.dredge, subset = F.TarsusMax1.dredge$delta < 2, revised.var = TRUE, fit = TRUE)

#Summary of averaged model (See the second set of Conditionally Averaged Coefficients)
summary(F.TarsusMax1.avg)
```
VERY COOL!! Max temp and precip 1 have no effect on Tarsus, but they do on Bill depth.

```{r female tarsus time period 2 models}
F.TarsusMax2.mdl <- lm(data = F.scaled.df, TarsusAgeResids ~ MaxTempMean12_22*PrecipSum12_22 + Weight, na.action = "na.fail")

#Full model summary
summary(F.TarsusMax2.mdl)

#dredge function applied to determine the best combination of variables
F.TarsusMax2.dredge <- dredge(F.TarsusMax2.mdl, rank = "AICc")

#model.avg function averages all top models within 2 delta values of each other
F.TarsusMax2.avg <- model.avg(F.TarsusMax2.dredge, subset = F.TarsusMax1.dredge$delta < 2, revised.var = TRUE, fit = TRUE)

#Summary of averaged model (See the second set of Conditionally Averaged Coefficients)
summary(F.TarsusMax2.avg)
```
In the time period two model, Max Temp and Precip are non-significant, but the Temp * Precip interaction is signficant. Still an interesting departure from the bill metric model results.


### Female Skull Models

```{r female skull time period 1 models}
F.SkullMax1.mdl <- lm(data = F.scaled.df, SkullAgeResids ~ MaxTempMean1_11*PrecipSum1_11 + Weight, na.action = "na.fail")

#Full model summary
summary(F.SkullMax1.mdl)

#dredge function applied to determine the best combination of variables
F.SkullMax1.dredge <- dredge(F.SkullMax1.mdl, rank = "AICc")

#model.avg function averages all top models within 2 delta values of each other
F.SkullMax1.avg <- model.avg(F.SkullMax1.dredge, subset = F.SkullMax1.dredge$delta < 2, revised.var = TRUE, fit = TRUE)

#Summary of averaged model (See the second set of Conditionally Averaged Coefficients)
summary(F.SkullMax1.avg)
```
Like tarsus, there is no effect of climate variables on skull in time period 1


```{r female skull time period 2 models}
F.SkullMax2.mdl <- lm(data = F.scaled.df, SkullAgeResids ~ MaxTempMean12_22*PrecipSum12_22 + Weight, na.action = "na.fail")

#Full model summary
summary(F.SkullMax2.mdl)

#dredge function applied to determine the best combination of variables
F.SkullMax2.dredge <- dredge(F.SkullMax2.mdl, rank = "AICc")
F.SkullMax2.dredge

#Top model is over two delta AICc values away from next top model, so no averaging necessary

#Reprint full model summary
summary(F.SkullMax2.mdl)
```

In time period two, Max Temp and Precip are positively associated with skull~age residuals.


### Female Upper Bill Surface Area Models

```{r female UBS time period 1 models}
F.UBSMax1.mdl <- lm(data = F.scaled.df, UBSAgeResids ~ MaxTempMean1_11*PrecipSum1_11 + Weight, na.action = "na.fail")

#Full model summary
summary(F.UBSMax1.mdl)

#dredge function applied to determine the best combination of variables
F.UBSMax1.dredge <- dredge(F.UBSMax1.mdl, rank = "AICc")

#model.avg function averages all top models within 2 delta values of each other
F.UBSMax1.avg <- model.avg(F.UBSMax1.dredge, subset = F.UBSMax1.dredge$delta < 2, revised.var = TRUE, fit = TRUE)

#Summary of averaged model (See the second set of Conditionally Averaged Coefficients)
summary(F.UBSMax1.avg)
```
Dredge drops UBS from the model because it's not explaining enough variance.

Let's check out time period 2
```{r female UBS time period 2 models}
F.UBSMax2.mdl <- lm(data = F.scaled.df, UBSAgeResids ~ MaxTempMean12_22*PrecipSum12_22 + Weight, na.action = "na.fail")

#Full model summary
summary(F.UBSMax2.mdl)

#dredge function applied to determine the best combination of variables
F.UBSMax2.dredge <- dredge(F.UBSMax2.mdl, rank = "AICc")

#model.avg function averages all top models within 2 delta values of each other
F.UBSMax2.avg <- model.avg(F.UBSMax2.dredge, subset = F.UBSMax2.dredge$delta < 2, revised.var = TRUE, fit = TRUE)

#Summary of averaged model (See the second set of Conditionally Averaged Coefficients)
summary(F.UBSMax2.avg)
```

Temp and Precip affect UBS in time period 2


### Female Total Bill Surface Area Models
Does upper bill respond more?

Start with just time period 2 for now
```{r female TBS time period 2 models}
F.TBSMax2.mdl <- lm(data = F.scaled.df, TBSAgeResids ~ MaxTempMean12_22*PrecipSum12_22 + Weight, na.action = "na.fail")

#Full model summary
summary(F.TBSMax2.mdl)

#dredge function applied to determine the best combination of variables
F.TBSMax2.dredge <- dredge(F.TBSMax2.mdl, rank = "AICc")

#model.avg function averages all top models within 2 delta values of each other
F.TBSMax2.avg <- model.avg(F.TBSMax2.dredge, subset = F.TBSMax2.dredge$delta < 2, revised.var = TRUE, fit = TRUE)

#Summary of averaged model (See the second set of Conditionally Averaged Coefficients)
summary(F.TBSMax2.avg)
```

Max Temp 2 is positively associated with TBS age residuals
