---
title: American Crow nestling morphology responds to yearly fluctuations in temperature
  and precipitation
author: "Justin Mann"
date: "`r Sys.Date()`"
output: html_document
---

```{r libraries, results="hide", warning=FALSE, message=FALSE}
library(tidyverse)
library(broom) #tidy() to create tibbles from model summaries
library(ggpubr) #ggarrange for plot wraps
library(bbmle) #AICtab() for model comparison
library(DHARMa) #model validation functions
library(mgcv)
library(mgcViz)

theme_set(theme_classic()) #default plots with no gridlines
```


This color palette was developed to ensure that individuals with colorblindness can see the contrast between all color combinations.

```{r colorblind accessible pallet}
colorBlindPal  <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
                       "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```


A function to created data frames needed to produce forest plots for linear models.
```{r dfs for fplot function}
fplot_df <- function(model, dataset, metric) {
  df <- tidy(model, quick = FALSE)
  ci <- as_tibble(confint(model))
  df$ci.lower <- ci$`2.5 %`
  df$ci.upper <- ci$`97.5 %`
  df$Dataset <- dataset
  df$Metric <- metric
  df <- df[-1,]
  return(df)
}
```


A function to create the forest plots for linear models.
```{r fplot function}
fplot <- function(metric) {
    ggplot(data = metric) +
        geom_errorbar(aes(x = term, ymin = ci.lower, ymax = ci.upper, color = Dataset),
                      linewidth = 1, width = 0.3, position = position_dodge(width = 0.4)) +
        geom_point(aes(x = term, y = estimate, color = Dataset), 
                   shape = 16, size = 3, position = position_dodge(width = 0.4)) +
        scale_color_manual(name = "", values = c("#000000", "#E69F00", "#56B4E9"),
                           labels = c("All", "Female", "Male")) +
        coord_flip() +
        geom_hline(yintercept = 0, color = "red", size = 1, linetype = "dotted") +
        scale_x_discrete(labels = c("Min Temp", "Min Temp * Precip", "Precip","Weight")) +
        ylab("Parameter estimate") +
        theme(plot.title = element_text(size = 16),
              axis.text.x = element_text(size = 12),
              axis.title.x = element_text(size = 14),
              axis.text.y = element_text(size = 14),
              axis.title.y = element_blank(),
              legend.position = "top",
              plot.margin = margin(15, 15, 15, 15))
}
```

A function to create dataframes for GAM predictions.
```{r make_gam_pred_df function}
make_gam_pred_df <- function(dataframe, model, focal_var, length_out = 200) {
  # Check focal variable exists
  if (!focal_var %in% names(dataframe)) {
    stop(paste("Variable", focal_var, "not found in dataframe."))
  }
  
  # Build new data frame
  pred_df <- as.data.frame(lapply(dataframe, function(x) {
    if (is.numeric(x)) mean(x, na.rm = TRUE) else unique(x)[1]
  }))
  
  # Replace focal variable with sequence
  pred_df <- pred_df[rep(1, length_out), ]  # replicate row
  pred_df[[focal_var]] <- seq(
    min(dataframe[[focal_var]], na.rm = TRUE),
    max(dataframe[[focal_var]], na.rm = TRUE),
    length.out = length_out
  )
  
  # Predict with standard errors
  pred <- predict(model, newdata = pred_df, type = "response", se.fit = TRUE)
  
  pred_df$fit <- pred$fit
  pred_df$se <- pred$se.fit
  pred_df$upper <- pred_df$fit + 2 * pred_df$se
  pred_df$lower <- pred_df$fit - 2 * pred_df$se
  
  return(pred_df)
}
```


A function to create GAM effect plots
```{r plot_gam_effect function}
plot_gam_effect <- function(model, dataframe, focal_var, response_var,
                            xlab = NULL, ylab = NULL, color = "#56B4E9") {
  # Build prediction dataframe
  pred_df <- make_gam_pred_df(dataframe, model, focal_var)
  
  # Default axis labels
  if (is.null(xlab)) xlab <- focal_var
  if (is.null(ylab)) ylab <- response_var
  
  # Build plot
  p <- ggplot(pred_df, aes_string(x = focal_var, y = "fit")) +
    geom_line(size = 1.2, color = color) +
    geom_ribbon(aes(ymin = lower, ymax = upper), fill = color, alpha = 0.2) +
    geom_point(data = dataframe,
               aes_string(x = focal_var, y = response_var),
               shape = 1) +
    labs(x = xlab, y = ylab)
  
  return(p)
}
```



## Import Nestling Data

```{r unscaled data}
df <- read.csv("CrowNestlingClimate_UnscaledData_7.8.23.csv", h=TRUE)
# n=2030 nestlings
df$TBSWeightRatio <- df$TBS/df$Weight # adding a vector to hold the ratio of Total Bill Surface Area (TBS) to Weight
head(df)
```


## Import Weather Data

```{r clim.df}
clim_df <- read.csv("ClimateMetrics_AllMonths1989-2022.csv", h=T)
```


## Data Scaling

### Normalize Continuous Data

For each continuous vector, subtract each value from the mean (center) and divide it by the standard deviation. Since the continuous data were collected in a variety of units with different orders of magnitude, scaling the continuous data results in better fit models.

```{r scaling}
#categorical data  
categorical_df <- df[,1:11]

#continuous data
continuous_df <- df[,12:47]

#scale continuous data
#?scale()
scaled_mat <- scale(continuous_df, center = TRUE, scale = TRUE)

#join unscaled and scaled data
scaled_df <- cbind(categorical_df,scaled_mat)
```

## Data frames for males, females and unknown sex


```{r sexes data frames}
#Males scaled
M_scaled_df <- subset(scaled_df, Sex=="M")
#Males unscaled
M_df <- subset(df, Sex=="M")

#Females scaled
F_scaled_df <- subset(scaled_df, Sex=="F")
#Females unscaled
F_df <- subset(df, Sex=="F")

#Unsexed scaled
U_scaled_df <- subset(scaled_df, Sex=="U")
#Unsexed unscaled
U_df <- subset(df, Sex=="U")

#Both sexes scaled
B_scaled_df <- rbind(F_scaled_df,M_scaled_df)
#Both sexes unscaled
B_df <- rbind(F_df,M_df)
```


## Summarizing Weather across Years

Here, I use dplyr functions to manipulated the climate data frame and create a subset that includes the months when crows are breeding in Ithaca.

```{r breedingClim_df}
clim_df$Date <- as.Date(clim_df$Date)
clim_df$Month <- lubridate::month(clim_df$Date)
clim_df <- clim_df %>% 
  relocate(Month, .after = Year)
breedingClim_df <- clim_df %>% #filtering weather data to include only 1 March-30 June
  filter(between(Month, 3,6)) %>% 
  filter(between(JulDay, 60,181))
```

## Plotting minimum temperature and precipitation during the breeding season across years

```{r plot median min temp}
median(breedingClim_df$MinC, na.rm=TRUE)
min_plot <- ggplot(data = breedingClim_df, aes(x=as.factor(Year), y=MinC))+
  geom_boxplot()+
  geom_hline(yintercept = 3.89, color = "red", linetype = "dotted", linewidth = 1)+
  ylab("Minimum Temperature (C)")+
  xlab("")+
  theme(axis.text.x = element_text(angle = 90))
```


```{r plot precip}
median(breedingClim_df$PrecipCM, na.rm=TRUE)
precip_plot <- ggplot(data = clim_df, aes(x=as.factor(Year), y=PrecipCM))+
  geom_boxplot()+
  geom_hline(yintercept = 0.025, color = "red", linetype = "dotted", linewidth = 1)+
  ylab("Precipitation (cm)")+
  xlab("")+
  theme(axis.text.x = element_text(angle = 90))
```

```{r wrap climate plots, out.width='100%'}
BreedingClimate_wrap <- ggarrange(min_plot,precip_plot, ncol = 1)
BreedingClimate_wrap
```


### Weight by Minimum Temperature Plot

```{r WeightMinC_plot}
WeightMinC_plot <- ggplot(data = df, aes(x = MinC8_22, y = Weight, color = Sex))+
  geom_jitter(width = 0.2, shape = 1, size = 1.8)+
  geom_smooth(method="lm", aes(fill = Sex), alpha = 0.2)+
  scale_color_manual(name="",
                    values=c("#E69F00","#56B4E9","#000000"),
                    labels=c("Female","Male","Unsexed"))+
  scale_fill_manual(values = c("#E69F00","#56B4E9","#000000"), guide = "none")+
  ylab("Weight (g)")+
  xlab("Average minimum temperature (C)")+
  theme(plot.title = element_text(size = 16),
          axis.text.x = element_text(size = 12),
          axis.title.x = element_text(size = 14),
          axis.text.y = element_text(size = 14),
          axis.title.y = element_text(size = 14),
          legend.position = "top",
          plot.margin = margin(15,15,15,15))
suppressWarnings(print(WeightMinC_plot))
#cowplot::save_plot("Plots/WeightMinC_plot.png", WeightMinC_plot, base_height = 4, base_width = 7)
```


### Male Weight Model

```{r M_Weight_mdl}
M_Weight_mdl <- lm(Weight ~ MinC8_22 * PrecipSum8_22, data = M_scaled_df)
summary(M_Weight_mdl)
```


```{r M_Weight model validation}
M_Weight_simres <- simulateResiduals(M_Weight_mdl, n = 1000, plot = TRUE)
```

```{r M_Weight_nointer_mdl}
M_Weight_nointer_mdl <- lm(Weight ~ MinC8_22 + PrecipSum8_22, data = M_scaled_df)
summary(M_Weight_nointer_mdl)
```
Removing the interaction in the male weight model has no significant impact on the results.


```{r M_Weight_nointer model validation}
M_Weight_simres <- simulateResiduals(M_Weight_nointer_mdl, n = 1000, plot = TRUE)
```

Without the interaction between temp & precip in the male weight model, the KS test becomes significant, while it is non significant when the interaction is included. 


```{r M_Weight models AIC comparison}
AIC(M_Weight_nointer_mdl, M_Weight_mdl)
```
There is a 1.45 AIC value difference between the M_Weight_nointer_mdl & M_Weight_mdl and thus on strong evidence that one model fits better than the other. Since the no interaction model (M_Weight_nointer_mdl) residuals deviate from a normal distribution and there is no significant change in the result, we will stick with the interaction model (M_Weight_mdl). 

### Female Weight Model

```{r F_Weight_mdl}
F_Weight_mdl <- lm(Weight ~ MinC8_22 * PrecipSum8_22, data = F_scaled_df)
summary(F_Weight_mdl)
```


```{r F_Weight model validation}
F_Weight_simres <- simulateResiduals(F_Weight_mdl, n = 1000, plot = TRUE)
```


```{r F_Weight_nointer_mdl}
F_Weight_nointer_mdl <- lm(Weight ~ MinC8_22 + PrecipSum8_22, data = F_scaled_df)
summary(F_Weight_nointer_mdl)
```
Removing the interaction in the female weight model has no significant impact on the results. 


```{r F_Weight_nointer model validation}
F_Weight_simres <- simulateResiduals(F_Weight_nointer_mdl, n = 1000, plot = TRUE)
```

For females, the model without an interaction still has non significant validation tests.


### All Nestlings Weight Model

```{r A_Weight_mdl}
A_Weight_mdl <- lm(Weight ~ MinC8_22 * PrecipSum8_22, data = scaled_df)
summary(A_Weight_mdl)
```


```{r A_Weight_mdl validation}
A_Weight_simres <- simulateResiduals(A_Weight_mdl, n = 1000, plot = TRUE)
```


```{r A_Weight_nointer_mdl}
A_Weight_nointer_mdl <- lm(Weight ~ MinC8_22 + PrecipSum8_22, data = scaled_df)
summary(A_Weight_nointer_mdl)
```
Removing the interaction in the all nestling weight model has no significant impact on the results.

```{r A_Weight_nointer_mdl validation}
A_Weight_simres <- simulateResiduals(A_Weight_nointer_mdl, n = 1000, plot = TRUE)
```
For all nestlings, the model without an interaction the validation tests remain non significant.

### Data frames for Weight Forest Plot

```{r Weight_dfs for fplot}
M_Weight_df <- fplot_df(M_Weight_mdl, "Male", "Weight")
F_Weight_df <- fplot_df(F_Weight_mdl, "Female", "Weight")
A_Weight_df <- fplot_df(A_Weight_mdl, "All", "Weight")

Weight_df <- rbind(M_Weight_df, F_Weight_df, A_Weight_df)
```

### Weight Forest Plot

```{r Weight_fplot}
Weight_fplot <- fplot(Weight_df)
Weight_fplot
```


### Weight Plots Wrapped

```{r Weight_wrap, out.width='100%'}
Weight_wrap <- ggarrange(WeightMinC_plot, Weight_fplot, ncol = 2, labels = c("A","B"), widths = c(1.6,1.4))
Weight_wrap
```

## How does weather affect nestling tarsus growth?

### Tarsus by Minimum Temperature Plot

```{r TarsusMinC_plot}
TarsusMinC_plot <- ggplot(data = df, aes(x = MinC8_22, y = Tarsus, color = Sex))+
  geom_jitter(width = 0.2, shape = 1, size = 1.8)+
  geom_smooth(method="loess", aes(fill = Sex), alpha = 0.2)+
  scale_color_manual(name="",
                    values=c("#E69F00","#56B4E9","#000000"),
                    labels=c("Female","Male","Unsexed"))+
  scale_fill_manual(values = c("#E69F00","#56B4E9","#000000"), guide = "none")+
  ylab("Tarsus (mm)")+
  xlab("Average minimum temperature (C)")+
  theme(plot.title = element_text(size = 16),
          axis.text.x = element_text(size = 12),
          axis.title.x = element_text(size = 14),
          axis.text.y = element_text(size = 14),
          axis.title.y = element_text(size = 14),
          legend.position = "top",
          plot.margin = margin(15,15,15,15))
suppressWarnings(print(TarsusMinC_plot))
```


### Male Tarsus Model

```{r M_Tarsus_mdl}
M_Tarsus_mdl <- glm(Tarsus ~ MinC8_22 * PrecipSum8_22 + Weight, data = M_scaled_df)
summary(M_Tarsus_mdl)
```

```{r M_Tarsus_mdl validation}
M_Tasus_simres <- simulateResiduals(M_Tarsus_mdl, n = 1000, plot = TRUE)
```
The male tarsus model fails the DHARMa outlier test. 


```{r M_Tarsus_nointer_mdl}
M_Tarsus_nointer_mdl <- glm(Tarsus ~ MinC8_22 + PrecipSum8_22 + Weight, data = M_scaled_df)
summary(M_Tarsus_nointer_mdl)
```


```{r M_Tarsus_nointer_mdl validation}
M_Tasus_nointer_simres <- simulateResiduals(M_Tarsus_nointer_mdl, n = 1000, plot = TRUE)
```


```{r M_Tarsus AIC comparison}
AIC(M_Tarsus_mdl,M_Tarsus_nointer_mdl)
```


```{r M_Tarsus_gam_mdl}
M_Tarsus_gam_mdl <- gam(Tarsus ~ s(MinC8_22) + s(PrecipSum8_22) + te(MinC8_22, PrecipSum8_22) + s(Weight), family = scat, data = M_scaled_df)
summary(M_Tarsus_gam_mdl)
```
The GAM model recognizes a significantly non-linear effect of precipitation on male tarsus growth.


```{r M_Tarsus_nointer_gam_mdl}
M_Tarsus_nointer_gam_mdl <- gam(Tarsus ~ s(MinC8_22) + s(PrecipSum8_22) + s(Weight), family = scat, data = M_scaled_df)
summary(M_Tarsus_nointer_gam_mdl)
```
Removing the GAM interaction term does not change the significance of the other parameters, so we will keep the interaction term. 


Using the getViz function from mgcViz package to view the partial effects of each model parameter.
```{r M_Tarsus_gam_mdl viz}
M_Tarsus_gam_viz <- getViz(M_Tarsus_gam_mdl)
plot(M_Tarsus_gam_viz)
```


```{r M_Tarsus gam pred df}
M_Tarsus_gam_pred_df <- make_gam_pred_df(dataframe = M_scaled_df, model = M_Tarsus_gam_mdl, focal_var = "PrecipSum8_22")
```


```{r M_Tarsus gam effect plot}
plot_gam_effect(model = M_Tarsus_gam_mdl,
                dataframe = M_scaled_df,
                focal_var = "PrecipSum8_22",
                response_var = "Tarsus",
                xlab = "Scaled precipitation",
                ylab = "Scaled tarsus length")
```





